### 2019-07-07 juliacon2019proceedings/paper/header.tex
Paper upload

% **************GENERATED FILE, DO NOT EDIT**************

\title{GlobalSearchRegression.jl: \\ Building bridges between Machine Learning and Econometrics in Fat-Data scenarios}

\author[1, 3, 4]{Demian Panigo}
\author[1, 2]{Plabo Glüzmann}
\author[1, 5]{Esteban Mocskos}
\author[3]{Adan Mauri Ungaro}
\author[3]{Valentín Mari}
\author[3, 4]{Nicolás Monzón}

\affil[1]{National Scientific and Technical Research Council (CONICET)}
\affil[2]{Center For Distributive, Labor and Social Studies (CEDLAS)}
\affil[3]{National University of La Plata}
\affil[4]{National University of Avellaneda}
\affil[5]{National University of Buenos Aires}

\keywords{Julia, Parallel computing, Econometrics, all-subset regression, Machine Learning, Fat-Data}

### 2019-07-07 juliacon2019proceedings/paper/paper.tex
Paper upload

% JuliaCon proceedings template
\documentclass{juliacon}
\setcounter{page}{1}

% Additional packages used%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{algorithm,amsmath,xcolor,caption}
\usepackage[noend]{algpseudocode}
\usepackage{hyperref}
\DeclareMathOperator{\sgn}{sign}
\DeclareCaptionFont{lightblue}{\color{black}}
\captionsetup[algorithm]{labelfont={bf,lightblue}, textfont={it}}
\renewcommand{\thealgorithm}{\arabic{algorithm}}
\usepackage{array}
\newcolumntype{C}[1]{>{\centering\arraybackslash}m{#1}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\input{header}

\maketitle

\begin{abstract}
The aim of this paper is twofold. The first one is to describe a novel research-project aimed at building bridges between machine learning and econometric worlds. The second one is to introduce the main characteristics and comparative performance of the first Julia-native all-subset regression algorithm included in \verb GlobalSearchRegression.jl  (v1.0.3). As other available alternatives, this algorithm allows researchers to obtain the best model specification among all possible covariate combinations - in terms of user defined information criteria-, but up to 3165 and 197 times faster than STATA and R alternatives, respectively. 
\end{abstract}

\section{Introduction}
While allowing for better and more accurate analysis (and forecasts), fat-data availability generates a revival of Bellman’s \cite{Bellman1961} -and newer- high-dimensionality concerns:
\begin{enumerate}
    \item Exponential increase in required information and execution time \cite{Yu2003} ;
    \item Overfitting risk \cite{Defernez1999}; 
    \item Less-informative euclidean distances \cite{Aggarwal2001}; and
    \item Unfeasible estimators \cite{Buhlmann2011}. 
\end{enumerate}

Notwithstanding, the advantage of having thousands/millions of features to deal with complex phenomena stimulates an unprecedented number of methodological -and technological- improvements to manage the ‘curse of dimensionality’ \cite{Bolon2016}. \vskip 6pt

In Economics, this process has a dual approach with machine-learning (ML) and econometric (EC) algorithms emerging for different purposes: the former for prediction/forecasts (focusing on $\hat{y}$) and the latter for estimation/causal inference (interested in $\hat{\beta}$). Alternatively, the same distinction can be expressed in Diebold’s terms as non-causal vs causal prediction (see \cite{athey2015}), where ML algorithms are designed to reduce prediction sampling-risks -i.e. learning through cross-validation techniques- and EC methods to identify unbiased multivariate relationships -i.e. avoiding consistency issues through residual and coefficient tests for model selection. \vskip 6pt

In turn, ML feature selection algorithms can be classified into three different families: Filters, Wrappers and Embedded -depending on whether they use some classifier/response variable information or not, or how variable selection is made along with the learning process, see \cite{CHANDRASHEKAR201416}. Similarly, most EC dimensionality reduction approaches can be classified into three different groups: Exhaustive, General-to-Specific and Specific-to-General -depending on the search pattern; see \cite{gluzmann2015}. \vskip 6pt

Despite significant improvements in recent econometric developments -like PCGIVE/Autometrics or Retina algorithms, which combine some ML and EC characteristics-, available alternatives fails to fully exploit cross-validation and model averaging capabilities -see \cite{Doornik09autometrics}, \cite{perezamaral2003}, \cite{DAVIDSON1981}, \cite{derksen1992}, \cite{marinucci2008}, \cite{herwartz2010}, and \cite{castle2006}. \vskip 6pt

Conversely, newer ML algorithms -like Convolutional Neural Networks or Bootstrap-Based LASSO, which improve complex non-linear adjustment or model selection under regularization schemes- achieved unprecedented forecast accuracy but disregarding model interpretability and/or parameter estimation issues -i.e omitting residual and coefficient tests; see \cite{Bzdok2018}. \vskip 6pt

Following Varian’s \cite{varian2014} advices, about ML and EC complementarities -i.e. merging algorithms from different families to reduce both sampling and model uncertainty-, we are developing a novel multi-layer-multi-algorithm methodology combining two reinforcing paradigms: The LSE “Testimation” approach -to obtain information about residual properties, see \cite{abramovich2006}- and the Bayesian-like “Double-model averaging” -across different covariates and sub-samples, see \cite{hoetening1999}. This methodology includes five complementary layers -handling cross-section, time series and panel data-: 1) Pre-processing: with outlier detection, missing values identification, seasonal adjustment and normalization/standardization functions; 2) Feature extraction: creation of logs, squares, inverses and interactions from selected variables; 3) Feature pre-selection: using filter and embedded ML algorithms like CFS, Variance threshold and LASSO functions; 4) Final feature selection: with a modified all-subset regression approach, including residual tests and model averaging capabilities; 5) Post-estimation fine-tuning: coefficient re-evaluation through cross-validation techniques and model averaging across different k-fold results. \vskip 6pt

The objective of this paper is to introduce the main characteristics and comparative performance of a key layer of our methodology: the modified all-subset regression algorithm included in \href{https://github.com/ParallelGSReg/GlobalSearchRegression.jl}{GlobalSearchRegression.jl} (v1.0.3). As other available alternatives (like \href{https://cran.r-project.org/web/packages/MuMIn/MuMIn.pdf}{MuMin-pdredge} in R, or \href{https://www.researchgate.net/profile/Pablo_Gluzmann/publication/264782750_Global_Search_Regression_A_New_Automatic_Model-selection_Technique_for_Cross-section_Time-series_and_Panel-data_Regressions/links/53eed18a0cf23733e812c10d/Global-Search-Regression-A-New-Automatic-Model-selection-Technique-for-Cross-section-Time-series-and-Panel-data-Regressions.pdf?origin=publication_detail}{GSREG} Stata alternatives), this Julia algorithm allows researchers to obtain the best model specification among all possible covariate/feature combinations - in terms of user defined information criteria-, but up to 3165 times faster than Stata and 197 times faster than R. \vskip 6pt

\section{Package's main features}
\label{sec:packagefeatures}
%

Written in Julia, GlobalSearchRegression is a parallel (and improved) version of the Stata-GSREG all-subset regression command (get the original code \href{https://ideas.repec.org/c/boc/bocode/s457737.html}{here}). The package structure is quite simple, as shown in figure 1:

%%%%%%%%%%%%%%%%%% Figure 1
\begin{figure}[h]
\centerline{\includegraphics[width=10cm]{paper/Images/flowchart.png}}
\caption{ GlobalSearchRegression.jl Structure Flowchart}
	\label{fig:sample_figure}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%

Through the gsreg function of the \verb interface.jl  internal package, users set the appropriate database to be used, the general unrestricted model -GUM, which defines the search space- and additional options for model selection. With this information and complementary supporting functions and definitions provided by \verb strings.jl  -i.e. error messages-, \verb utils.jl  -i.e. equation formatting, combinatorial analysis, database manipulation, sorting results, etc.- and \verb gsreg_results.jl  -i.e. the structure to save estimation results-, the \verb core.jl  package perform the all-subset-regression algorithm explained in the pseudocode below, to obtain the following outputs: 1) a matrix -optionally exported to a csv file through \verb utils.jl-  including regression coefficients, selection criteria, observations and (optionally) t-test, residual tests, averaging-weights and out-of-sample metrics for every alternative model; 2) a text file -also displayed on screen- which contains the best model specification and (optionally) model averaging results in terms of the user-selected information criteria -see multiple examples in \verb runtest.jl-. \vskip 6pt

%%%%%%%%%%%%%%%%%%%%%%% Algorithm 1
\begin{algorithm}[ht]
  \scriptsize
  \caption{module Core.jl}
  \begin{enumerate}

    \item[1.] \textit{\textbf{function} gsreg\_single\_proc\_results!(args…)}
    \begin{enumerate}
        \item[1.1.] Select regression covariates
        \item[1.2.] Perform QR Decomposition
        \item[1.3.] Estimate regression results
        \item[1.4.] Calculate additional tests
        \item[1.5.] Save individual results in a Shared Array
    \end{enumerate}
    \item[] \textbf{end} \textit{function gsreg\_single\_proc\_results!(args…)}

\vspace{2mm}

    \item[2.] \textit{\textbf{function} gsreg\_proc\_results!(args…)}
    \begin{enumerate}
        \item[2.1.] \textbf{for} $j=1$ : $((k^2-1)/ nworkers)$ \textit{\# where nworkers is the user defined number of cores, and k is the numbers of covariates in the GUM}
        \begin{enumerate}
            \item[2.1.1.] $order = (j -1) * nworkers + workerID$
            \item[2.1.2.] \textit{gsreg\_single\_proc\_results!(order, args...)}
        \end{enumerate}
        \item[] \textbf{end} for
    \end{enumerate}
    \item[] \textbf{end} \textit{function gsreg\_single\_proc\_results!(args…)}

\vspace{2mm}

    \item[3.] \textit{\textbf{function} proc!(args…)}
    \begin{enumerate}
        \item[3.1.] Create environment (Shared Array and other objects)
        \item[3.2.] for $workerID = 1:nworkers$
        \begin{enumerate}
            \item[3.2.1] spawn jobs among workerIDs to perform gsreg\_proc\_results!
        \end{enumerate}
        \item[] \textbf{end} for
        \item[3.3.] Perform vector operations
        \item[3.4.] Call \verb utils.jl  sort function
        \item[3.5.] Create results array
    \end{enumerate}
    \item[] \textbf{end} \textit{function proc!(args…)}

\vspace{2mm}

    \item[4.] Export results using \verb gsreg\_results.jl   structure
    \item[5.] Export summary results to a txt file 
    \item[6.] Optionally send the results structure to \verb utils.jl  to export a csv file.
  \end{enumerate}

\textbf{end} module \verb Core.jl .
\end{algorithm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Comparative performance against \textit{R} and \textit{STATA}}
\label{sec:comparativeperf}

%%%%%%%%%%%%%%%%%% Table 1
\begin{table*}[!t]
\tabcolsep1pt
\centering
\tbl{Average execution time and speed-up metrics -over 5 runs-}{
    \scalebox{0.8}{
    \begin{tabular}{|C{1cm}|C{1cm}|C{1cm}|C{1.5cm}|C{1.5cm}|C{1.5cm}|C{1.5cm}|C{1.5cm}|C{1.5cm}|C{1.5cm}|C{1.5cm}|}
    \hline
    \multirow{Cov.} & \multirow{Obs} & \multirow{Threads} & \multicolumn{3}{c|}{Execution time (in seconds)} & \multicolumn{3}{c|}{Parallel Speed-up} & \multicolumn{2}{c|}{Julia Speed-up} \\
\cline{4-11}      &   &   & Julia & R & Stata & Julia & R & Stata & Over R & Over Stata \\
    \hline
    15 & 100 & 1 & 14.0 & 69.1 & 646.6 & 1.0 & 1.0 & 1.0 & 4.9 & 46.2 \\
    \hline
    15 & 100 & 4 & 17.0 & 33.4 & 80.3 & 0.8 & 2.1 & 8.0 & 2.0 & 4.7 \\
    \hline
    15 & 100 & 16 & 22.0 & 23.6 & 22.1 & 0.6 & 2.9 & 29.2 & 1.1 & 1.0 \\
    \hline
    15 & 100 & 32 & 31.4 & 22.3 & 15.1 & 0.4 & 3.1 & 43.0 & 0.7 & 0.5 \\
    \hline
    15 & 1000 & 1 & 18.6 & 74.9 & 667.5 & 1.0 & 1.0 & 1.0 & 4.0 & 35.9 \\
    \hline
    15 & 1000 & 4 & 18.5 & 35.3 & 81.6 & 1.0 & 2.1 & 8.2 & 1.9 & 4.4 \\
    \hline
    15 & 1000 & 16 & 22.2 & 24.6 & 23.3 & 0.8 & 3.1 & 28.7 & 1.1 & 1.0 \\
    \hline
    15 & 1000 & 32 & 31.5 & 21.5 & 16.0 & 0.6 & 3.5 & 41.6 & 0.7 & 0.5 \\
    \hline
    15 & 10000 & 1 & 61.6 & 142.0 & 809.0 & 1.0 & 1.0 & 1.0 & 2.3 & 13.1 \\
    \hline
    15 & 10000 & 4 & 30.5 & 61.4 & 114.7 & 2.0 & 2.3 & 7.1 & 2.0 & 3.8 \\
    \hline
    15 & 10000 & 16 & 25.7 & 38.4 & 37.3 & 2.4 & 3.7 & 21.7 & 1.5 & 1.5 \\
    \hline
    15 & 10000 & 32 & 33.4 & 35.5 & 26.7 & 1.8 & 4.0 & 30.3 & 1.1 & 0.8 \\
    \hline
    20 & 100 & 1 & 169.2 & 10538.9 & 535693.2 & 1.0 & 1.0 & 1.0 & 62.3 & 3165.1 \\
    \hline
    20 & 100 & 4 & 65.6 & 9275.4 & 75510.2 & 2.6 & 1.1 & 7.1 & 141.4 & 1151.1 \\
    \hline
    20 & 100 & 16 & 44.7 & 8855.2 & 4526.3 & 3.8 & 1.2 & 118.4 & 197.9 & 101.2 \\
    \hline
    20 & 100 & 32 & 51.2 & 8732.4 & 1658.2 & 3.3 & 1.2 & 323.0 & 170.7 & 32.4 \\
    \hline
    20 & 1000 & 1 & 362.4 & 10765.9 &   & 1.0 & 1.0 &   & 29.7 &  \\
    \hline
    20 & 1000 & 4 & 119.0 & 9352.3 &   & 3.0 & 1.2 &   & 78.6 &  \\
    \hline
    20 & 1000 & 16 & 58.8 & 8926.4 &   & 6.2 & 1.2 &   & 151.8 &  \\
    \hline
    20 & 1000 & 32 & 59.8 & 8753.9 &   & 6.1 & 1.2 &   & 146.4 &  \\
    \hline
    20 & 10000 & 1 & 2338.4 & 13218.9 &   & 1.0 & 1.0 &   & 5.7 &  \\
    \hline
    20 & 10000 & 4 & 629.4 & 10287.9 &   & 3.7 & 1.3 &   & 16.3 &  \\
    \hline
    20 & 10000 & 16 & 198.6 & 9392.3 &   & 11.8 & 1.4 &   & 47.3 &  \\
    \hline
    20 & 10000 & 32 & 149.5 & 9041.6 &   & 15.6 & 1.5 &   & 60.5 &  \\
    \hline
    25 & 100 & 1 & 6700.7 &   &   & 1.0 &   &   &   &  \\
    \hline
    25 & 100 & 4 & 1937.7 &   &   & 3.5 &   &   &   &  \\
    \hline
    25 & 100 & 16 & 913.7 &   &   & 7.3 &   &   &   &  \\
    \hline
    25 & 100 & 32 & 803.9 &   &   & 8.3 &   &   &   &  \\
    \hline
    25 & 1000 & 1 & 14257.4 &   &   & 1.0 &   &   &   &  \\
    \hline
    25 & 1000 & 4 & 3954.2 &   &   & 3.6 &   &   &   &  \\
    \hline
    25 & 1000 & 16 & 1471.4 &   &   & 9.7 &   &   &   &  \\
    \hline
    25 & 1000 & 32 & 1159.9 &   &   & 12.3 &   &   &   &  \\
    \hline
    25 & 10000 & 1 & 93450.0 &   &   & 1.0 &   &   &   &  \\
    \hline
    25 & 10000 & 4 & 23783.8 &   &   & 3.9 &   &   &   &  \\
    \hline
    25 & 10000 & 16 & 6825.6 &   &   & 13.7 &   &   &   &  \\
    \hline
    25 & 10000 & 32 & 4660.4 &   &   & 20.1 &   &   &   &  \\
    \hline
    \end{tabular}    }   }
\end{table*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In table 1, we present a performance comparison of our GLobalSearchRegression Julia-package against its main alternatives: MuMin-pdredge and GSREG (written in R and Stata\footnote{The parallel version of Stata-GSREG is still under development. A preliminary version is available upon request from authors}, respectively).
Execution times were obtained from a HED architecture using a Threadripper 1950x build, with 16 cores (32 threads) overclocked to 3.8GHz and 64 GiB of DDR4-RAM at 3200Mhz. Comparative scripts were implemented on Julia 1.0.3, R 3.6.0 and Stata 15 IC, running on Ubuntu 18.04.2 LTS -Linux kernel 4.15-\footnote{All these test are available \href{https://github.com/ParallelGSReg/GlobalSearchRegression.jl/tree/master/juliacon2019proceedings/reproducibility}{here}} \vskip 6pt

For experimental -random variable- databases with a few covariates -up to 15 explanatory variables-, our Julia algorithm only provides significant time improvement in standard personal computers -e.g. 4 cores-, being up to twice faster than R and 4 times faster than Stata. For HED computers or HPC nodes, there is almost no difference among the best result obtained for each alternative. \vskip 6pt

However, for databases with 20 or more covariates, our Julia all-subset-regression code is always faster, irrespective of the number of observations or threads -up to 3165 times faster than STATA and 197 times faster than R-. Execution time differences exponentially increase with the number of covariates and slightly decrease with available observations. Moreover, Stata and R alternatives become unfeasible for databases with 25 or more covariates. For a confirmatory analysis, in figure 2 we present execution-time kernel densities for the 20 covariates - 100 observations - 32 threads case, obtained from 300 independent (non-cached) runs. Kernel results show that execution time differences are not an artifact obtained from noisy runs. Our Julia algorithm is consistently faster than R and Stata alternatives. \vskip 6pt

A detailed speed-up analysis is also available for the 25-covariate case. In figure 3, it's shown that our Julia all-subset-regression algorithm scales almost linearly for large databases -while the number of threads is not higher than the number of physical cores-. With small databases, Amdhal's law \cite{Amdahl1967} inputs change. Parallel tasks become lighter and speed-up efficiency degrades consistently with additional threads, because the marginal overhead cost of a larger environment creation is not overcompensated by parallelism gains obtained from additional threads. Notwithstanding, using only physical cores speed-up efficiency is always above 45 \%  -with an average of 84\% for 2, 4, 8 and 16 threads-.

%%%%%%%%%%%%%%%%%% Figure 2

\begin{figure*}[!t]
  \begin{subfigure}
    \centering
    \includegraphics[width=5.5cm]{paper/Images/juliatime.png}
  \end{subfigure}
    \centering
  \begin{subfigure}
    \includegraphics[width=5.5cm]{paper/Images/statatime.png}
  \end{subfigure}
    \centering
  \begin{subfigure}
    \includegraphics[width=5.5cm]{paper/Images/rtime.png}
  \end{subfigure}
  \vspace{2mm}
\caption{Execution time Kernel Densities from Julia, R and Stata}
\end{figure*}

%%%%%%%%%%%%%%%%%% Figure 3
\begin{figure*}[!t]
\centering
    \includegraphics[width=16cm]{paper/Images/juliaexe.PNG}  
    \vspace{2mm}
    \caption{Execution time, speed-up and speed-up efficiency for the 25-covariate case using GlobalSearchRegression.jl}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Why GlobalSearchRegression.jl is faster than existing alternatives?}
\label{sec:whygsreg}
\subsection{JULIA platform}
\label{subsub:juliaplat}

Despite some \verb GlobalSearchRegression.jl  specific features to be examined below, our all-subset-regression algorithm benefits from the well-known Julia language efficiency for High Performance Computing tasks. \vskip 6pt

%%%%%%%%%%%%%%%%%% Table 2
\begin{table}[!h]
\centering
\tbl{Julia speed-up over STATA and R in basic functions}{
    \begin{tabular}{|l|c|c|}
    \hline
    Function & Speed-up over R & Speed-up over Stata \\
    \hline
    \hline
    recursion\_fibonacci & 251.28 & 76.92 \\
    \hline
    recursion\_quicksort & 32.36 & 48.54 \\
    \hline
    matrix\_multiply & 11.6 & 14.07 \\
    \hline
    iteration\_pi\_sum & 14.33 & 26.89 \\
    \hline
    matrix\_statistics & 7.65 & 44.92 \\
    \hline
    parse\_integers & 28.4 & 49.38 \\
    \hline
    userfunc\_mandelbrot & 175.44 & 368.42 \\
    \hline
    \hline
    Simple-Average & 74.44 & 89.88 \\
    \hline
    Weighted-Average & 12.15 & 22.01 \\
    \hline
    \end{tabular}
    }
    \caption*{Note: Weighted-average were estimated as the Ratio between total execution time for R or Stata, and Julia's total execution time -for all basic functions-. Benchmarkings were obtained using a i7-4700MQ quad-core build, with 8 GiB of DDR3 1600 Mhz RAM, under Windows 8 and running Julia 1.1.0, Stata 15 and R 3.5.3}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%

Julia JIT-compilation allows packages to run faster than those executed using interpreted or byte-compiled languages (like R or Stata-Mata). Indeed, basic functions running on Julia can be up to 251 and 368 times faster than those running in R and Stata, respectively -with an average speed-up of 75 and 90, see Table 2-.

\subsection{Parallel strategy and memory setup}
\label{subsub:parallelst}
It is well know that multicore architectures can be used to speed-up execution times through two main paradigms: data and task-parallelism \cite{zaki2001}. The preferred strategy critically depends on:
\begin{enumerate}
    \item Database structure;
    \item Algorithm serial portion; and
    \item Interthread communication costs.
\end{enumerate} 
The first discussion is about tall vs fat data. While tall databases are more suitable for data-parallelism \cite{babu2013}, fat-structures improve relative performance of task-parallelism (because tasks increase exponentially with covariates/columns in feature selection problems, see \cite{foster1994}). \vskip 6pt

Additionally, the choice between alternative paradigms takes into account the Amdahl's Law for the specific algorithm to be used. Task-parallelism is usually better for econometric and machine learning algorithms requiring some specific serial optimization paths (i.e. arima-arfima models), while data-parallelism performs better under linear-algebra solutions (i.e. OLS-family estimators, see \cite{guo2012}). \vskip 6pt

Finally, we have the problem of intercomunication costs. Data-parallelism -generally- involves intense needs of inter-thread-communication. While task-parallelism communication costs depends on Load-Balancing choices (i.e. Dynamic vs Static), they are usually lower than data-parallelism ones \footnote{At least when Static Load Balancing is implemented, because it allows for Coarse-grained granularity \cite{gordon2006}} \cite{MOREANO2017}. \vskip 6pt

For feature selection problems, pros and cons of alternative strategies often determine that available cores should be used for task parallelism. Databases are fat, data-mining algorithms can include large serial portions, and intercomunication costs can be huge for large-multicore architectures. These reasons explain why all available all-subset-regression packages use taks-parallism to speed-up execution times. \vskip 6pt

As for the memory setup, there are also alternative methodologies. First, it's necessary to choose among Static vs. Dynamic memory allocations \cite{prajapati2015}. To improve speed-up, Static "once-and-for-all" allocations are often preferred (even at a cost of higher average memory utilization). Second, shared-memory strategies must be determined. Depending on both object-size and CPU architecture -cache size and its distribution among cores-, it could be optimal to use large shared arrays or -alternatively- smaller core-specific objects. Splitting output matrices to work with smaller non-shared arrays could be useful for cache optimization purposes, but it could also entail additional communication costs and higher memory requirements \cite{ahmed2015}. In practice, feature selection algorithms usually prefer shared-arrays for high performance computing. \vskip 6pt

\verb GlobalSearchRegression.jl  (execution-time) advantages have been obtained combining:
\begin{itemize}
    \item[a)]  Task-parallelism
    \item[b)]  Static Load-Balancing
    \item[c)]  Coarse-grained granularity   
    \item[d)]  Static memory allocation
    \item[e)]  Efficient shared-array implementation
\end{itemize}

While some of these characteristics are shared with R and Stata alternatives (\verb MuMin-pdredge  and \verb GSREG,  respectively), our Static Load-Balancing algorithm outperform the round-robin R scheduling (implemented by the clusterapply function included in the \verb parallel  R-package see \cite{deb2013}) and the Shared-Array strategy significantly improves I/O performance against Stata. By construction, pure Static Load-Balancing in GlobalSearchRegression.jl avoids Round-Robin communication costs and execution gaps. This advantage overcompensate minimal\footnote{Minimal because our static scheduler guarantees that average task-complexity will not be too different among workers} load-asymmetries, associated with any static scheduling. In turn, using efficient shared-arrays to store all-subset-regression results allows us to outperform the \verb Stata-GSREG  methodology which heavily relies on slower I/O disk operations (because multiple instances must be launched to enable task-parallelism and, therefore, shared-arrays become unfeasible). \vskip 6pt

\subsection{OLS estimation}
\label{subsub:ols}
Efficient Ordinary Least Squares (OLS) algorithms rely on Linear Algebra operations (matrix decomposition, matrix inversion, etc.).\footnote{Optimization alternatives (i.e. Gradient descent), while quite inefficient for linear models, can also be used for non-linear estimations \cite{abdi2007}} The traditional $(X'X)^{-1}$ operation could be time-expensive with unstable solutions under certain conditions \cite{jameson1981}. A preferred method is the QR-decomposition developed by Francis \cite{francis1961} and Kublanovskaya \cite{kublanovskaya1962s}. The QR factorization allows us to decompose any full rank $N \times p$ matrix $\bar{X}$ as:

\begin{equation}
    X=QR
\end{equation}

where

\begin{itemize}
    \item[•] $Q$ is a $N \times p$ matrix with $Q'Q=I$  ; and
    \item[•] $R$ a $p \times p$ upper triangular matrix.
\end{itemize}

The QR decomposition is fast and provides stable numerical solutions under rank-deficient matrices. Alternative factorizations are either slower (SVD decomposition) or potentially unstable (Cholesky decomposition)\cite{agarwal2014}. \vskip 6pt

\verb GlobalSearchRegression.jl  OLS estimation through QR-decompositions outperform existing Julia alternatives (like \verb GLM.jl)  allowing for large speed-ups compared with \verb R-lm    and \verb Stata-regress  commands. The following table shows execution time differences for a 200 covariates - 1000 observations - multivariate linear regression \footnote{Execution times were calculated for alternative OLS algorithms available for all-subset-regression packages in Julia, R and Stata.}:

%%%%%%%%%%%%%%%%%% Table 3
\begin{table}[htbp]
  \centering
\tbl{Execution times for different OLS algorithms in R, Stata and Julia}{
    \begin{tabular}{|c|c|c|c|c|}
    \hline
      & GlobalSearchRegression.jl &R-lm & Stata-reg & GLM.jl \\
    \hline
    Execution time & 0.012 & 0.06 & 0.2 & 0.023 \\
    \hline
    Speed-up & 1 & 5 & 16.67 & 1.92 \\
    \hline
    \end{tabular}}
    \caption*{Note: Execution times were obtained using a i7-7500 dual-core build, with 8 GiB of DDR4 RAM, under Windows 10 and running Julia 1.1.0, Stata 13 and RStudio 3.6.0. Speed-ups are obtaining dividing each execution time by the GlobalSearchRegression.jl execution time.}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%

It must be notice that execution times are compilation-free, because all-subset-regression algorithms must perform thousand to millions of regressions where compilation time is absent (it only affects the first regression).

\section{Conclusion}
\label{sec:con}

\begin{quote}
\textit{"There are a number of areas where there would be opportunities for fruitful collaboration between econometrics and machine learning [... and] the most important area for collaboration involves causal inference"}. \cite{varian2014}
\end{quote}

As Hal Varian emphasizes, there is a need for mutual collaboration between machine learning developers/practitioners and econometricians. In this paper we describe a research-project aimed at building bridges between machine learning and econometric worlds and introduce the main characteristics of its first outcome: a Julia-native all-subset regression algorithm (\verb GlobalSearchRegression.jl)  which runs up to 3165 and 197 times faster than existing Stata and R alternatives, respectively. \vskip 6pt

Throughout the paper, it has been shown that execution-time gains are explained by multiple efficient strategies combined in \verb GlobalSearchRegression.jl  (i.e. task parallelism, static load-balancing, coarse-grained granularity, static memory allocation, efficient shared array implementation, and OLS estimation using neat QR decompositions). However, the main 'explanatory variable' is the impressive speed-up in atomic operations obtained using the Julia language. \vskip 6pt

Notwithstanding, increasing availability of Big and -more challenging- Fat-data, force us to go beyond pure all-subset-regression approaches and combine it with machine learning feature selection algorithms. Work in progress include a new hybrid package merging LASSO capabilities, all-subset-regression robustness and K-fold cross validation strengths.

\section{Acknowledgments}
\label{sec:ackno}
This research benefited from the financial support of 1) the National Scientific and Technical Research Council and the YPF-Foundation (PIO CONICET-YPF 13320150100020CO); and 2) the National Agency for Scientific and Technological Promotion (PICT-2017-0867). We would also like to thank PhD. Jorge Carrera for his technical assistance on Big-data econometric algorithms.
\input{bib.tex}

\end{document}

### 2019-07-11 paper/paper2.tex
Create paper2.tex

--- 2019-07-07 juliacon2019proceedings/paper/paper.tex
@@
 \usepackage{algorithm,amsmath,xcolor,caption}
-\usepackage[noend]{algpseudocode}
+%\usepackage[noend]{algpseudocode}
 \usepackage{hyperref}
@@
 \captionsetup[algorithm]{labelfont={bf,lightblue}, textfont={it}}
-\renewcommand{\thealgorithm}{\arabic{algorithm}}
+%\renewcommand{\thealgorithm}{\arabic{algorithm}}
 \usepackage{array}
@@
 \section{Introduction}
+\label{sec:introduction}
 While allowing for better and more accurate analysis (and forecasts), fat-data availability generates a revival of Bellman’s \cite{Bellman1961} -and newer- high-dimensionality concerns:
@@
 \begin{figure}[h]
-\centerline{\includegraphics[width=10cm]{paper/Images/flowchart.png}}
+\centerline{\includegraphics[width=10cm]{flowchart.png}}
 \caption{ GlobalSearchRegression.jl Structure Flowchart}
@@
     \centering
-    \includegraphics[width=5.5cm]{paper/Images/juliatime.png}
+    \includegraphics[width=5.5cm]{juliatime.png}
   \end{subfigure}
@@
   \begin{subfigure}
-    \includegraphics[width=5.5cm]{paper/Images/statatime.png}
+    \includegraphics[width=5.5cm]{statatime.png}
   \end{subfigure}
@@
   \begin{subfigure}
-    \includegraphics[width=5.5cm]{paper/Images/rtime.png}
+    \includegraphics[width=5.5cm]{rtime.png}
   \end{subfigure}
@@
 \centering
-    \includegraphics[width=16cm]{paper/Images/juliaexe.PNG}  
+    \includegraphics[width=16cm]{juliaexe.PNG}  
     \vspace{2mm}

### 2019-07-11 paper/paper.tex
Update paper.tex

--- 2019-07-11 paper/paper2.tex
@@
 \label{sec:introduction}
-While allowing for better and more accurate analysis (and forecasts), fat-data availability generates a revival of Bellman’s \cite{Bellman1961} -and newer- high-dimensionality concerns:
+While allowing for better and more accurate analysis (and forecasts), fat-data availability generates a revival of Bellman’s -and newer- high-dimensionality concerns:
 \begin{enumerate}
-    \item Exponential increase in required information and execution time \cite{Yu2003} ;
-    \item Overfitting risk \cite{Defernez1999}; 
-    \item Less-informative euclidean distances \cite{Aggarwal2001}; and
-    \item Unfeasible estimators \cite{Buhlmann2011}. 
+    \item Exponential increase in required information and execution time;
+    \item Overfitting risk ; 
+    \item Less-informative euclidean distances; and
+    \item Unfeasible estimators. 
 \end{enumerate}
 
-Notwithstanding, the advantage of having thousands/millions of features to deal with complex phenomena stimulates an unprecedented number of methodological -and technological- improvements to manage the ‘curse of dimensionality’ \cite{Bolon2016}.
+Notwithstanding, the advantage of having thousands/millions of features to deal with complex phenomena stimulates an unprecedented number of methodological -and technological- improvements to manage the ‘curse of dimensionality’.
 \vskip 6pt
@@
 In Economics, this process has a dual approach with machine-learning (ML) and econometric (EC) algorithms emerging for different purposes: the former for prediction/forecasts (focusing on $\hat{y}$) and the latter for estimation/causal inference (interested in $\hat{\beta}$).
-Alternatively, the same distinction can be expressed in Diebold’s terms as non-causal vs causal prediction (see \cite{athey2015}), where ML algorithms are designed to reduce prediction sampling-risks -i.e.
+Alternatively, the same distinction can be expressed in Diebold’s terms as non-causal vs causal prediction, where ML algorithms are designed to reduce prediction sampling-risks -i.e.
 learning through cross-validation techniques- and EC methods to identify unbiased multivariate relationships -i.e.
@@
 
-In turn, ML feature selection algorithms can be classified into three different families: Filters, Wrappers and Embedded -depending on whether they use some classifier/response variable information or not, or how variable selection is made along with the learning process, see \cite{CHANDRASHEKAR201416}.
-Similarly, most EC dimensionality reduction approaches can be classified into three different groups: Exhaustive, General-to-Specific and Specific-to-General -depending on the search pattern; see \cite{gluzmann2015}.
+In turn, ML feature selection algorithms can be classified into three different families: Filters, Wrappers and Embedded -depending on whether they use some classifier/response variable information or not, or how variable selection is made along with the learning process.
+Similarly, most EC dimensionality reduction approaches can be classified into three different groups: Exhaustive, General-to-Specific and Specific-to-General -depending on the search pattern.
 \vskip 6pt
 
-Despite significant improvements in recent econometric developments -like PCGIVE/Autometrics or Retina algorithms, which combine some ML and EC characteristics-, available alternatives fails to fully exploit cross-validation and model averaging capabilities -see \cite{Doornik09autometrics}, \cite{perezamaral2003}, \cite{DAVIDSON1981}, \cite{derksen1992}, \cite{marinucci2008}, \cite{herwartz2010}, and \cite{castle2006}.
+Despite significant improvements in recent econometric developments -like PCGIVE/Autometrics or Retina algorithms, which combine some ML and EC characteristics-, available alternatives fails to fully exploit cross-validation and model averaging capabilities.
 \vskip 6pt
 
-Conversely, newer ML algorithms -like Convolutional Neural Networks or Bootstrap-Based LASSO, which improve complex non-linear adjustment or model selection under regularization schemes- achieved unprecedented forecast accuracy but disregarding model interpretability and/or parameter estimation issues -i.e omitting residual and coefficient tests; see \cite{Bzdok2018}.
+Conversely, newer ML algorithms -like Convolutional Neural Networks or Bootstrap-Based LASSO, which improve complex non-linear adjustment or model selection under regularization schemes- achieved unprecedented forecast accuracy but disregarding model interpretability and/or parameter estimation issues -i.e omitting residual and coefficient tests.
 \vskip 6pt
 
-Following Varian’s \cite{varian2014} advices, about ML and EC complementarities -i.e.
-merging algorithms from different families to reduce both sampling and model uncertainty-, we are developing a novel multi-layer-multi-algorithm methodology combining two reinforcing paradigms: The LSE “Testimation” approach -to obtain information about residual properties, see \cite{abramovich2006}- and the Bayesian-like “Double-model averaging” -across different covariates and sub-samples, see \cite{hoetening1999}.
+Following Varian’s advices, about ML and EC complementarities -i.e.
+merging algorithms from different families to reduce both sampling and model uncertainty-, we are developing a novel multi-layer-multi-algorithm methodology combining two reinforcing paradigms: The LSE “Testimation” approach -to obtain information about residual properties- and the Bayesian-like “Double-model averaging” -across different covariates and sub-samples.
 This methodology includes five complementary layers -handling cross-section, time series and panel data-: 1) Pre-processing: with outlier detection, missing values identification, seasonal adjustment and normalization/standardization functions; 2) Feature extraction: creation of logs, squares, inverses and interactions from selected variables; 3) Feature pre-selection: using filter and embedded ML algorithms like CFS, Variance threshold and LASSO functions; 4) Final feature selection: with a modified all-subset regression approach, including residual tests and model averaging capabilities; 5) Post-estimation fine-tuning: coefficient re-evaluation through cross-validation techniques and model averaging across different k-fold results.

### 2019-07-12 paper/paper.tex
Update paper.tex
Add files via upload

--- 2019-07-11 paper/paper2.tex
@@
 \documentclass{juliacon}
+\usepackage{amsmath}
 \setcounter{page}{1}
 
-% Additional packages used%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\usepackage{algorithm,amsmath,xcolor,caption}
-%\usepackage[noend]{algpseudocode}
-\usepackage{hyperref}
-\DeclareMathOperator{\sgn}{sign}
-\DeclareCaptionFont{lightblue}{\color{black}}
-\captionsetup[algorithm]{labelfont={bf,lightblue}, textfont={it}}
-%\renewcommand{\thealgorithm}{\arabic{algorithm}}
-\usepackage{array}
-\newcolumntype{C}[1]{>{\centering\arraybackslash}m{#1}}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{document}
+\input{header}
+\maketitle
+\begin{abstract}
 
-\begin{document}
-
-\input{header}
-
-\maketitle
-
-\begin{abstract}
 The aim of this paper is twofold.
@@
 As other available alternatives, this algorithm allows researchers to obtain the best model specification among all possible covariate combinations - in terms of user defined information criteria-, but up to 3165 and 197 times faster than STATA and R alternatives, respectively.
+
 \end{abstract}
@@
 \section{Introduction}
-\label{sec:introduction}
 While allowing for better and more accurate analysis (and forecasts), fat-data availability generates a revival of Bellman’s \cite{Bellman1961} -and newer- high-dimensionality concerns:
@@
 \label{sec:packagefeatures}
-%
 
@@
 \vskip 6pt
+\break
 
 %%%%%%%%%%%%%%%%%%%%%%% Algorithm 1
-\begin{algorithm}[ht]
-  \scriptsize
-  \caption{module Core.jl}
+\begin{listing}
+\hline
+\center{ \textbf{Pseudo-code for module Core.jl}}
+\vspace{2mm}
+\hline
   \begin{enumerate}
@@
 
-\textbf{end} module \verb Core.jl .
-\end{algorithm}
+\begin{flushleft}
+\textbf{end} module \verb Core.jl . \hfill
+\end{flushleft}
+\hline
+\end{listing}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{Comparative performance against \textit{R} and \textit{STATA}}
@@
 \begin{table*}[!t]
-\tabcolsep1pt
 \centering
 \tbl{Average execution time and speed-up metrics -over 5 runs-}{
-    \scalebox{0.8}{
-    \begin{tabular}{|C{1cm}|C{1cm}|C{1cm}|C{1.5cm}|C{1.5cm}|C{1.5cm}|C{1.5cm}|C{1.5cm}|C{1.5cm}|C{1.5cm}|C{1.5cm}|}
+\scalebox{0.85}{
+    \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
     \hline
-    \multirow{Cov.} & \multirow{Obs} & \multirow{Threads} & \multicolumn{3}{c|}{Execution time (in seconds)} & \multicolumn{3}{c|}{Parallel Speed-up} & \multicolumn{2}{c|}{Julia Speed-up} \\
+    \multirow{Cov.} & \multirow{Obs} & \multirow{Threads} & \multicolumn{3}{|c|}{Execution time (in seconds)} & \multicolumn{3}{
+    c|}{Parallel Speed-up} & \multicolumn{2}{|c|}{Julia Speed-up} \\
 \cline{4-11}      &   &   & Julia & R & Stata & Julia & R & Stata & Over R & Over Stata \\
@@
     \hline 
-    \end{tabular}    }   }
+    \end{tabular}}}
 \end{table*}
@@
 Despite some \verb GlobalSearchRegression.jl  specific features to be examined below, our all-subset-regression algorithm benefits from the well-known Julia language efficiency for High Performance Computing tasks.
-\vskip 6pt
+
+\vspace{-2mm}
 
@@
     \hline
+    \multicolumn{3}{p{8.5cm}}{Note: Weighted-average were estimated as the Ratio between total execution time for R or Stata, and Julia's total execution time.
+Benchmarkings were obtained using a i7-4700MQ quad-core build, with 8 GiB of DDR3 1600 Mhz RAM, under Windows 8 and running Julia 1.1.0, Stata 15 and R 3.5.3}
     \end{tabular}
     }
-    \caption*{Note: Weighted-average were estimated as the Ratio between total execution time for R or Stata, and Julia's total execution time -for all basic functions-.
-Benchmarkings were obtained using a i7-4700MQ quad-core build, with 8 GiB of DDR3 1600 Mhz RAM, under Windows 8 and running Julia 1.1.0, Stata 15 and R 3.5.3}
 \end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\break
 
@@
 \verb GlobalSearchRegression.jl  OLS estimation through QR-decompositions outperform existing Julia alternatives (like \verb GLM.jl)  allowing for large speed-ups compared with \verb R-lm    and \verb Stata-regress  commands.
-The following table shows execution time differences for a 200 covariates - 1000 observations - multivariate linear regression \footnote{Execution times were calculated for alternative OLS algorithms available for all-subset-regression packages in Julia, R and Stata.}:
+Table 3 shows execution time differences for a 200 covariates - 1000 observations - multivariate linear regression \footnote{Execution times were calculated for alternative OLS algorithms available for all-subset-regression packages in Julia, R and Stata.}.
+\vskip 6pt
 
+It must be notice that execution times are compilation-free, because all-subset-regression algorithms must perform thousand to millions of regressions where compilation time is absent (it only affects the first regression).
+\vskip 6pt
+
+\break
 %%%%%%%%%%%%%%%%%% Table 3
-\begin{table}[htbp]
+\begin{table}[!h]
   \centering
-\tbl{Execution times for different OLS algorithms in R, Stata and Julia}{
+\tbl{Execution times for OLS algorithms in R, Stata and Julia}{
     \begin{tabular}{|c|c|c|c|c|}
@@
     \hline
-    Execution time & 0.012 & 0.06 & 0.2 & 0.023 \\
+    Exec. time & 0.012 & 0.06 & 0.2 & 0.023 \\
     \hline
@@
     \hline
+    \multicolumn{5}{p{8.5cm}}{Note: Execution times were obtained using a i7-7500 dual-core build, with 8 GiB of DDR4 RAM, under Windows 10 and running Julia 1.1.0, Stata 13 and RStudio 3.6.0.
+Speed-ups are obtaining dividing each execution time by the GlobalSearchRegression.jl execution time.} \\
     \end{tabular}}
-    \caption*{Note: Execution times were obtained using a i7-7500 dual-core build, with 8 GiB of DDR4 RAM, under Windows 10 and running Julia 1.1.0, Stata 13 and RStudio 3.6.0.
-Speed-ups are obtaining dividing each execution time by the GlobalSearchRegression.jl execution time.}
 \end{table}
@@
 
-It must be notice that execution times are compilation-free, because all-subset-regression algorithms must perform thousand to millions of regressions where compilation time is absent (it only affects the first regression).
-
 \section{Conclusion}
 \label{sec:con}
-
+\vspace{2mm}
 \begin{quote}
@@
 \end{quote}
+\vspace{2mm}
 
@@
 Jorge Carrera for his technical assistance on Big-data econometric algorithms.
+
 \input{bib.tex}
@@
 \end{document}
+
+% Inspired by the International Journal of Computer Applications template

### 2019-07-12 paper/paper.tex
Update paper.tex

@@
 \section{Introduction}
+\label{sec:introduction}
+
 While allowing for better and more accurate analysis (and forecasts), fat-data availability generates a revival of Bellman’s \cite{Bellman1961} -and newer- high-dimensionality concerns:

### 2019-07-12 paper/paper.tex
Update paper.tex

--- 2019-07-11 paper/paper.tex
@@
 \documentclass{juliacon}
+\usepackage{amsmath}
 \setcounter{page}{1}
 
-% Additional packages used%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\usepackage{algorithm,amsmath,xcolor,caption}
-%\usepackage[noend]{algpseudocode}
-\usepackage{hyperref}
-\DeclareMathOperator{\sgn}{sign}
-\DeclareCaptionFont{lightblue}{\color{black}}
-\captionsetup[algorithm]{labelfont={bf,lightblue}, textfont={it}}
-%\renewcommand{\thealgorithm}{\arabic{algorithm}}
-\usepackage{array}
-\newcolumntype{C}[1]{>{\centering\arraybackslash}m{#1}}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{document}
+\input{header}
+\maketitle
+\begin{abstract}
 
-\begin{document}
-
-\input{header}
-
-\maketitle
-
-\begin{abstract}
 The aim of this paper is twofold.
-The first one is to describe a novel research-project aimed at building bridges between machine learning and econometric worlds.
+The first one is to describe a novel research-project designed for building bridges between machine learning and econometric worlds.
 The second one is to introduce the main characteristics and comparative performance of the first Julia-native all-subset regression algorithm included in \verb GlobalSearchRegression.jl  (v1.0.3).
 As other available alternatives, this algorithm allows researchers to obtain the best model specification among all possible covariate combinations - in terms of user defined information criteria-, but up to 3165 and 197 times faster than STATA and R alternatives, respectively.
+
 \end{abstract}
@@
 \section{Introduction}
-\label{sec:introduction}
 While allowing for better and more accurate analysis (and forecasts), fat-data availability generates a revival of Bellman’s -and newer- high-dimensionality concerns:
 \begin{enumerate}
-    \item Exponential increase in required information and execution time;
-    \item Overfitting risk ; 
+    \item Exponential increase in required information and execution time ;
+    \item Overfitting risk; 
     \item Less-informative euclidean distances; and

### 2019-07-14 src/Output/decorations/latex/tex/tpl.tex
Several changes

\documentclass{article}

\usepackage{GSReg-style}

\usepackage[utf8]{inputenc} 
\usepackage[T1]{fontenc}    
\usepackage{hyperref}       
\usepackage{url}            
\usepackage{booktabs}       
\usepackage{amsfonts}       
\usepackage{nicefrac}       
\usepackage{microtype}

\title{Methodology, data and results}

\author{
  David S.~Hippocampus \\
  Department of Computer Science\\
  Cranberry-Lemon University\\
  Pittsburgh, PA 15213 \\
  \texttt{hippo@cs.cranberry-lemon.edu} \\
  \And
 Elias D.~Striatum \\
  Department of Electrical Engineering\\
  Mount-Sheikh University\\
  Santa Narimana, Levand \\
  \texttt{stariate@ee.mount-sheikh.edu} \\
}

\begin{document}
\maketitle

\section{Introduction}

GlobalSearchRegression is both the world-fastest all-subset-regression command (a widespread tool for automatic model/feature selection) and a first-step to develop a coeherent framework to merge Machine Learning and Econometric algorithms.

Written in Julia, it is a High Performance Computing version of the Stata-gsreg command (get the original code here). In a multicore personal computer (we use a Threadripper 1950x build for benchmarks), it runs up-to 100 times faster than the original Stata-code and up-to 10 times faster than well-known R-alternatives (pdredge).

Notwithstanding, GlobalSearchRegression main focus is not only on execution-times but also on progressively combining Machine Learning algorithms with Econometric diagnosis tools into a friendly Graphical User Interface (GUI) to simplify embarrassingly parallel quantitative-research.

In a Machine Learning environment (e.g. problems focusing on predictive analysis / forecasting accuracy) there is an increasing universe of “training/test” algorithms (many of them showing very interesting performance in Julia) to compare alternative results and find-out a suitable model.

However, problems focusing on causal inference require five important econometric features: 1) Parsimony (to avoid very large atheoretical models); 2) Interpretability (for causal inference, rejecting “intuition-loss” transformation and/or complex combinations); 3) Across-models sensitivity analysis (uncertainty is the only certainty; parameter distributions are preferred against “best-model” unique results); 4) Robustness to time series and panel data information (preventing the use of raw bootstrapping or random subsample selection for training and test sets); and 5) advanced residual properties (e.g. going beyond the i.i.d assumption and looking for additional panel structure properties -for each model being evaluated-, which force a departure from many traditional machine learning algorithms).

For all these reasons, researchers increasingly prefer advanced all-subset-regression approaches, choosing among alternative models by means of in-sample and/or out-of-sample criteria, model averaging results, bayesian priors for theoretical bounds on covariates coefficients and different residual constraints. While still unfeasible for large problems (choosing among hundreds of covariates), hardware and software innovations allow researchers to implement this approach in many different scientific projects, choosing among one billion models in a few hours using standard personal computers.

\section{Methodology}

\section{Variables}

Database used is shown in table 1:

\begin{table}[!h]
  \centering
  \caption{Descriptive Statistics for the main dataset}
    \begin{tabular}{|p{5cm}|c|c|c|c|c|c|}
    \hline
    Variable & Obs. & Mean & Sd & Max & Min & \% missing \\
    \hline
    \hline
    {{#var_summary}}
    {{name}} & {{nobs}} & {{mean}} & {{std}} & {{max}} & {{min}} & {{miss}}\% \\ 
    \hline
    {{/var_summary}}
    \end{tabular}
\end{table}

{{#lasso}}
\section{Regularization}

Lasso regression is a type of linear regression that uses shrinkage. Shrinkage is where data values are shrunk towards a central point, like the mean. The lasso procedure encourages simple, sparse models (i.e. models with fewer parameters). This particular type of regression is well-suited for models showing high levels of muticollinearity or when you want to automate certain parts of model selection, like variable selection/parameter elimination.

Lasso regression performs L1 regularization, which adds a penalty equal to the absolute value of the magnitude of coefficients. This type of regularization can result in sparse models with few coefficients; Some coefficients can become zero and eliminated from the model. Larger penalties result in coefficient values closer to zero, which is the ideal for producing simpler models. On the other hand, L2 regularization (e.g. Ridge regression) doesn’t result in elimination of coefficients or sparse models. This makes the Lasso far easier to interpret than the Ridge.

\begin{equation}
    \sum_{n=1}^{n}(y_i - \sum_{j}x_{ij}\beta_{j})^2 + \lambda \sum_{j=1}^p|\beta_{j}|
\end{equation}

Which is the same as minimizing the sum of squares with constraint $\sum \beta_{j}≤ s$. Some of the $\beta_s$ are shrunk to exactly zero, resulting in a regression model that’s easier to interpret.

A tuning parameter, $\lambda$ controls the strength of the L1 penalty. $\lambda$ is basically the amount of shrinkage:

When $ \lambda = 0$, no parameters are eliminated. The estimate is equal to the one found with linear regression.
As $\lambda$ increases, more and more coefficients are set to zero and eliminated (theoretically, when $\lambda = \infty$, all coefficients are eliminated).
As $\lambda$ increases, bias increases.

As $\lambda$ decreases, variance increases.

If an intercept is included in the model, it is usually left unchanged.

LASSO regression is shown in the following table:

\begin{table}[!h]
  \centering
  \caption{LASSO Regression results}
    \begin{tabular}{l c}
    \hline
                 &       \\
    VARIABLES    &  {{indep}} \\
    \hline
    \hline
    {{#summary}}
    {{var}}  & {{coef}} \\
    {{/summary}}
    Constant &  \\
    \hline
    \hline
    Observations &  \\
    \lambda      &  \\
    R-squared    &  \\
    \hline
    \multicolumn{2}{c}{Standard errors in parentheses} \\
    \multicolumn{2}{c}{*** p<0.01, ** p<0.05, * p<0.1} \\
    \end{tabular}
  \label{tab:addlabel}
\end{table}
{{/lasso}}
\section{Gsreg}

\subsection{All sub-subset regression Best Model}

\subsection{All sub-subset regression Model Averaging}

\subsection{Coefficient, t-test, information criteria distributions and main statistics}

combinar coefficient, t-test (contour), kernel del criterio con y sin coefficient

\section{k-fold cross-validation}

\bibliographystyle{unsrt}  
\begin{thebibliography}{1}

\bibitem{gsreg2019}
Panigo Demian, Glüzmann Pablo, Mauri Ungaro Adan, Mari Valentín and Monzón Nicolás. 2019.
\newblock \textit{GlobalSearchRegression.jl: Building bridges between Machine Learning and Econometrics in Fat-Data scenarios}.
\newblock The Journal of Open Source Software, X(X), XXX--XXX. DOI:xxxxx.x.x.x.x.xxx

\end{thebibliography}

\end{document}

### 2019-07-14 src/AllSubsetRegression/AllSubsetRegression.jl

@@ -5,11 +5,12 @@ module AllSubsetRegression
     using Distributed, Distributions, SharedArrays, LinearAlgebra
     using ..GlobalSearchRegression
 
-    export ols, ols!, AllSubsetRegressionResult
+    export ols, ols!, to_string, AllSubsetRegressionResult
     
     include("const.jl")
     include("strings.jl")
     include("utils.jl")
     include("structs/result.jl")
+    include("core.jl")
     include("estimators/ols.jl")
 end

### 2019-07-14 src/AllSubsetRegression/core.jl

@@ -1,0 +1,88 @@
+
+"""
+to_string
+"""
+function to_string(data::GlobalSearchRegression.GSRegData, result::AllSubsetRegressionResult)
+    datanames_index = create_datanames_index(result.datanames)
+
+    out = ""
+    out *= @sprintf("\n")
+    out *= @sprintf("══════════════════════════════════════════════════════════════════════════════\n")
+    out *= @sprintf("                              Best model results                              \n")
+    out *= @sprintf("══════════════════════════════════════════════════════════════════════════════\n")
+    out *= @sprintf("                                                                              \n")
+    out *= @sprintf("                                     Dependent variable: %s                   \n", data.depvar)
+    out *= @sprintf("                                     ─────────────────────────────────────────\n")
+    out *= @sprintf("                                                                              \n")
+    out *= @sprintf(" Selected covariates                 Coef.")
+    if result.ttest
+        out *= @sprintf("        Std.         t-test")
+    end
+    out *= @sprintf("\n")
+    out *= @sprintf("──────────────────────────────────────────────────────────────────────────────\n")
+
+    cols = get_selected_variables(Int64(result.bestresult_data[datanames_index[:index]]), data.expvars, data.intercept)
+
+    for pos in cols
+        varname = data.expvars[pos]
+        out *= @sprintf(" %-35s", varname)
+        out *= @sprintf(" %-10f", result.bestresult_data[datanames_index[Symbol(string(varname, "_b"))]])
+        if result.ttest
+            out *= @sprintf("   %-10f", result.bestresult_data[datanames_index[Symbol(string(varname, "_bstd"))]])
+            out *= @sprintf("   %-10f", result.bestresult_data[datanames_index[Symbol(string(varname, "_t"))]])
+        end
+        out *= @sprintf("\n")
+    end
+
+    out *= @sprintf("──────────────────────────────────────────────────────────────────────────────\n")
+    out *= @sprintf(" Observations                        %-10d\n", result.bestresult_data[datanames_index[:nobs]])
+    out *= @sprintf(" Adjusted R²                         %-10f\n", result.bestresult_data[datanames_index[:r2adj]])
+    out *= @sprintf(" F-statistic                         %-10f\n", result.bestresult_data[datanames_index[:F]])
+    for criteria in result.criteria
+        if AVAILABLE_CRITERIA[criteria]["verbose_show"]
[…]

### 2019-07-14 src/AllSubsetRegression/estimators/ols.jl

@@ -322,90 +322,3 @@ function execute_row!(
     end
     
 end
-
-# Todo: REMOVE
-function to_string(data)
-    result = data.results[1]
-    datanames_index = create_datanames_index(result.datanames)
-
-    out = ""
-    out *= @sprintf("\n")
-    out *= @sprintf("══════════════════════════════════════════════════════════════════════════════\n")
-    out *= @sprintf("                              Best model results                              \n")
-    out *= @sprintf("══════════════════════════════════════════════════════════════════════════════\n")
-    out *= @sprintf("                                                                              \n")
-    out *= @sprintf("                                     Dependent variable: %s                   \n", data.depvar)
-    out *= @sprintf("                                     ─────────────────────────────────────────\n")
-    out *= @sprintf("                                                                              \n")
-    out *= @sprintf(" Selected covariates                 Coef.")
-    if result.ttest
-        out *= @sprintf("        Std.         t-test")
-    end
-    out *= @sprintf("\n")
-    out *= @sprintf("──────────────────────────────────────────────────────────────────────────────\n")
-
-    cols = get_selected_variables(Int64(result.bestresult_data[datanames_index[:index]]), data.expvars, data.intercept)
-
-    for pos in cols
-        varname = data.expvars[pos]
-        out *= @sprintf(" %-35s", varname)
-        out *= @sprintf(" %-10f", result.bestresult_data[datanames_index[Symbol(string(varname, "_b"))]])
-        if result.ttest
-            out *= @sprintf("   %-10f", result.bestresult_data[datanames_index[Symbol(string(varname, "_bstd"))]])
-            out *= @sprintf("   %-10f", result.bestresult_data[datanames_index[Symbol(string(varname, "_t"))]])
-        end
-        out *= @sprintf("\n")
-    end
-
-    out *= @sprintf("──────────────────────────────────────────────────────────────────────────────\n")
-    out *= @sprintf(" Observations                        %-10d\n", result.bestresult_data[datanames_index[:nobs]])
-    out *= @sprintf(" Adjusted R²                         %-10f\n", result.bestresult_data[datanames_index[:r2adj]])
-    out *= @sprintf(" F-statistic                         %-10f\n", result.bestresult_data[datanames_index[:F]])
-    for criteria in result.criteria
-        if AVAILABLE_CRITERIA[criteria]["verbose_show"]
[…]

### 2019-07-14 src/AllSubsetRegression/structs/result.jl

@@ -25,7 +25,7 @@ mutable struct AllSubsetRegressionResult <: GlobalSearchRegression.GSRegResult
             residualtest,
             orderresults
         )
-        
+
         new(datanames, modelavg_datanames, nothing, nothing, nothing, outsample, criteria, modelavg, ttest, residualtest, orderresults, 0)
     end
 end

### 2019-07-14 src/AllSubsetRegression/utils.jl

@@ -7,7 +7,7 @@ function create_result(data, outsample, criteria, ttest, modelavg, residualtest,
         push!(criteria, :r2adj)
     end
 
-    if :rmseout ∉ criteria && outsample != OUTSAMPLE_DEFAULT
+    if :rmseout ∉ criteria && outsample > 0
         push!(criteria, :rmseout)
     end
 

### 2019-07-14 src/FeatureExtraction/core.jl

@@ -1,28 +1,3 @@
-function featureextraction!(
-    data::GlobalSearchRegression.GSRegData;
-    fe_sqr::Union{Nothing, String, Symbol, Array{String}, Array{Symbol}}=nothing,
-    fe_log::Union{Nothing, String, Symbol, Array{String}, Array{Symbol}}=nothing,
-    fe_inv::Union{Nothing, String, Symbol, Array{String}, Array{Symbol}}=nothing,
-    fe_lag::Union{Nothing, Array}=nothing,
-    interaction::Union{Nothing, Array}=nothing,
-    removemissings=REMOVEMISSINGS_DEFAULT
-    )
-
-    new_data = featureextraction(
-        data,
-        fe_sqr=fe_sqr,
-        fe_log=fe_log,
-        fe_inv=fe_inv,
-        fe_lag=fe_lag,
-        interaction=interaction,
-        removemissings=removemissings
-    )
-
-    data = GlobalSearchRegression.copy_data!(new_data, data)
-
-    return data
-end
-
 function featureextraction(
     data::GlobalSearchRegression.GSRegData;
     fe_sqr::Union{Nothing, String, Symbol, Array{String}, Array{Symbol}}=nothing,
@@ -33,39 +8,70 @@ function featureextraction(
     removemissings=REMOVEMISSINGS_DEFAULT
     )
 
-    fe_data = GlobalSearchRegression.copy_data(data)
+    new_data = GlobalSearchRegression.copy_data(data)
+
+    new_data = featureextraction(
+        new_data,
+        fe_sqr=fe_sqr,
+        fe_log=fe_log,
+        fe_inv=fe_inv,
+        fe_lag=fe_lag,
+        interaction=interaction,
+        removemissings=removemissings
+    )
+
+    return new_data
+end
+
+function featureextraction!(
+    data::GlobalSearchRegression.GSRegData;
+    fe_sqr::Union{Nothing, String, Symbol, Array{String}, Array{Symbol}}=nothing,
+    fe_log::Union{Nothing, String, Symbol, Array{String}, Array{Symbol}}=nothing,
+    fe_inv::Union{Nothing, String, Symbol, Array{String}, Array{Symbol}}=nothing,
+    fe_lag::Union{Nothing, Array}=nothing,
+    interaction::Union{Nothing, Array}=nothing,
+    removemissings=REMOVEMISSINGS_DEFAULT
+    )
+
[…]

### 2019-07-14 src/FeatureExtraction/utils.jl

@@ -2,7 +2,7 @@
 Parse fe variables
 """
 function parse_fe_variables(fe_vars, expvars; depvar=nothing, is_pair=false)
-    valid_vars = expvars
+    valid_vars = copy(expvars)
 
     if depvar != nothing
         append!(valid_vars, [depvar])
@@ -125,46 +125,80 @@ function data_add_fe_lag(data, fe_vars)
     nobs = size(data.expvars_data, 1)
     postfix = "_l"
     csis = (data.panel != nothing) ? unique(data.panel_data) : [nothing]
-    
+    depvar_enabled = false
+
     for var in fe_vars
-        col = GlobalSearchRegression.get_column_index(var[1], data.expvars)
-        num_cols = 0
-        for i = 1:var[2]
-            if !(Symbol(string(var[1], postfix, i)) in data.expvars)
-                num_cols = num_cols + 1
-            end
-        end
-        var_data = Array{Union{Missing, data.datatype}}(missing, nobs, num_cols)
-        m = 1
-        for i = 1:var[2]
-            expvar = Symbol(string(var[1], postfix, i))
-            
-            col_added = false
-            for csi in csis
-                rows = (csi != nothing) ? findall(x->x == csi, data.panel_data) : collect(1:1:nobs)
-                num_rows = size(rows, 1)
-                if !(expvar in data.expvars)
-                    var_data[rows[1]:rows[1]+num_rows-1, m] .= lag(data.expvars_data[rows[1]:rows[1]+num_rows-1, col], i)
-                    col_added = true
-                else
-                    n = GlobalSearchRegression.get_column_index(expvar, data.expvars)
-                    data.expvars_data[rows[1]:rows[1]+num_rows-1, n].= lag(data.expvars_data[rows[1]:rows[1]+num_rows-1, col], i)
+        if var in data.expvars
+            col = GlobalSearchRegression.get_column_index(var[1], data.expvars)
+            num_cols = 0
+            for i = 1:var[2]
+                if !(Symbol(string(var[1], postfix, i)) in data.expvars)
+                    num_cols = num_cols + 1
                 end
             end
-            if col_added
-                m = m + 1
-            end
+            var_data = Array{Union{Missing, data.datatype}}(missing, nobs, num_cols)
+            m = 1
+            for i = 1:var[2]
+                expvar = Symbol(string(var[1], postfix, i))
+                
+                col_added = false
+                for csi in csis
[…]

### 2019-07-14 src/GlobalSearchRegression.jl

@@ -1,35 +1,26 @@
 module GlobalSearchRegression
 
-using DataFrames,
-      Distributions,
-      Distributed,
-      Printf,
-      SharedArrays,
-      LinearAlgebra,
-      DelimitedFiles
-
 include("structs/gsreg_data.jl")
 include("datatypes/gsreg_result.jl")
+include("const.jl")
+include("strings.jl")
 include("utils.jl")
 
-#include("strings.jl")
-#include("interface.jl")
-#include("core.jl")
 include("Preprocessing/Preprocessing.jl")
 include("FeatureExtraction/FeatureExtraction.jl")
-include("CrossValidation/CrossValidation.jl")
 include("PreliminarySelection/PreliminarySelection.jl")
-include("OutputDecoration/OutputDecoration.jl")
 include("AllSubsetRegression/AllSubsetRegression.jl")
+include("CrossValidation/CrossValidation.jl")
+include("Output/Output.jl")
 
 using ..Preprocessing
 using ..FeatureExtraction
 using ..PreliminarySelection
 using ..AllSubsetRegression
-using ..OutputDecoration
+using ..Output
 
 export GSRegData, GSRegResult
 
-export Preprocessing, FeatureExtraction, PreliminarySelection, OutputDecoration
+export Preprocessing, FeatureExtraction, PreliminarySelection, Output
 
 end

### 2019-07-14 src/Output/Output.jl

@@ -1,0 +1,14 @@
+module Output
+    using DelimitedFiles, Printf
+    using ..GlobalSearchRegression
+
+    export csv, summary, latex
+
+    include("const.jl")
+    include("strings.jl")
+    include("utils.jl")
+    include("decorations/csv/csv.jl")
+    include("decorations/summary/summary.jl")
+    include("decorations/latex/latex.jl")
+    include("core.jl")
+end

### 2019-07-14 src/Output/core.jl

@@ -1,0 +1,1 @@
+Base.show(io::IO, data::GlobalSearchRegression.GSRegData) = summary(data)

### 2019-07-14 src/Output/decorations/csv/csv.jl

@@ -1,0 +1,30 @@
+function csv(data::GlobalSearchRegression.GSRegData, filename::String; resultnum::Int64=1)
+    csv(data, filename=filename, resultnum=resultnum)
+end
+
+function csv(data::GlobalSearchRegression.GSRegData; filename::Union{Nothing, String}=nothing, resultnum::Int64=1)
+    csv(data, data.results[resultnum], filename=filename)
+end
+
+function csv(data::GlobalSearchRegression.GSRegData, result::GlobalSearchRegression.AllSubsetRegression.AllSubsetRegressionResult, filename::String)
+    csv(data, result, filename=filename)
+end
+
+function csv(data::GlobalSearchRegression.GSRegData, result::GlobalSearchRegression.AllSubsetRegression.AllSubsetRegressionResult; filename::Union{Nothing, String}=nothing)
+    header = []
+    for dataname in result.datanames
+        push!(header, String(dataname))
+    end
+
+    res = vcat(permutedims(header), result.data)
+    
+    if filename != nothing
+        file = open(filename, "w")
+        writedlm(file, res, ',')
+        close(file)
+    else
+        for row in eachrow(res)
+            print(join(row, ','))
+        end
+    end
+end

### 2019-07-14 src/Output/decorations/latex/latex.jl

@@ -1,4 +1,14 @@
-function latex(result::GlobalSearchRegression.GSRegData)
+include("consts.jl")
+
+function latex(data::GlobalSearchRegression.GSRegData, path::String=DEFAULT_DEST_FOLDER)
+    latex(result, path=path)
+end
+
+function latex(data::GlobalSearchRegression.GSRegData; path::String=DEFAULT_DEST_FOLDER)
+    res = Dict()
+
+    res[:base] = base(data)
+
     #construir diccionario desde data parcial
         #formula
         #input features extraction
@@ -8,6 +18,43 @@ function latex(result::GlobalSearchRegression.GSRegData)
     #crear env (copiar files estaticos necesarios)
     #renderizar plots
     #renderizar tpl
+end
+
+function base(data::GlobalSearchRegression.GSRegData)
+    dict = Dict()
+    #dict[:]
+
+    equation::Array{Symbol}
+    depvar::Symbol
+    expvars::Array{Symbol}
+    panel::Union{Symbol, Nothing} 
+    time::Union{Symbol, Nothing}
+    depvar_data::Union{Array{Float64}, Array{Float32}, Array{Union{Float64, Missing}}, Array{Union{Float32, Missing}}}
+    expvars_data::Union{Array{Float64}, Array{Float32}, Array{Union{Float64, Missing}}, Array{Union{Float32, Missing}}}
+    panel_data::Union{Nothing, Array{Int64}, Array{Int32}, Array{Union{Int64, Missing}}, Array{Union{Int32, Missing}}}
+    time_data::Union{Nothing, Array{Float64}, Array{Float32}, Array{Union{Float64, Missing}}, Array{Union{Float32, Missing}}}
+    intercept::Bool
+    datatype::DataType
+    removemissings::Bool
+    nobs::Int64
+    options::Array{Any}
+    extras::Dict
+    previous_data::Array{Any}
+    results::Array{Any}
+    
+    for var in names(data)
+        orig = data[var]
+        obs = collect(skipmissing(orig))
+        push!(result, Dict(
+            "name" => string(var),
+            "nobs" => length(obs),
+            "mean" => @sprintf("%.2f", mean(obs)),
+            "std"  => @sprintf("%.2f", std(obs)),
+            "max"  => @sprintf("%.2f", maximum(obs)),
+            "min"  => @sprintf("%.2f", minimum(obs)),
[…]

### 2019-07-14 src/Output/decorations/summary/summary.jl

@@ -1,0 +1,25 @@
+function summary(data::GlobalSearchRegression.GSRegData, filename::String; resultnum::Int64=1)
+    summary(data, filename=filename, resultnum=resultnum)
+end
+
+function summary(data::GlobalSearchRegression.GSRegData; filename::Union{Nothing, String}=nothing, resultnum::Int64=1)
+    if size(data.results, 1) > 0
+        summary(data, data.results[resultnum], filename=filename)
+    end
+    return Base.show(data)
+end
+
+function summary(data::GlobalSearchRegression.GSRegData, result::GlobalSearchRegression.AllSubsetRegression.AllSubsetRegressionResult, filename::String)
+    summary(data, result, filename=filename)
+end
+
+function summary(data::GlobalSearchRegression.GSRegData, result::GlobalSearchRegression.AllSubsetRegression.AllSubsetRegressionResult; filename::Union{Nothing, String}=nothing)
+    sum = GlobalSearchRegression.AllSubsetRegression.to_string(data, result)
+    if filename != nothing
+        file = open(filename, "w")
+        write(file, sum)
+        close(file)
+    else
+        println(sum)
+    end
+end

### 2019-07-14 src/OutputDecoration/OutputDecoration.jl

@@ -1,13 +1,0 @@
-module OutputDecoration
-    
-    using ..GlobalSearchRegression
-    using KernelDensity, Distributions, StatsPlots, Plots, Mustache, Statistics, Printf
-
-    include("const.jl")
-    include("utils.jl")
-    include("strings.jl")
-    include("core.jl")
-
-    export latex
-
-end

### 2019-07-14 src/Preprocessing/core.jl

@@ -300,7 +300,7 @@ function processinput(
 
     nobs = size(depvar_data, 1)
 
-    return GlobalSearchRegression.GSRegData(
+    gsreg_data = GlobalSearchRegression.GSRegData(
         equation,
         depvar,
         expvars,
@@ -315,4 +315,17 @@ function processinput(
         removemissings,
         nobs
     )
+
+    gsreg_data.extras[GlobalSearchRegression.generate_extra_key(:input, gsreg_data.extras)] = Dict(
+        :equation => equation,
+        :method => method,
+        :intercept => intercept,
+        :time => time,
+        :panel => panel,
+        :seasonaladjustment => seasonaladjustment,
+        :removeoutliers => removeoutliers,
+        :removemissings => removemissings
+    )
+
+    return gsreg_data
 end

### 2019-07-14 src/interface.jl

@@ -1,305 +1,0 @@
-function gsreg(
-    equation::String;
-    data=nothing,
-    datanames=nothing,
-    intercept=INTERCEPT_DEFAULT,
-    outsample=OUTSAMPLE_DEFAULT,
-    criteria=CRITERIA_DEFAULT,
-    ttest=TTEST_DEFAULT,
-    method=METHOD_DEFAULT,
-    vectoroperation=VECTOR_OPERATION_DEFAULT,
-    modelavg=MODEL_AVG_DEFAULT,
-    residualtest=RESIDUAL_TEST_DEFAULT,
-    time=TIME_DEFAULT,
-    summary=SUMMARY_DEFAULT,
-    csv=CSV_DEFAULT,
-    resultscsv=CSV_DEFAULT,
-    orderresults=ORDER_RESULTS_DEFAULT,
-    onmessage=ON_MESSAGE_DEFAULT,
-    parallel=PARALLEL_DEFAULT
-    )
-
-    return gsreg(
-        equation,
-        data,
-        datanames=datanames,
-        intercept=intercept,
-        outsample=outsample,
-        criteria=criteria,
-        ttest=ttest,
-        method=method,
-        vectoroperation=vectoroperation,
-        modelavg=modelavg,
-        residualtest=residualtest,
-        time=time,
-        summary=summary,
-        resultscsv=resultscsv,
-        csv=csv,
-        orderresults=orderresults,
-        onmessage=onmessage,
-        parallel=parallel
-    )
-end
-
-function gsreg(
-    equation::String,
-    data;
-    datanames=nothing,
-    intercept=INTERCEPT_DEFAULT,
-    outsample=OUTSAMPLE_DEFAULT,
-    criteria=CRITERIA_DEFAULT,
-    ttest=TTEST_DEFAULT,
-    method=METHOD_DEFAULT,
-    vectoroperation=VECTOR_OPERATION_DEFAULT,
-    modelavg=MODEL_AVG_DEFAULT,
-    residualtest=RESIDUAL_TEST_DEFAULT,
-    time=TIME_DEFAULT,
-    summary=SUMMARY_DEFAULT,
-    csv=CSV_DEFAULT,
-    resultscsv=CSV_DEFAULT,
-    orderresults=ORDER_RESULTS_DEFAULT,
-    onmessage=ON_MESSAGE_DEFAULT,
-    parallel=PARALLEL_DEFAULT
-    )
-
-    equation = equation_str_to_strarr(equation)
-
-    return gsreg(
[…]

### 2019-07-14 src/utils.jl

@@ -172,84 +172,17 @@ function copy_data!(from_data::GSRegData, to_data::GSRegData)
     return to_data
 end
 
-# OLD
-
 """
-Returns the position of the header value based on this structure.
-    - Index
-    - Covariates
-        * b
-        * bstd
-        * T-test
-    - Equation general information merged with criteria user-defined options.
-    - Order from user combined criteria
-    - Weight
+Generate extra key
 """
-function get_data_position(name, expvars, intercept, ttest, residualtest, time, criteria)
-    data_cols_num = length(expvars)
-    mult_col = (ttest == true) ? 3 : 1
-
-    # INDEX
-    if name == INDEX
-        return 1
-    end
-    displacement = 1
-    displacement += mult_col * (data_cols_num) + 1
-
-    # EQUATION_GENERAL_INFORMATION
-    testfields = (residualtest != nothing && residualtest) ? ((time != nothing) ? RESIDUAL_TESTS_TIME : RESIDUAL_TESTS_CROSS) : []
-    equation_general_information_and_criteria = unique([ EQUATION_GENERAL_INFORMATION; criteria; testfields ])
-    if name in equation_general_information_and_criteria
-        return displacement + findfirst(isequal(name), equation_general_information_and_criteria) - 1
-    end
-    displacement += length(equation_general_information_and_criteria)
-
-    if name == ORDER
-        return displacement
-    end
-    displacement += 1
-
-    if name == WEIGHT
-        return displacement
-    end
-    displacement = 1
-
-    # Covariates
-    string_name = string(name)
-    base_name = Symbol(replace(replace(replace(string_name, "_bstd" => ""), "_t" => ""), "_b" => ""))
-    if base_name in expvars
-        displacement = displacement + (findfirst(isequal(base_name), expvars) - 1) * mult_col
-        if occursin("_bstd", string_name)
-            return displacement + 2
+function generate_extra_key(extra_key, extras)
+    if !(extra_key in keys(extras))
+        return extra_key
+    else
+        posfix = 2
+        while Symbol(string(extra_key, "_", posfix)) in keys(extras)
+            posfix = posfix + 1
         end
-        if occursin("_b", string_name)
-            return displacement + 1
-        end
-        if occursin("_t", string_name)
-            return displacement + 3
-        end
+        return Symbol(string(extra_key, "_", posfix))
     end
-end
-
-
-function export_csv(io::IO, result::GSRegResult)
-    head = []
[…]

### 2019-07-14 test/dummy_test.jl

@@ -1,20 +1,24 @@
-using CSV, GlobalSearchRegression, Distributed
+extras = Dict()
 
-data = randn(10,10)
-for i in 1:10
-    for n in 1:10
-        data[i,n] = parse(Int, string(i,n))
-    end
-end
-datanames = [:y, :x1, :x2, :x3, :x4, :x5, :x6, :x7, :x8, :x9]
 
-data = GlobalSearchRegression.Preprocessing.input(
-    "y x*",
-    data,
-    datanames=datanames,
-    intercept=true
-)
+extras = Dict()
 
-data2 = GlobalSearchRegression.FeatureExtraction.featureextraction!(data, fe_sqr=:x1)
-println(data2)
-println(data2.expvars_data)
+extras[get_keys(:a, extras)] = "hola"
+println(extras)
+extras[get_keys(:a, extras)] = "hola"
+println(extras)
+
+
+"""using CSV, GlobalSearchRegression, Distributed
+
+data = CSV.read("data/small.csv")
+data = GlobalSearchRegression.Preprocessing.input("y x*", data, intercept=true)
+println(data.expvars)
+data = GlobalSearchRegression.FeatureExtraction.featureextraction!(data, fe_lag=[:x1=>1, :y=>2])
+println(data.extras)
+
+#data = GlobalSearchRegression.AllSubsetRegression.ols!(data)
+
+#GlobalSearchRegression.Output.summary(data, "summary.txt")
+#GlobalSearchRegression.Output.csv(data, "salida.csv")
+"""

### 2019-07-14 test/latex.jl

@@ -3,8 +3,7 @@ using CSV, GlobalSearchRegression, Distributed
 data = CSV.read("test/data/small.csv")
 
 data = GlobalSearchRegression.Preprocessing.input("y x*", data, intercept=true)
-
-result = GlobalSearchRegression.AllSubsetRegression.run_ols(
+result = GlobalSearchRegression.AllSubsetRegression.ols(
     data,
     outsample=10,
     criteria=[:r2adj, :bic, :aic, :aicc, :cp, :rmse, :sse, :rmseout],
@@ -13,5 +12,4 @@ result = GlobalSearchRegression.AllSubsetRegression.run_ols(
     residualtest=true,
     orderresults=false
 )
-
-GlobalSearchRegression.OutputDecoration.latex(result)
+GlobalSearchRegression.OutputDecoration.csv_res(result.results[1], "salida.csv")

### 2019-07-15 test/main.tex
Latex

--- 2019-07-14 src/Output/decorations/latex/tex/tpl.tex
@@
     \hline
-    {{#var_summary}}
-    {{name}} & {{nobs}} & {{mean}} & {{std}} & {{max}} & {{min}} & {{miss}}\% \\ 
-    \hline
-    {{/var_summary}}
     \end{tabular}
@@
 
-{{#lasso}}
-\section{Regularization}
-
-Lasso regression is a type of linear regression that uses shrinkage.
-Shrinkage is where data values are shrunk towards a central point, like the mean.
-The lasso procedure encourages simple, sparse models (i.e.
-models with fewer parameters).
-This particular type of regression is well-suited for models showing high levels of muticollinearity or when you want to automate certain parts of model selection, like variable selection/parameter elimination.
-
-Lasso regression performs L1 regularization, which adds a penalty equal to the absolute value of the magnitude of coefficients.
-This type of regularization can result in sparse models with few coefficients; Some coefficients can become zero and eliminated from the model.
-Larger penalties result in coefficient values closer to zero, which is the ideal for producing simpler models.
-On the other hand, L2 regularization (e.g.
-Ridge regression) doesn’t result in elimination of coefficients or sparse models.
-This makes the Lasso far easier to interpret than the Ridge.
-
-\begin{equation}
-    \sum_{n=1}^{n}(y_i - \sum_{j}x_{ij}\beta_{j})^2 + \lambda \sum_{j=1}^p|\beta_{j}|
-\end{equation}
-
-Which is the same as minimizing the sum of squares with constraint $\sum \beta_{j}≤ s$. Some of the $\beta_s$ are shrunk to exactly zero, resulting in a regression model that’s easier to interpret.
-
-A tuning parameter, $\lambda$ controls the strength of the L1 penalty. $\lambda$ is basically the amount of shrinkage:
-
-When $ \lambda = 0$, no parameters are eliminated. The estimate is equal to the one found with linear regression.
-As $\lambda$ increases, more and more coefficients are set to zero and eliminated (theoretically, when $\lambda = \infty$, all coefficients are eliminated).
-As $\lambda$ increases, bias increases.
-
-As $\lambda$ decreases, variance increases.
-
-If an intercept is included in the model, it is usually left unchanged.
-
-LASSO regression is shown in the following table:
-
-\begin{table}[!h]
-  \centering
-  \caption{LASSO Regression results}
-    \begin{tabular}{l c}
-    \hline
-                 &       \\
-    VARIABLES    &  {{indep}} \\
-    \hline
-    \hline
-    {{#summary}}
-    {{var}}  & {{coef}} \\
-    {{/summary}}
-    Constant &  \\
-    \hline
-    \hline
-    Observations &  \\
-    \lambda      &  \\
-    R-squared    &  \\
-    \hline
-    \multicolumn{2}{c}{Standard errors in parentheses} \\
-    \multicolumn{2}{c}{*** p<0.01, ** p<0.05, * p<0.1} \\
-    \end{tabular}
-  \label{tab:addlabel}
-\end{table}
-{{/lasso}}
 \section{Gsreg}

### 2019-07-15 src/AllSubsetRegression/utils.jl

@@ -150,15 +150,15 @@ Add values to extras
 """
 function addextras(data, result)
     data.extras[GlobalSearchRegression.generate_extra_key(ALLSUBSETREGRESSION_EXTRAKEY, data.extras)] = Dict(
-        "datanames" => result.datanames,
-        "fixedvariables" => result.fixedvariables,
-        "outsample" => result.outsample,
-        "criteria" => result.criteria,
-        "modelavg" => result.modelavg,
-        "ttest" => result.ttest,
-        "residualtest" => result.residualtest,
-        "orderresults" => result.orderresults,
-        "nobs" => result.nobs        
+        :datanames => result.datanames,
+        :fixedvariables => result.fixedvariables,
+        :outsample => result.outsample,
+        :criteria => result.criteria,
+        :modelavg => result.modelavg,
+        :ttest => result.ttest,
+        :residualtest => result.residualtest,
+        :orderresults => result.orderresults,
+        :nobs => result.nobs        
     )
     return data
 end

### 2019-07-15 src/CrossValidation/utils.jl

@@ -3,8 +3,8 @@ Add values to extras
 """
 function addextras(data, result)
     data.extras[GlobalSearchRegression.generate_extra_key(CROSSVALIDATION_EXTRAKEY, data.extras)] = Dict(
-        "datanames" => result.datanames,
-        "ttest" => result.ttest
+        :datanames => result.datanames,
+        :ttest => result.ttest
     )
     return data
 end

### 2019-07-15 src/FeatureExtraction/utils.jl

@@ -240,12 +240,12 @@ Add values to extras
 """
 function addextras(data, fe_sqr, fe_log, fe_inv, fe_lag, interaction, removemissings)
     data.extras[GlobalSearchRegression.generate_extra_key(FEATUREEXTRACTION_EXTRAKEY, data.extras)] = Dict(
-        "fe_sqr" => fe_sqr,
-        "fe_log" => fe_log,
-        "fe_inv" => fe_inv,
-        "fe_lag" => fe_lag,
-        "interaction" => interaction,
-        "removemissings" => removemissings
+        :fe_sqr => fe_sqr,
+        :fe_log => fe_log,
+        :fe_inv => fe_inv,
+        :fe_lag => fe_lag,
+        :interaction => interaction,
+        :removemissings => removemissings
     )
     return data
 end

### 2019-07-15 src/Output/Output.jl

@@ -1,5 +1,5 @@
 module Output
-    using DelimitedFiles, Printf
+    using DelimitedFiles, Printf, Statistics, Mustache
     using ..GlobalSearchRegression
 
     export csv, summary, latex

### 2019-07-15 src/Output/const.jl

@@ -1,0 +1,1 @@
+const OUTPUT_EXTRAKEY = :output

### 2019-07-15 src/Output/decorations/csv/csv.jl

@@ -5,6 +5,7 @@ function csv(data::GlobalSearchRegression.GSRegData, filename::String; resultnum
 end
 
 function csv(data::GlobalSearchRegression.GSRegData; filename::Union{Nothing, String}=nothing, resultnum::Int64=1)
+    addextras(data, :csv, filename, nothing)
     if size(data.results, 1) > 0
         return csv(data, data.results[resultnum], filename=filename)
     end

### 2019-07-15 src/Output/decorations/latex/latex.jl

@@ -1,4 +1,4 @@
-const TEX_TEMPLATE_FOLDER = joinpath(dirname(@__FILE__), "tex")
+const TEX_TEMPLATE_FOLDER = joinpath(dirname(@__FILE__), "tpl")
 const DEFAULT_LATEX_DEST_FOLDER = "./Latex"
 
 function latex(data::GlobalSearchRegression.GSRegData, path::Union{Nothing, String}=DEFAULT_LATEX_DEST_FOLDER)
@@ -6,123 +6,126 @@ function latex(data::GlobalSearchRegression.GSRegData, path::Union{Nothing, Stri
 end
 
 function latex(data::GlobalSearchRegression.GSRegData; path::Union{Nothing, String}=DEFAULT_LATEX_DEST_FOLDER)
+    addextras(data, :latex, nothing, path)
     if size(data.results, 1) > 0
         dict = Dict()
-        #dict basico
+        latex!(dict, data)
         for i in 1:size(data.results, 1)
-            append!(dict, latex(data, data.results[i], path))
+            latex!(dict, data, data.results[i])
         end
-        #cierre basico
-        render_latex(path, dict)
+        render_latex(dict, path)
     end
 end
 
-function latex(data::GlobalSearchRegression.GSRegData, result::GlobalSearchRegression.AllSubsetRegression.AllSubsetRegressionResult, path::AbstractString)
-    dict = GlobalSearchRegression.AllSubsetRegression.to_latex_dict(data, result)
-    create_figures(result, path)
-    return :allsubsetregression => dict
-end
+function latex!(dict::Dict, data::GlobalSearchRegression.GSRegData)
+    preprocessing_dict = process_dict(data.extras[Preprocessing.PREPROCESSING_EXTRAKEY])
 
-function latex(data::GlobalSearchRegression.GSRegData, result::GlobalSearchRegression.CrossValidation.CrossValidationResult, path::AbstractString)
-    dict = GlobalSearchRegression.CrossValidation.to_latex_dict(data, result)
-    create_figures(result, path)
-    return :kfoldcrossvalidation => dict
-end
+    if "seasonaladjustment" in keys(preprocessing_dict) && preprocessing_dict["seasonaladjustment"] != nothing
+        sa = preprocessing_dict["seasonaladjustment"] 
+        fe_seasonaladjustment_names=Array{String}(undef, size(sa, 1))
+        fe_seasonaladjustment_vals=Array{Int64}(undef, size(sa, 1))
[…]

### 2019-07-15 src/Output/decorations/summary/summary.jl

@@ -3,6 +3,7 @@ function summary(data::GlobalSearchRegression.GSRegData, filename::String; resul
 end
 
 function summary(data::GlobalSearchRegression.GSRegData; filename::Union{Nothing, String}=nothing, resultnum::Union{Nothing, Int}=nothing)
+    addextras(data, :summary, filename, nothing)
     if size(data.results, 1) > 0
         if resultnum != nothing
             return summary(data, data.results[resultnum], filename=filename)

### 2019-07-15 src/Output/utils.jl

@@ -1,0 +1,11 @@
+"""
+Add values to extras
+"""
+function addextras(data, outputtype, filename, path)
+    data.extras[GlobalSearchRegression.generate_extra_key(OUTPUT_EXTRAKEY, data.extras)] = Dict(
+        :outputtype => outputtype,
+        :filename => filename,
+        :path => path
+    )
+    return data
+end

### 2019-07-15 src/Preprocessing/utils.jl

@@ -205,17 +205,17 @@ Add values to extras
 """
 function addextras(data, method, seasonaladjustment, removeoutliers)
     data.extras[GlobalSearchRegression.generate_extra_key(PREPROCESSING_EXTRAKEY, data.extras)] = Dict(
-        "equation" => vcat(data.depvar, data.expvars),
-        "depvar" => data.depvar,
-        "expvars" => data.expvars,
-        "data" => DEFAULT_DATANAME,
-        "method" => method,
-        "intercept" => data.intercept,
-        "panel" => data.panel,
-        "time" => data.time,
-        "seasonaladjustment" => seasonaladjustment,
-        "removeoutliers" => removeoutliers,
-        "removemissings" => data.removemissings
+        :equation => vcat(data.depvar, data.expvars),
+        :depvar => data.depvar,
+        :expvars => data.expvars,
+        :data => DEFAULT_DATANAME,
+        :method => method,
+        :intercept => data.intercept,
+        :panel => data.panel,
+        :time => data.time,
+        :seasonaladjustment => seasonaladjustment,
+        :removeoutliers => removeoutliers,
+        :removemissings => data.removemissings
     )
     return data
 end

### 2019-07-15 test/dummy_test.jl

@@ -2,3 +2,4 @@ using CSV, GlobalSearchRegression, Distributed
 
 data = CSV.read("data/small.csv")
 @time data = GlobalSearchRegression.gsr("y x*", data, kfoldcrossvalidation=true)
+GlobalSearchRegression.Output.latex(data, "./")

### 2019-07-19 src/Output/decorations/latex/tpl.tex
Latex dict fixes

\documentclass{article}

\usepackage{GSReg-style}

\title{GlobalSearchRegression.jl \\
       \vspace{5mm} REPORT}

%\author{
%  Insert author name \\
%  Insert Institution/Affiliation \\
%  Insert other researcher information \\
%  \texttt{insert@email.com} \\
%   \and if there are more authors
%\author{
%  Insert author name \\
%  insert Institution/Affiliation \\
%  insert other researcher information \\
%  \texttt{insert@email.com} \\
%}

\begin{document}

\maketitle

\vspace{5mm}
\tableofcontents
\clearpage

\section{Introduction}
The advantage of having thousands/millions of features to deal with complex phenomena stimulates an unprecedented number of methodological -and technological- improvements to manage the ‘curse of dimensionality’.

In Economics, this process has a dual approach with machine-learning (ML) and econometric (EC) algorithms emerging for different purposes: the former for prediction/forecasts (focusing on $\hat{y}$) and the latter for estimation/causal inference (interested in $\hat{\beta}$). Alternatively, the same distinction can be expressed in Diebold’s terms as non-causal vs causal prediction, where ML algorithms are designed to reduce prediction sampling-risks -i.e. learning through cross-validation techniques- and EC methods to identify unbiased multivariate relationships -i.e. avoiding consistency issues through residual and coefficient tests for model selection.

Following Varian’s advices, about ML and EC complementarities -i.e. merging algorithms from different families to reduce both sampling and model uncertainty-, we are developing a novel multi-layer-multi-algorithm methodology combining two reinforcing paradigms: The London School of Economics (LSE) “Testimation” approach -to obtain information about residual properties- and the Bayesian-like “Double-model averaging” -across different covariates and sub-samples. This methodology includes five complementary layers -handling cross-section, time series and panel data- see \cite{gsreg2019}: \begin{enumerate}
    \item Pre-processing: with outlier detection, missing values identification, seasonal adjustment and normalization/standardization functions;

    \item  Feature extraction: creation of logs, squares, inverses and interactions from selected variables;

    \item  Feature pre-selection: using filter and embedded ML algorithms like CFS, Variance threshold and LASSO functions;

    \item Final feature selection: with a modified all-subset regression approach, including residual tests and model averaging capabilities;

    \item Post-estimation fine-tuning: coefficient re-evaluation through cross-validation techniques and model averaging across different k-fold results. 
\end{enumerate}

In order to implement this feature selection algorithm, the following syntax has been used:

\begin{lstlisting} 
      using GlobalSearchRegression
      GlobalSearchRegression.gsr(
        {{#input}}
        equation = "{{equation}}",
        data = {{data}},
        datanames = {{datanames}},
        method = :{{method}},
        intercept = {{intercept}},
        {{#panel}}panel = {{.}},{{/panel}}
        {{#time}}time = {{.}},{{/time}}
        {{#seasonaladjustment}}seasonaladjustment = {{.}},{{/seasonaladjustment}}
        removeoutliers = {{removeoutliers}},
        {{/input}}

        fe_sqr
        fe_log
        fe_inv
        fe_lag
        interaction
        preliminaryselection
        fixedvariables
        outsample
        criteria
        ttest
        modelavg
        residualtest
        orderresults
        kfoldcrossvalidation
        numfolds
        testsetshare
        exportcsv
        exportsummary
\end{lstlisting}

The report is structured as follows. After this introduction, the methodology is presented. In section 3, descriptive statistics are introduced. In turn, section 4 is dedicated to LASSO results. In turn, section 4 is dedicated to All-subset-regression results. After that, section 5 shows All-subset-regression results. Finally, the last section examines K-fold cross-validation outcomes.

\section{Methodology}

{{#input}}
\subsection{Pre-processing}
It performs required variable transformations to improve model accuracy and feature selection. In this report, it has been used the following internal pre-processing functions:

\begin{enumerate}
    \item Remove-missings: Rows with missing values have been ommited for regression purposes.

  {{#seasonalfortex}}
    \item Seasonal-adjustment: variables {{#:fe_seasonaladjustment_names}}{{.}}, {{/:fe_seasonaladjustment_names}}have been selected for seasonal adjustment using \verb SingularSpectrumAnalysis.jl  (see \cite{hassani2007}). For each one, the function removes the seasonal component using window lengths equal to {{#:fe_seasonaladjustment_vals}}{{.}}, {{/:fe_seasonaladjustment_vals}}respectively.
  {{/seasonalfortex}}

  {{#seasonalfortex2}}
  \item Seasonal-adjustment: variable {{#:fe_seasonaladjustment_names2}}{{.}}{{/:fe_seasonaladjustment_names2}} has been selected for seasonal adjustment using \verb SingularSpectrumAnalysis.jl  (see \cite{hassani2007}). The function removes the seasonal component using a window length equal to {{#:fe_seasonaladjustment_vals2}}{{.}}{{/:fe_seasonaladjustment_vals2}}.
  {{/seasonalfortex2}}

  {{#removeoutliers}} 
  \item Remove-outliers: extreme observations (because of input errors or extraordinary/non-relevant events) have been removed using the standard 3-sigma rule (see \cite{lehmann2013}).
  {{/removeoutliers}}
\end{enumerate}
{{/input}}
{{#featureextraction}}
\subsection{Feature extraction}

In this stage, selected functions have been used to create additional covariates with the following transformations:

\begin{enumerate}
  {{#fe_lag}}
    {{#vars}}
    \item Lags: for variables {{#names}}{{.}}, {{/names}}the lag operator created lag polinominals of order {{#values}}{{.}}, {{/values}}respectively, as additional explanatory variables.
    {{/vars}}
    {{#var}}
    \item Lags: for variable {{#names}}{{.}}{{/names}}, the lag operator created a lag polinominal of order {{#values}}{{.}}{{/values}}, as an additional explanatory variable.
    {{/var}}
  {{/fe_lag}}
  {{#fe_log}}
    {{#vars}}
    \item Logs: for variables {{#names}}{{.}}, {{/names}}the logarithm transformation was applied to generate new covariates.
    {{/vars}}
    {{#var}}
    \item Logs: for variable {{#names}}{{.}}{{/names}}, the logarithm transformation was applied to generate a new covariate.
    {{/var}}
  {{/fe_log}}
  {{#fe_inv}}
    {{#vars}}
    \item Inverse: for variables {{#names}}{{.}}, {{/names}}the inverse function was implemented to create additional covariates.
    {{/vars}}
    {{#var}}
    \item Inverse: for variable {{#names}}{{.}}{{/names}}, the inverse function was implemented to create an additional covariate.
    {{/var}}
  {{/fe_inv}}
  {{#fe_sqr}}
    {{#vars}}
    \item Squares: for variables {{#names}}{{.}}, {{/names}}the square transformation was implemented to create additional explanatory variables.
    {{/vars}}
    {{#var}}
    \item Squares: for variable {{#names}}{{.}}{{/names}}, the square transformation was implemented to create an additional explanatory variable.
    {{/var}}
  {{/fe_sqr}} 
  {{#interaction}}
    {{#vars}}
    \item Interactions: for variables {{#names}}{{.}}, {{/names}}all possible first-level interactions were created as additional covariates.
    {{/vars}}
    {{#var}}
    \item Interactions: for variable {{#names}}{{.}}{{/names}}, all possible first-level interactions were created as an additional covariate.
    {{/var}}
  {{/interaction}}
\end{enumerate}
{{/featureextraction}}
{{#preliminaryselection}}
\subsection{Regularization - LASSO}
The Least Absolute Shrinkage and Selection Operator (LASSO) algorithm is a type of regularized linear regression that uses shrinkage (see \cite{tibshirani1996}) to obtain simple sparse models. This particular type of regression is well-suited for feature selection in models with high levels of muticollinearity, and particularly efficient in fat-data scenarios.

The LASSO regression is a Machine Learning wrapper algorithm (see \cite{chandrashekar2014}) that performs L1 regularization on the optimization function. It adds a penalty term proportional to the sum of coefficients absolute values. With this type of regularization some estimation parameters become zero and -therefore- associated variables can eliminated from the model.
\begin{equation}
    \sum_{n=1}^{n}(y_i - \sum_{j}x_{ij}\beta_{j})^2 + \lambda \sum_{j=1}^p|\beta_{j}|
\end{equation}

Equation (1) entails a residual sum of squares minimization with constraint $\sum \beta_{j}\leq s$. Some of the $\beta_s$ are shrunk to zero, resulting in a more parsimonious regression model.

A tuning parameter, $\lambda$ controls the strength of the L1 penalty. $\lambda$ is basically the amount of shrinkage:

When $ \lambda = 0$, no parameters are eliminated. LASSO estimates replicate OLS ones.

As $\lambda$ increases, more and more coefficients are set to zero and associated variables can be eliminated (theoretically, when $\lambda = \infty$, no covariate is retained).

The choice of $\lambda$ entails a well-known trade-off:  As $\lambda$ increases, estimator bias increases but as $\lambda$ decreases, estimator variance increases (i.e. omitted variables vs model over-fitting).

In this report, the $\lambda$ parameter has been dynamically defined in order to retain up to {{lassonumvars}} covariates.

It must be noticed that all predictors are standardized "on-the-fly", in order to avoid scale issues in feature selection.
{{/preliminaryselection}}

{{#allsubsetregression}}
\subsection{All-subset-Regression}
Unlike other feature selection algorithms (including LASSO), All-subset-regression (ASR) approaches guarantees both in-sample and out-of-sample optimality (i.e. better information criteria results than any other method). However, it has been left aside by econometricians and machine learning practitioners because of computational concerns. Execution times for ASR algorithms in a more-than-20-covariates environement were prohibitive until now. Using existing ASR packages, a simple feature selection problem for 20 covariates usually takes more than 8000 seconds in 
\href{https://cran.r-project.org/web/packages/MuMIn/MuMIn.pdf}{R}, and more than 500000 seconds in \href{https://ideas.repec.org/c/boc/bocode/s457737.html#download}{Stata}. Moreover, with 25 potential covariates both algorithms are unable to obtain feasible-solutions in standard personal computers.

Fortunately, the \verb GlobalSearchRegression.jl package has significantly reduced execution times, running up to 3165 times faster than Stata and 197 times faster than R (see \cite{gsreg2019}). This improvement allows researchers to regain attention on ASR algorithms, looking for better feature selection results.

In this Julia package, the best model among $2^{n}-1$ alternatives is selected using a potentially composite ordering variable defined as the equally-weighted average of normalized (to guarantee equal weights) and harmonized (to ensure that higher values always identify better models) user's specified criteria. For in-sample adjustment, available alternatives include: Adjusted R2 (:r2adj, the default), Bayesian information criteria (:bic), Akaike and Corrected Akaike information criteria (:aic and :aicc), Mallows's Cp statistic (:cp), Sum of squared errors (also known as Residual sum of squares, :sse) and the Root mean square error (:rmse). For out-of-sample accuracy, there is available the out-of-sample root mean square error (:rmsout). Users are free to combine in-sample and out-of-sample information criteria. In this report, selected information criteria include ({{#criteria_names}}{{.}}, {{/criteria_names}}the key variable/s for feature selection.

Additional options applied in this report includes:

\begin{enumerate}
  {{#intercept}}
  \item Intercept has been included in all models. Alternatively, users could erase it by selecting the intercept=false boolean option.
  {{/intercept}}
  {{#outsample}}
  \item The outsample option identifies how many observations are used for prediction purposes. In this case, it has been set to {{outsample}}.
  {{/outsample}}
  {{#ttest}}
  \item The user's choice has been ttest=true. Therefore, standard deviation, ttest parameters and related probabilities has been calculated.
  {{/ttest}}
  {{#modelavg}}
  \item Across-models' average coefficients, t-tests and additional statistics were obtained using combined-criteria exponential weights because of the modelavg=true option. More precisely, each alternative model has a weight given by w1/sum(w1), where w1 is defined as exp(-delta/2) and delta is equal to max(index)-index -- where index is the above mentioned normalized, harmonized and potentially combined selection criteria--.
  {{/modelavg}}
  {{#residualtest}}
  \item The residualtest=true option enables white heteroskedasticity and Jarque-Bera normality test to be implemented for each model.
  {{/residualtest}}
  {{#residualtest}}
  \item The residualtest=true option enables white heteroskedasticity, Jarque-Bera normality test and the Breusch-Godfrey test for autocorrelation to be implemented for each model.
  {{/residualtest}}
  {{#orderresults}}  
  \item User's specification of orderresults=true entails that the output matrix has been sorted by the the above mentioned normalized, harmonized and potentially combined selection criteria.
  {{/orderresults}}
\end{enumerate}
{{/allsubsetregression}}

--------------------------------------------------

{{#crossvalidation}}
\subsection{K-fold Cross Validation}

Cross-validation (CV) is a procedure used to examine feature selection robustness to re-sampling. Among different alternatives, the K-fold approach has a parameter $K$ which identifies the number of groups that a given database must be split into (see \cite{arlot2010}). In this report user selected k-fold number is {{kfolds}}.

The general procedure is as follows:

\begin{enumerate}
  \item Randomly split the database into k disjoint -roughly equally sized- groups
  \item For each group:
  \begin{enumerate}
    \item Take a group as a hold out or test data set (leave-one-out scheme);
    \item Take the remaining groups together as a training data set;
    \item Fit a model on the training set and evaluate it on the test set; and
    \item Retain the evaluation (i.e out-of-sample Root Mean Square Error -RMSE-).
  \end{enumerate}
  \item Summarize model strengths using CV scores
\end{enumerate}

In \verb GlobalSearchRegression.jl  the K-fold cross-validation is available for both LASSO pre-selection and ASR final selection. In the latter, for each K-partition $2^{p} - 1$ alternative models are fitted (where p is the number of potential covariates included in the ASR algorithm) and the candidate ‘optimal’ model is selected using the out-of-sample Root Mean Square Error (obtained from the test set). Therefore, K-candidate models are retained (one for each K-partition). The final "best" model is obtained using either across-model averages or medians.

This cross-validation specific alternative has been denominated as \textit{Averaging Cross validation (ACV)} by Jung and Hu (see, \cite{jung2015}). The authors found that:

\begin{quote}
"Due to the averaging effect, efficiency of the final parameter estimates obtained by ACV improves over that of the traditional K-fold CV. We note that parameter estimates of CV and ACV are identical when all the candidate ‘optimal’ models from ACV are identical to the model selected by the traditional CV."

\hfill Jung and Hu (2015:168)
\end{quote}

It is worth mentioning that K-fold preferred methodologies change depending on whether cross-section, time-series or panel data observations are employed. For the first one, standard K-fold random allocation is the gold-standard (see \cite{arlot2010}).

{{#time}}
For time series, however, this methodology could decrease model selection accuracy because -potential- serial correlation violate the cross-validation fundamental assumption of i.i.d. data (see \cite{bergmeir2012}). Among available alternatives, most widely used are non-dependent k-fold cross-validation (see \cite{bergmeir2018}) and rolling forecast origin cross-validation (based on \cite{hyndman2013}). Unfortunately, the  first one entails an inefficient use of available information and second one has comparison problems for the above mentioned ACV approach (because each sampling partition has a different training set size). Therefore, \verb GlobalSearchRegression.jl uses a slightly modified version of the rolling forecast origin cross-validation, with the following steps:

\begin{enumerate}
\item User defines the rolling test-set share ($s1$) and the number of sub-samples (K);
\item Therefore, the rolling training-set share ($s2$) is automatically obtained from:

\begin{equation}
  T=s1 \times T+s2 \times T+(K-1)
\end{equation}
or
\begin{equation}
  s2=(1-s1)-[(K-1)/T]
\end{equation}
where $T$ is the total number of observations.
\item Rolling sub-samples are defined using the following pseudo-code (where data is supossed to be a time-sorted matrix/array/dataframe.):

\begin{algorithm}
\caption*{\textbf{Cross validation pseudo-code 1}: Rolling sub-samples for time series}
\begin{itemize}
  \item[] for $i=1:K$
  \begin{itemize}
    \item[]  Training\_i=data[i:s2*T,:]
    \item[] Test\_i=data[(s2 \times T+i):((s2 \times T+i)+(s1 \times T)-1),:]
  \end{itemize}
  \item[] end
\end{itemize}
\end{algorithm}

\item For each sub-sample:

\begin{enumerate}
\item the first $s_{2}*T$ observations are used to train the model and the subsequent $s_{1}*T$ observations are retained to test model accuracy and compute the out-of-sample RMSE;
\item the "best candidate" (across different covariate combinations) is the model which minimizes the out-of-sample RMSE;
\end{enumerate}
\item Finally, the cross-validated best model is obtained averaging (or using median) coefficients and standard deviations across the K-best candidates.
\end{enumerate}

In this report the test size has been set to {{tsetsize}} and, as already mentioned,
selected k-fold number is {{kfolds}}.
{{/time}}
{{#panelid}}
For panel data, cross-validation techniques are similar to time-series ones, but stratified by panel-id (because panel databases can be unbalanced). More precisely, the cross-validation strategy is defined by:

\begin{enumerate}
\item As for time series, user defines the rolling test-set share ($s1$) and the number of sub-samples (K);
\item But the rolling training-set share ($s2$) is obtained from a slightly modified equation:
\begin{equation}
  \forall j, s2=(1-s1)-[(K-1)/T{j}] 
\end{equation}
where $T{j}$ is the total number of time series observations for panel-id = j.
\item Therefore, rolling sub-samples are defined as (once again, data should be time-sorted matrix/array/dataframe):

\begin{algorithm}
\caption*{\textbf{Cross validation pseudo-code 2}: Rolling sub-samples for panel data}
\begin{itemize}
    \item[] for $i=1:K$
    \begin{itemize}
        \item[]  for $j=1:Q$
        \begin{itemize}
            \item[] Training\_i\_j=data[i:s2 \times T{j},:]
            \item[] Test\_i\_j=data[(s2 \times T{j}+i):((s2 \times T{j}+i)+(s1 \times T{j})-1),:]
        \end{itemize}
        \item[] end
    \end{itemize}
    \item[] end
\end{itemize}     
\end{algorithm}

\item For each sub-sample K, the time series methodology is reproduce henceforth.
\end{enumerate}
{{/panelid}}
{{/crossvalidation}}

{{#input}}
\section{Descriptive Statistics}

Main descriptive statistics for All-subset-regression potential covariates are presented in table 1:

\clearpage

\section{Variables}

\begin{table}[!h]
  \centering
  \caption{Descriptive Statistics for the main dataset}
    \begin{tabular}{|p{2cm}|p{4cm}|c|c|c|c|c|c|}
    \hline
    Variable & Description & Obs. & Mean & Sd & Max & Min & \% Miss \\
    \hline
    \hline
    {{#descriptive}}{{^name}}
    \hline
    \end{tabular}
\end{table}

\clearpage

\begin{table}[!h]
  \centering
  \caption{Descriptive Statistics for the main dataset (cont.)}
    \begin{tabular}{|p{2cm}|p{4cm}|c|c|c|c|c|c|}
    \hline
    Variable & Description & Obs. & Mean & Sd & Max & Min & \% Miss \\
    \hline
    \hline
    {{/name}}{{#name}}{{name}} & Insert Description & {{nobs}} & {{mean}} & {{std}} & {{max}} & {{min}} & {{miss}}\% \\ 
    {{/name}}{{/descriptive}}\hline
    \end{tabular}
\end{table}
{{/input}}

{{#preliminaryselection}}
\section{Regularization results}

LASSO regression is shown in the following table:

\begin{table}[!h]
  \centering
  \caption{LASSO Regression results}
    \begin{tabular}{l c}
    \hline
    \hline
              & \\
    Variables & {{ depvar }} \\
    \hline
    \hline
    {{#expvars}}
      {{ name }} & {{ coef }} \\
    {{/expvars}}
    \hline
    \hline
    Observations &  {{ nobs }} \\
    \lambda      &  {{ lambda }} \\
    \hline
    \end{tabular}
  \label{tab:addlabel}
\end{table}
{{/preliminaryselection}}

{{#allsubsetregression}}
\section{Global Search Regression}

\subsection{All sub-subset regression: Best Model and Model Averaging}

\begin{table}[!h]
  \centering
  \caption{GSReg results}
    {{#bestmodel}}

    \begin{tabular}{l c{{#modelavg}} c{{/modelavg}}}
    \hline
    \hline
                 &  Best Model              {{#modelavg}} & Model Averaging           {{/modelavg}} \\
    Variables    &  {{depvar}}              {{#modelavg}} & {{depvar}}                {{/modelavg}} \\
    \hline{{#bmexpvars}} 
    {{name}}     & {{best.b}}{{best.stars}} {{#avg}} & {{b}}{{stars}}    {{/avg}} \\{{#ttest}}
                 & {{best.bstd}}            {{#avg}} & {{bstd}} {{/avg}} \\{{/ttest}}
    {{/bmexpvars}}\hline

    Observations &   \multicolumn{ {{^avg}}1{{/avg}} {{#avg}}2{{/avg}} }{c}{ } \\
    Criteria     &   \multicolumn{ {{^avg}}1{{/avg}} {{#avg}}2{{/avg}} }{c}{ } \\
    \hline
    \hline
    \multicolumn{ {{^avg}}2{{/avg}} {{#avg}}3{{/avg}} }{c}{Standard errors in parentheses} \\
    \multicolumn{ {{^avg}}2{{/avg}} {{#avg}}3{{/avg}} }{c}{*** p < 0.01, ** p < 0.05, * p < 0.1} \\
    \end{tabular}
    {{/bestmodel}}
  \label{tab:addlabel}
\end{table}

\subsection{Coefficient, t-test and selection criteria gains distributions}

In the following pages, coefficient, t-test and selection criteria distributions are presented. For each covariate, four figures are included: two bivariate density plots (a contour plot and a wireframe plot, for coefficients and t-tests distributions) and two selection criteria contribution plots (a Kernel density plot and a combined Box-Violin plot). The last two plots are used to see the combined\_criteria\_index variation explained by the inclusion of each covariate in the models. 
Finally, we include a unique figure where covariate relative performance is compared using the average impact of each explanatory variable on the combined\_criteria\_index.

\clearpage

{{#expvars}}
\begin{center}
    \large{\textbf{Coefficient, t-test and selection criteria gains distributions for {{name}} }}
\end{center}

\vspace{-5mm}

\begin{figure}[!ht]
  \centering
  \begin{minipage}[b]{0.46\textwidth}
    \centering
    \includegraphics[width=\textwidth]{contour_{{name}}_b_t.png}
    \caption{Bivariate Kernel density (Contour view)}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{0.53\textwidth}
    \centering
    \includegraphics[width=\textwidth]{wireframe_{{name}}_b_t.png}
    \caption{Bivariate Kernel density (Contour view)}
  \end{minipage}

  \begin{minipage}[b]{0.48\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Kdensity_criteria_{{name}}.png}
    \caption{Selection criteria gains for including {{name}} (Kernel view)}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{0.48\textwidth}
    \centering    
    \includegraphics[width=\textwidth]{BoxViolinDot_{{name}}.png}
    \caption{Selection criteria gains for including {{name}} (Box-Violin view)}    
  \end{minipage}
\end{figure}

\vspace{1cm}

The following table shows main statistics of coefficient and t-test distribution

\begin{table}[!h]
    \centering
    \caption{Statistics}
    \begin{tabular}{|l|c|c|}
    \hline
    Variable {{name}} Statistics &  Coefficient Distribution &  T-test Distribution  \\
    \hline
    \hline
    Simple average    & {{b.avg}}      & {{t.avg}} \\
    \hline
    Median            & {{b.median}}   & {{t.median}} \\
    \hline
    Mode              & {{b.mode}}     & {{t.mode}} \\
    \hline
    Skewness          & {{b.std}}      & {{t.std}} \\
    \hline
    kurtosis          & {{b.skew}}     & {{t.skew}} \\
    \hline
    Positive Share    & {{b.kurt}}     & {{t.kurt}} \\
    \hline
    Significant Share & {{b.posshare}} & {{t.sigshare}} \\
    \hline
    \end{tabular}
\end{table}

\clearpage
{{/expvars}}

\begin{figure}[!ht]
    \centering
    \caption{Covariable relevance related to selection criteria}
    \includegraphics[scale=0.6]{cov_relevance.png}
\end{figure}

In this figure it is shown that potential covariates included in the general unrrestricted model of the all-subset-regression algorithm display singnificant differences in terms of the user selected information criteria. For each explanatory variable information criteria gains were obtained as the differece between averages information criteria obtained from models which includes and excludes that covariate. Available statistics suggests that there {{are or is}} {{numofpositivegainsvariables}} explanatory {{variable or variables}} that improved model accuracy. {{Among them, {{bestvar}} or {{bestvar}}}} helps to increase up to a {{gainsinperc}}\% the user selected information criteria. On the contrary, there {{are or is}} {{numofnegativegainsvariables}} {{covariate or covariates}} that have a deleterious impact on model accuracy. This is specially true for {{worstvar}}, which seems to decrease up to a {{lossinperc}}\% the user selected information criteria}}
{{/allsubsetregression}}

{{#crossvalidation}}
\section{k-fold cross-validation}

\begin{table}[!h]
  \centering
  \caption{K-fold cross-validation Results}
    \begin{tabular}{l c c}
    \hline
    \multicolumn{3}{c}{K-fold scheme:\textbf{Insert scheme}} \\
                 & {{kfolds}}-fold  & {{kfolds}}-fold \\
    Variables    & Mean             & Median          \\
    \hline
    \hline
                 &                  &                  \\
                 &                  &                  \\
    \hline

    Error out-sample &     &   \\
    Error in-sample  &     &   \\
                     &     &   \\
    \hline
    \hline
    \multicolumn{3}{c}{\textit{Standard errors in parentheses}} \\
    \multicolumn{3}{c}{*** p < 0.01, ** p < 0.05, * p < 0.1} \\
    \hline
    \end{tabular}
  \label{tab:addlabel}
\end{table}
{{/crossvalidation}}

\addcontentsline{toc}{section}{References} 
\bibliographystyle{unsrt}  
\begin{thebibliography}{1}

\bibitem{gsreg2019}
Panigo D., Glüzmann P., Mocskos, E., Mauri Ungaro, A., Mari, V., and Monzón, N. (2019). \textit{GlobalSearchRegression.jl: Building bridges between Machine Learning and Econometrics in Fat-Data scenarios}.Paper presented at JuliaCon2019, Baltimore-MD, United States.

\bibitem{hassani2007}
Hassani H. (2007). \textit{Singular Spectrum Analysis: Methodology and Comparison}. Journal of Data Science, 5, 239-257.

\bibitem{lehmann2013}
Lehmann, R. (2013). \textit{3 sigma-rule for outlier detection from the viewpoint of geodetic adjustment}. Journal of Surveying Engineering, 139(4), 157-165.

\bibitem{tibshirani1996}
Tibshirani, R. (1996). \textit{Regression shrinkage and selection via the lasso}. Journal of the Royal Statistical Society: Series B (Methodological), 58(1), 267-288.

\bibitem{chandrashekar2014}
Chandrashekar, G., and Sahin, F. (2014). \textit{A survey on feature selection methods}. Computers & Electrical Engineering, 40(1), 16-28.

\bibitem{gluzmann2015}
Gluzmann, P., and Panigo, D. (2015). \textit{Global search regression: A new automatic model-selection technique for cross-section, time-series, and panel-data regressions.} The Stata Journal, 15(2), 325-349.

\bibitem{arlot2010}
Arlot, S., and Celisse, A. (2010).\textit{A survey of cross-validation procedures for model selection}. Statistics surveys, 4, 40-79.

\bibitem{jung2015}
Jung, Y., and Hu, J. (2015). \textit{A K-fold averaging cross-validation procedure}. Journal of nonparametric statistics, 27(2), 167-179.

\bibitem{bergmeir2012}
Bergmeir, C., and Benítez, J. M. (2012). \textit{On the use of cross-validation for time series predictor evaluation}. Information Sciences, 191, 192-213.

\bibitem{bergmeir2018}
Bergmeir, C., Hyndman, R. J., and Koo, B. (2018). \textit{A note on the validity of cross-validation for evaluating autoregressive time series prediction}. Computational Statistics & Data Analysis, 120, 70-83.

\bibitem{hyndman2013}
Hyndman, R. J., and Athanasopoulos, G. (2013). Measuring forecast accuracy. Gilliland M, Tashman L, Sglavo U. Business forecasting: practical problems and solutions, 177-84.

\end{thebibliography}

\end{document}

### 2019-07-19 src/AllSubsetRegression/core.jl

@@ -63,8 +63,6 @@ function to_string(data::GlobalSearchRegression.GSRegData, result::AllSubsetRegr
         out *= @sprintf("\n")
         out *= @sprintf("──────────────────────────────────────────────────────────────────────────────\n")
 
-
-
         for varname in data.expvars
             out *= @sprintf(" %-35s", varname)
             out *= @sprintf(" %-10f", result.modelavg_data[datanames_index[Symbol(string(varname, "_b"))]])

### 2019-07-19 src/AllSubsetRegression/utils.jl

@@ -151,14 +151,18 @@ Add values to extras
 function addextras(data, result)
     data.extras[GlobalSearchRegression.generate_extra_key(ALLSUBSETREGRESSION_EXTRAKEY, data.extras)] = Dict(
         :datanames => result.datanames,
-        :fixedvariables => result.fixedvariables,
-        :outsample => result.outsample,
-        :criteria => result.criteria,
-        :modelavg => result.modelavg,
-        :ttest => result.ttest,
+        :depvar => data.depvar,
+        :expvars => data.expvars,
+        :nobs => data.nobs,
+        :time => data.time,
         :residualtest => result.residualtest,
-        :orderresults => result.orderresults,
-        :nobs => result.nobs        
+        :criteria => result.criteria,
+        :intercept => data.intercept,
+        :ttest => result.ttest,
+        :outsample => result.outsample,
+        :modelavg => result.modelavg,
+        :fixedvariables => result.fixedvariables,
+        :orderresults => result.orderresults
     )
     return data
 end

### 2019-07-19 src/CrossValidation/utils.jl

@@ -4,7 +4,13 @@ Add values to extras
 function addextras(data, result)
     data.extras[GlobalSearchRegression.generate_extra_key(CROSSVALIDATION_EXTRAKEY, data.extras)] = Dict(
         :datanames => result.datanames,
-        :ttest => result.ttest
+        :ttest => result.ttest,
+        :kfolds => result.k,
+        :tsetsize => result.s,
+        :panel => data.panel,
+        :time => data.time,
+        :median => result.median_data, #TODO: Add expvars
+        :average => result.average_data #TODO: Add expvars
     )
     return data
 end

### 2019-07-19 src/Output/decorations/latex/latex.jl

@@ -2,10 +2,6 @@ const TEX_TEMPLATE_FOLDER = joinpath(dirname(@__FILE__), "tpl")
 const DEFAULT_LATEX_DEST_FOLDER = "./Latex"
 
 function latex(data::GlobalSearchRegression.GSRegData, path::Union{Nothing, String}=DEFAULT_LATEX_DEST_FOLDER)
-    return latex(data, path=path)
-end
-
-function latex(data::GlobalSearchRegression.GSRegData; path::Union{Nothing, String}=DEFAULT_LATEX_DEST_FOLDER)
     addextras(data, :latex, nothing, path)
     if size(data.results, 1) > 0
         dict = Dict()
@@ -13,34 +9,92 @@ function latex(data::GlobalSearchRegression.GSRegData; path::Union{Nothing, Stri
         for i in 1:size(data.results, 1)
             latex!(dict, data, data.results[i])
         end
+        #render_plots(dict, data)
+        create_workspace(path)
         render_latex(dict, path)
     end
 end
 
 function latex!(dict::Dict, data::GlobalSearchRegression.GSRegData)
+    # Preprocessing    
     preprocessing_dict = process_dict(data.extras[Preprocessing.PREPROCESSING_EXTRAKEY])
+    preprocessing_dict["equation"] = join(map(x -> "$x", filter(x -> x != :_cons, preprocessing_dict["datanames"])), " ")
+    preprocessing_dict["datanames"] = string("[:", join(preprocessing_dict["datanames"], ", :"), "]")
+    preprocessing_dict["descriptive"] = []
+
+    datanames_index = GlobalSearchRegression.create_datanames_index(data.expvars) 
+    
+    for (i, var) in enumerate(data.expvars)
+        orig = data.expvars_data[:, datanames_index[var]]
+        obs = collect(skipmissing(orig))
+        c_obs = length(obs)
+        c_miss = length(orig) - c_obs
+        push!(preprocessing_dict["descriptive"], Dict(
+            "name" => string(var),
+            "nobs" => length(obs),
+            "mean" => @sprintf("%.2f", mean(obs)),
+            "std"  => @sprintf("%.2f", std(obs)),
+            "max"  => @sprintf("%.2f", maximum(obs)),
+            "min"  => @sprintf("%.2f", minimum(obs)),
+            "miss" => @sprintf("%.2f", (c_miss/c_obs)*100)
+        ))
+        if( (i + 1) % 54 == 0 )
[…]

### 2019-07-19 src/Output/utils.jl

@@ -9,3 +9,24 @@ function addextras(data, outputtype, filename, path)
     )
     return data
 end
+
+
+function get_array_details(arr)
+    dict = Dict(arr)
+    Dict(
+        ((length(arr) == 1) ? "var" : "vars") => Dict(
+            "names" => map(string, collect(keys(dict))),
+            "values" => collect(values(dict))
+        ),
+        ((length(arr) == 1) ? "vars" : "var") => false
+    )
+end
+
+function get_array_simple_details(arr)
+    Dict(
+        ((length(arr) == 1) ? "var" : "vars") => Dict(
+            "names" => map(string, arr)
+        ),
+        ((length(arr) == 1) ? "vars" : "var") => false
+    )
+end

### 2019-07-19 src/PreliminarySelection/core.jl

@@ -22,7 +22,8 @@ function lasso!(data::GlobalSearchRegression.GSRegData)
     data.extras[:lasso_betas] = betas
 
     vars = map(b -> b != 0, betas)
-
+    lassonumvars = size(filter(b -> b != 0, betas), 1)
+    
     if data.intercept
         vars[GlobalSearchRegression.get_column_index(:_cons, data.expvars)] = true
     end
@@ -30,7 +31,7 @@ function lasso!(data::GlobalSearchRegression.GSRegData)
     data.expvars = data.expvars[vars]
     data.expvars_data = data.expvars_data[:,vars]
     
-    data = addextras(data)
+    data = addextras(data, lassonumvars)
 
     return data, vars
 end

### 2019-07-19 src/PreliminarySelection/utils.jl

@@ -1,9 +1,10 @@
 """
 Add values to extras
 """
-function addextras(data)
+function addextras(data, lassonumvars)
     data.extras[GlobalSearchRegression.generate_extra_key(PRELIMINARYSELECTION_EXTRAKEY, data.extras)] = Dict(
-        :enabled => true
+        :enabled => true,
+        :lassonumvars => lassonumvars
     )
     return data
 end

### 2019-07-19 src/Preprocessing/utils.jl

@@ -205,7 +205,7 @@ Add values to extras
 """
 function addextras(data, method, seasonaladjustment, removeoutliers)
     data.extras[GlobalSearchRegression.generate_extra_key(PREPROCESSING_EXTRAKEY, data.extras)] = Dict(
-        :equation => vcat(data.depvar, data.expvars),
+        :datanames => vcat(data.depvar, data.expvars),
         :depvar => data.depvar,
         :expvars => data.expvars,
         :data => DEFAULT_DATANAME,

### 2019-07-19 test/AllSubsetRegression/runtests.jl

@@ -1,0 +1,13 @@
+using Test, CSV, DelimitedFiles, GlobalSearchRegression
+
+data_small = CSV.read(DATABASE_SMALL)
+
+@testset "AllSubsetRegression" begin
+    @testset "With T-test" begin
+        res = gsr("y x*", data_small, ttest=true)
+
+        @show res.results[1]
+
+        @test 1 == 1
+    end
+end

### 2019-07-19 test/dummy_test.jl

@@ -1,5 +1,15 @@
 using CSV, GlobalSearchRegression, Distributed
 
 data = CSV.read("data/small.csv")
-@time data = GlobalSearchRegression.gsr("y x*", data, kfoldcrossvalidation=true)
-GlobalSearchRegression.Output.latex(data, "./")
+@time data = GlobalSearchRegression.gsr("y x*", 
+    data, 
+    ttest=true, 
+    kfoldcrossvalidation=true, 
+    residualtest=true,
+    removeoutliers=true,
+    outsample=10,
+    modelavg=true,
+    preliminaryselection=:lasso
+
+)
+GlobalSearchRegression.Output.latex(data, "./Latex")

### 2019-07-23 test/Latex/main.tex
Full integration

--- 2019-07-19 src/Output/decorations/latex/tpl.tex
@@
       GlobalSearchRegression.gsr(
-        {{#input}}
-        equation = "{{equation}}",
-        data = {{data}},
-        datanames = {{datanames}},
-        method = :{{method}},
-        intercept = {{intercept}},
-        {{#panel}}panel = {{.}},{{/panel}}
-        {{#time}}time = {{.}},{{/time}}
-        {{#seasonaladjustment}}seasonaladjustment = {{.}},{{/seasonaladjustment}}
-        removeoutliers = {{removeoutliers}},
-        {{/input}}
+        equation = "y x1 x2 x3 x4 x5",
+        data = dataname,
+        datanames = [:y, :x1, :x2, :x3, :x4, :x5, :_cons],
+        method = :fast,
+        intercept = true,
+
+        removeoutliers = true,
 
@@
 
-{{#input}}
 \subsection{Pre-processing}
@@
 
-  {{#seasonalfortex}}
-    \item Seasonal-adjustment: variables {{#:fe_seasonaladjustment_names}}{{.}}, {{/:fe_seasonaladjustment_names}}have been selected for seasonal adjustment using \verb SingularSpectrumAnalysis.jl  (see \cite{hassani2007}).
-For each one, the function removes the seasonal component using window lengths equal to {{#:fe_seasonaladjustment_vals}}{{.}}, {{/:fe_seasonaladjustment_vals}}respectively.
-  {{/seasonalfortex}}
-
-  {{#seasonalfortex2}}
-  \item Seasonal-adjustment: variable {{#:fe_seasonaladjustment_names2}}{{.}}{{/:fe_seasonaladjustment_names2}} has been selected for seasonal adjustment using \verb SingularSpectrumAnalysis.jl  (see \cite{hassani2007}).
-The function removes the seasonal component using a window length equal to {{#:fe_seasonaladjustment_vals2}}{{.}}{{/:fe_seasonaladjustment_vals2}}.
-  {{/seasonalfortex2}}
-
-  {{#removeoutliers}} 
   \item Remove-outliers: extreme observations (because of input errors or extraordinary/non-relevant events) have been removed using the standard 3-sigma rule (see \cite{lehmann2013}).
-  {{/removeoutliers}}
 \end{enumerate}
-{{/input}}
-{{#featureextraction}}
-\subsection{Feature extraction}
-
-In this stage, selected functions have been used to create additional covariates with the following transformations:
-
-\begin{enumerate}
-  {{#fe_lag}}
-    {{#vars}}
-    \item Lags: for variables {{#names}}{{.}}, {{/names}}the lag operator created lag polinominals of order {{#values}}{{.}}, {{/values}}respectively, as additional explanatory variables.
-    {{/vars}}
-    {{#var}}
-    \item Lags: for variable {{#names}}{{.}}{{/names}}, the lag operator created a lag polinominal of order {{#values}}{{.}}{{/values}}, as an additional explanatory variable.
-    {{/var}}
-  {{/fe_lag}}
-  {{#fe_log}}
-    {{#vars}}
-    \item Logs: for variables {{#names}}{{.}}, {{/names}}the logarithm transformation was applied to generate new covariates.
-    {{/vars}}
-    {{#var}}
-    \item Logs: for variable {{#names}}{{.}}{{/names}}, the logarithm transformation was applied to generate a new covariate.
-    {{/var}}
-  {{/fe_log}}
-  {{#fe_inv}}
-    {{#vars}}
-    \item Inverse: for variables {{#names}}{{.}}, {{/names}}the inverse function was implemented to create additional covariates.
-    {{/vars}}
-    {{#var}}
-    \item Inverse: for variable {{#names}}{{.}}{{/names}}, the inverse function was implemented to create an additional covariate.
-    {{/var}}
-  {{/fe_inv}}
-  {{#fe_sqr}}
-    {{#vars}}
-    \item Squares: for variables {{#names}}{{.}}, {{/names}}the square transformation was implemented to create additional explanatory variables.
-    {{/vars}}
-    {{#var}}
-    \item Squares: for variable {{#names}}{{.}}{{/names}}, the square transformation was implemented to create an additional explanatory variable.
-    {{/var}}
-  {{/fe_sqr}} 
-  {{#interaction}}
-    {{#vars}}
-    \item Interactions: for variables {{#names}}{{.}}, {{/names}}all possible first-level interactions were created as additional covariates.
-    {{/vars}}
-    {{#var}}
-    \item Interactions: for variable {{#names}}{{.}}{{/names}}, all possible first-level interactions were created as an additional covariate.
-    {{/var}}
-  {{/interaction}}
-\end{enumerate}
-{{/featureextraction}}
-{{#preliminaryselection}}
 \subsection{Regularization - LASSO}
@@
 
-In this report, the $\lambda$ parameter has been dynamically defined in order to retain up to {{lassonumvars}} covariates.
+In this report, the $\lambda$ parameter has been dynamically defined in order to retain up to 6 covariates.
 
 It must be noticed that all predictors are standardized "on-the-fly", in order to avoid scale issues in feature selection.
-{{/preliminaryselection}}
 
-{{#allsubsetregression}}
 \subsection{All-subset-Regression}
@@
 Users are free to combine in-sample and out-of-sample information criteria.
-In this report, selected information criteria include ({{#criteria_names}}{{.}}, {{/criteria_names}}the key variable/s for feature selection.
+In this report, selected information criteria include (the key variable/s for feature selection.
 
@@
 \begin{enumerate}
-  {{#intercept}}
   \item Intercept has been included in all models. Alternatively, users could erase it by selecting the intercept=false boolean option.
-  {{/intercept}}
-  {{#outsample}}
-  \item The outsample option identifies how many observations are used for prediction purposes. In this case, it has been set to {{outsample}}.
-  {{/outsample}}
-  {{#ttest}}
+  \item The outsample option identifies how many observations are used for prediction purposes. In this case, it has been set to 10.
   \item The user's choice has been ttest=true. Therefore, standard deviation, ttest parameters and related probabilities has been calculated.
-  {{/ttest}}
-  {{#modelavg}}
   \item Across-models' average coefficients, t-tests and additional statistics were obtained using combined-criteria exponential weights because of the modelavg=true option.
 More precisely, each alternative model has a weight given by w1/sum(w1), where w1 is defined as exp(-delta/2) and delta is equal to max(index)-index -- where index is the above mentioned normalized, harmonized and potentially combined selection criteria--.
-  {{/modelavg}}
-  {{#residualtest}}
   \item The residualtest=true option enables white heteroskedasticity and Jarque-Bera normality test to be implemented for each model.
-  {{/residualtest}}
-  {{#residualtest}}
   \item The residualtest=true option enables white heteroskedasticity, Jarque-Bera normality test and the Breusch-Godfrey test for autocorrelation to be implemented for each model.
-  {{/residualtest}}
-  {{#orderresults}}  
-  \item User's specification of orderresults=true entails that the output matrix has been sorted by the the above mentioned normalized, harmonized and potentially combined selection criteria.
-  {{/orderresults}}
 \end{enumerate}
-{{/allsubsetregression}}
 
@@
 
-{{#crossvalidation}}
 \subsection{K-fold Cross Validation}
@@
 Among different alternatives, the K-fold approach has a parameter $K$ which identifies the number of groups that a given database must be split into (see \cite{arlot2010}).
-In this report user selected k-fold number is {{kfolds}}.
+In this report user selected k-fold number is 5.
 
@@
 
-{{#time}}
-For time series, however, this methodology could decrease model selection accuracy because -potential- serial correlation violate the cross-validation fundamental assumption of i.i.d.
-data (see \cite{bergmeir2012}).
-Among available alternatives, most widely used are non-dependent k-fold cross-validation (see \cite{bergmeir2018}) and rolling forecast origin cross-validation (based on \cite{hyndman2013}).
-Unfortunately, the  first one entails an inefficient use of available information and second one has comparison problems for the above mentioned ACV approach (because each sampling partition has a different training set size).
-Therefore, \verb GlobalSearchRegression.jl uses a slightly modified version of the rolling forecast origin cross-validation, with the following steps:
-
-\begin{enumerate}
-\item User defines the rolling test-set share ($s1$) and the number of sub-samples (K);
-\item Therefore, the rolling training-set share ($s2$) is automatically obtained from:
-
-\begin{equation}
-  T=s1 \times T+s2 \times T+(K-1)
-\end{equation}
-or
-\begin{equation}
-  s2=(1-s1)-[(K-1)/T]
-\end{equation}
-where $T$ is the total number of observations.
-\item Rolling sub-samples are defined using the following pseudo-code (where data is supossed to be a time-sorted matrix/array/dataframe.):
-
-\begin{algorithm}
-\caption*{\textbf{Cross validation pseudo-code 1}: Rolling sub-samples for time series}
-\begin{itemize}
-  \item[] for $i=1:K$
-  \begin{itemize}
-    \item[]  Training\_i=data[i:s2*T,:]
-    \item[] Test\_i=data[(s2 \times T+i):((s2 \times T+i)+(s1 \times T)-1),:]
-  \end{itemize}
-  \item[] end
-\end{itemize}
-\end{algorithm}
-
-\item For each sub-sample:
-
-\begin{enumerate}
-\item the first $s_{2}*T$ observations are used to train the model and the subsequent $s_{1}*T$ observations are retained to test model accuracy and compute the out-of-sample RMSE;
-\item the "best candidate" (across different covariate combinations) is the model which minimizes the out-of-sample RMSE;
-\end{enumerate}
-\item Finally, the cross-validated best model is obtained averaging (or using median) coefficients and standard deviations across the K-best candidates.
-\end{enumerate}
-
-In this report the test size has been set to {{tsetsize}} and, as already mentioned,
-selected k-fold number is {{kfolds}}.
-{{/time}}
-{{#panelid}}
-For panel data, cross-validation techniques are similar to time-series ones, but stratified by panel-id (because panel databases can be unbalanced).
-More precisely, the cross-validation strategy is defined by:
-
-\begin{enumerate}
-\item As for time series, user defines the rolling test-set share ($s1$) and the number of sub-samples (K);
-\item But the rolling training-set share ($s2$) is obtained from a slightly modified equation:
-\begin{equation}
-  \forall j, s2=(1-s1)-[(K-1)/T{j}] 
-\end{equation}
-where $T{j}$ is the total number of time series observations for panel-id = j.
-\item Therefore, rolling sub-samples are defined as (once again, data should be time-sorted matrix/array/dataframe):
-
-\begin{algorithm}
-\caption*{\textbf{Cross validation pseudo-code 2}: Rolling sub-samples for panel data}
-\begin{itemize}
-    \item[] for $i=1:K$
-    \begin{itemize}
-        \item[]  for $j=1:Q$
-        \begin{itemize}
-            \item[] Training\_i\_j=data[i:s2 \times T{j},:]
-            \item[] Test\_i\_j=data[(s2 \times T{j}+i):((s2 \times T{j}+i)+(s1 \times T{j})-1),:]
-        \end{itemize}
-        \item[] end
-    \end{itemize}
-    \item[] end
-\end{itemize}     
-\end{algorithm}
-
-\item For each sub-sample K, the time series methodology is reproduce henceforth.
-\end{enumerate}
-{{/panelid}}
-{{/crossvalidation}}
-
-{{#input}}
 \section{Descriptive Statistics}
@@
     \hline
-    {{#descriptive}}{{^name}}
+    x1 & Insert Description & 96 & -0.03 & 1.08 & 2.29 & -2.76 & 0.00\% \\ 
+    x2 & Insert Description & 96 & -0.11 & 0.90 & 1.61 & -2.31 & 0.00\% \\ 
+    x3 & Insert Description & 96 & -0.10 & 0.95 & 2.15 & -2.38 & 0.00\% \\ 
+    x4 & Insert Description & 96 & 0.13 & 1.00 & 2.63 & -2.73 & 0.00\% \\ 
+    x5 & Insert Description & 96 & -0.09 & 0.84 & 1.80 & -2.48 & 0.00\% \\ 
+    _cons & Insert Description & 96 & 1.00 & 0.00 & 1.00 & 1.00 & 0.00\% \\ 
     \hline
@@
 
-\clearpage
-
-\begin{table}[!h]
-  \centering
-  \caption{Descriptive Statistics for the main dataset (cont.)}
-    \begin{tabular}{|p{2cm}|p{4cm}|c|c|c|c|c|c|}
-    \hline
-    Variable & Description & Obs. & Mean & Sd & Max & Min & \% Miss \\
-    \hline
-    \hline
-    {{/name}}{{#name}}{{name}} & Insert Description & {{nobs}} & {{mean}} & {{std}} & {{max}} & {{min}} & {{miss}}\% \\ 
-    {{/name}}{{/descriptive}}\hline
-    \end{tabular}
-\end{table}
-{{/input}}
-
-{{#preliminaryselection}}
 \section{Regularization results}
@@
               & \\
-    Variables & {{ depvar }} \\
+    Variables & y \\
     \hline
     \hline
-    {{#expvars}}
-      {{ name }} & {{ coef }} \\
-    {{/expvars}}
+       &  \\
+       &  \\
+       &  \\
+       &  \\
+       &  \\
+       &  \\
     \hline
     \hline
-    Observations &  {{ nobs }} \\
-    \lambda      &  {{ lambda }} \\
+    Observations &  96 \\
+    \lambda      &   \\
     \hline
@@
 \end{table}
-{{/preliminaryselection}}
 
-{{#allsubsetregression}}
 \section{Global Search Regression}
@@
   \caption{GSReg results}
-    {{#bestmodel}}
 
-    \begin{tabular}{l c{{#modelavg}} c{{/modelavg}}}
+    \begin{tabular}{l c c}
     \hline
     \hline
-                 &  Best Model              {{#modelavg}} & Model Averaging           {{/modelavg}} \\
-    Variables    &  {{depvar}}              {{#modelavg}} & {{depvar}}                {{/modelavg}} \\
-    \hline{{#bmexpvars}} 
-    {{name}}     & {{best.b}}{{best.stars}} {{#avg}} & {{b}}{{stars}}    {{/avg}} \\{{#ttest}}
-                 & {{best.bstd}}            {{#avg}} & {{bstd}} {{/avg}} \\{{/ttest}}
-    {{/bmexpvars}}\hline
+                 &  Best Model               & Model Averaging            \\
+    Variables    &  y               & y                 \\
+    \hline 
+    x1     & -0.121***  & -0.126***     \\
+                 &              & 0.103  \\
 
-    Observations &   \multicolumn{ {{^avg}}1{{/avg}} {{#avg}}2{{/avg}} }{c}{ } \\
-    Criteria     &   \multicolumn{ {{^avg}}1{{/avg}} {{#avg}}2{{/avg}} }{c}{ } \\
+    x2     &   & -0.012***     \\
+                 &              & 0.118  \\
+
+    x3     & 0.108*  & 0.109*     \\
+                 &              & 0.114  \\
+
+    x4     & 0.169*  & 0.152*     \\
+                 &              & 0.111  \\
+
+    x5     &   & -0.083***     \\
+                 &              & 0.136  \\
+
+    _cons     & 0.142*  & 0.146*     \\
+                 &              & 0.109  \\
+    \hline
+
+    Observations &   \multicolumn{ 1  }{c}{ } \\
+    Criteria     &   \multicolumn{ 1  }{c}{ } \\
     \hline
     \hline
-    \multicolumn{ {{^avg}}2{{/avg}} {{#avg}}3{{/avg}} }{c}{Standard errors in parentheses} \\
-    \multicolumn{ {{^avg}}2{{/avg}} {{#avg}}3{{/avg}} }{c}{*** p < 0.01, ** p < 0.05, * p < 0.1} \\
+    \multicolumn{ 2  }{c}{Standard errors in parentheses} \\
+    \multicolumn{ 2  }{c}{*** p < 0.01, ** p < 0.05, * p < 0.1} \\
     \end{tabular}
-    {{/bestmodel}}
   \label{tab:addlabel}
@@
 
-{{#expvars}}
 \begin{center}
-    \large{\textbf{Coefficient, t-test and selection criteria gains distributions for {{name}} }}
+    \large{\textbf{Coefficient, t-test and selection criteria gains distributions for  }}
 \end{center}
@@
     \centering
-    \includegraphics[width=\textwidth]{contour_{{name}}_b_t.png}
+    \includegraphics[width=\textwidth]{contour__b_t.png}
     \caption{Bivariate Kernel density (Contour view)}
@@
     \centering
-    \includegraphics[width=\textwidth]{wireframe_{{name}}_b_t.png}
+    \includegraphics[width=\textwidth]{wireframe__b_t.png}
     \caption{Bivariate Kernel density (Contour view)}
@@
     \centering
-    \includegraphics[width=\textwidth]{Kdensity_criteria_{{name}}.png}
-    \caption{Selection criteria gains for including {{name}} (Kernel view)}
+    \includegraphics[width=\textwidth]{Kdensity_criteria_.png}
+    \caption{Selection criteria gains for including  (Kernel view)}
   \end{minipage}
@@
     \centering    
-    \includegraphics[width=\textwidth]{BoxViolinDot_{{name}}.png}
-    \caption{Selection criteria gains for including {{name}} (Box-Violin view)}    
+    \includegraphics[width=\textwidth]{BoxViolinDot_.png}
+    \caption{Selection criteria gains for including  (Box-Violin view)}    
   \end{minipage}
@@
     \hline
-    Variable {{name}} Statistics &  Coefficient Distribution &  T-test Distribution  \\
+    Variable  Statistics &  Coefficient Distribution &  T-test Distribution  \\
     \hline
     \hline
-    Simple average    & {{b.avg}}      & {{t.avg}} \\
+    Simple average    &       &  \\
     \hline
-    Median            & {{b.median}}   & {{t.median}} \\
+    Median            &    &  \\
     \hline
-    Mode              & {{b.mode}}     & {{t.mode}} \\
+    Mode              &      &  \\
     \hline
-    Skewness          & {{b.std}}      & {{t.std}} \\
+    Skewness          &       &  \\
     \hline
-    kurtosis          & {{b.skew}}     & {{t.skew}} \\
+    kurtosis          &      &  \\
     \hline
-    Positive Share    & {{b.kurt}}     & {{t.kurt}} \\
+    Positive Share    &      &  \\
     \hline
-    Significant Share & {{b.posshare}} & {{t.sigshare}} \\
+    Significant Share &  &  \\
     \hline
@@
 \clearpage
-{{/expvars}}
+\begin{center}
+    \large{\textbf{Coefficient, t-test and selection criteria gains distributions for  }}
+\end{center}
+
+\vspace{-5mm}
+
+\begin{figure}[!ht]
+  \centering
+  \begin{minipage}[b]{0.46\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{contour__b_t.png}
+    \caption{Bivariate Kernel density (Contour view)}
+  \end{minipage}
+  \hfill
+  \begin{minipage}[b]{0.53\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{wireframe__b_t.png}
+    \caption{Bivariate Kernel density (Contour view)}
+  \end{minipage}
+
+  \begin{minipage}[b]{0.48\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Kdensity_criteria_.png}
+    \caption{Selection criteria gains for including  (Kernel view)}
+  \end{minipage}
+  \hfill
+  \begin{minipage}[b]{0.48\textwidth}
+    \centering    
+    \includegraphics[width=\textwidth]{BoxViolinDot_.png}
+    \caption{Selection criteria gains for including  (Box-Violin view)}    
+  \end{minipage}
+\end{figure}
+
+\vspace{1cm}
+
+The following table shows main statistics of coefficient and t-test distribution
+
+\begin{table}[!h]
+    \centering
+    \caption{Statistics}
+    \begin{tabular}{|l|c|c|}
+    \hline
+    Variable  Statistics &  Coefficient Distribution &  T-test Distribution  \\
+    \hline
+    \hline
+    Simple average    &       &  \\
+    \hline
+    Median            &    &  \\
+    \hline
+    Mode              &      &  \\
+    \hline
+    Skewness          &       &  \\
+    \hline
+    kurtosis          &      &  \\
+    \hline
+    Positive Share    &      &  \\
+    \hline
+    Significant Share &  &  \\
+    \hline
+    \end{tabular}
+\end{table}
+
+\clearpage
+\begin{center}
+    \large{\textbf{Coefficient, t-test and selection criteria gains distributions for  }}
+\end{center}
+
+\vspace{-5mm}
+
+\begin{figure}[!ht]
+  \centering
+  \begin{minipage}[b]{0.46\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{contour__b_t.png}
+    \caption{Bivariate Kernel density (Contour view)}
+  \end{minipage}
+  \hfill
+  \begin{minipage}[b]{0.53\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{wireframe__b_t.png}
+    \caption{Bivariate Kernel density (Contour view)}
+  \end{minipage}
+
+  \begin{minipage}[b]{0.48\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Kdensity_criteria_.png}
+    \caption{Selection criteria gains for including  (Kernel view)}
+  \end{minipage}
+  \hfill
+  \begin{minipage}[b]{0.48\textwidth}
+    \centering    
+    \includegraphics[width=\textwidth]{BoxViolinDot_.png}
+    \caption{Selection criteria gains for including  (Box-Violin view)}    
+  \end{minipage}
+\end{figure}
+
+\vspace{1cm}
+
+The following table shows main statistics of coefficient and t-test distribution
+
+\begin{table}[!h]
+    \centering
+    \caption{Statistics}
+    \begin{tabular}{|l|c|c|}
+    \hline
+    Variable  Statistics &  Coefficient Distribution &  T-test Distribution  \\
+    \hline
+    \hline
+    Simple average    &       &  \\
+    \hline
+    Median            &    &  \\
+    \hline
+    Mode              &      &  \\
+    \hline
+    Skewness          &       &  \\
+    \hline
+    kurtosis          &      &  \\
+    \hline
+    Positive Share    &      &  \\
+    \hline
+    Significant Share &  &  \\
+    \hline
+    \end{tabular}
+\end{table}
+
+\clearpage
+\begin{center}
+    \large{\textbf{Coefficient, t-test and selection criteria gains distributions for  }}
+\end{center}
+
+\vspace{-5mm}
+
+\begin{figure}[!ht]
+  \centering
+  \begin{minipage}[b]{0.46\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{contour__b_t.png}
+    \caption{Bivariate Kernel density (Contour view)}
+  \end{minipage}
+  \hfill
+  \begin{minipage}[b]{0.53\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{wireframe__b_t.png}
+    \caption{Bivariate Kernel density (Contour view)}
+  \end{minipage}
+
+  \begin{minipage}[b]{0.48\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Kdensity_criteria_.png}
+    \caption{Selection criteria gains for including  (Kernel view)}
+  \end{minipage}
+  \hfill
+  \begin{minipage}[b]{0.48\textwidth}
+    \centering    
+    \includegraphics[width=\textwidth]{BoxViolinDot_.png}
+    \caption{Selection criteria gains for including  (Box-Violin view)}    
+  \end{minipage}
+\end{figure}
+
+\vspace{1cm}
+
+The following table shows main statistics of coefficient and t-test distribution
+
+\begin{table}[!h]
+    \centering
+    \caption{Statistics}
+    \begin{tabular}{|l|c|c|}
+    \hline
+    Variable  Statistics &  Coefficient Distribution &  T-test Distribution  \\
+    \hline
+    \hline
+    Simple average    &       &  \\
+    \hline
+    Median            &    &  \\
+    \hline
+    Mode              &      &  \\
+    \hline
+    Skewness          &       &  \\
+    \hline
+    kurtosis          &      &  \\
+    \hline
+    Positive Share    &      &  \\
+    \hline
+    Significant Share &  &  \\
+    \hline
+    \end{tabular}
+\end{table}
+
+\clearpage
+\begin{center}
+    \large{\textbf{Coefficient, t-test and selection criteria gains distributions for  }}
+\end{center}
+
+\vspace{-5mm}
+
+\begin{figure}[!ht]
+  \centering
+  \begin{minipage}[b]{0.46\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{contour__b_t.png}
+    \caption{Bivariate Kernel density (Contour view)}
+  \end{minipage}
+  \hfill
+  \begin{minipage}[b]{0.53\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{wireframe__b_t.png}
+    \caption{Bivariate Kernel density (Contour view)}
+  \end{minipage}
+
+  \begin{minipage}[b]{0.48\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Kdensity_criteria_.png}
+    \caption{Selection criteria gains for including  (Kernel view)}
+  \end{minipage}
+  \hfill
+  \begin{minipage}[b]{0.48\textwidth}
+    \centering    
+    \includegraphics[width=\textwidth]{BoxViolinDot_.png}
+    \caption{Selection criteria gains for including  (Box-Violin view)}    
+  \end{minipage}
+\end{figure}
+
+\vspace{1cm}
+
+The following table shows main statistics of coefficient and t-test distribution
+
+\begin{table}[!h]
+    \centering
+    \caption{Statistics}
+    \begin{tabular}{|l|c|c|}
+    \hline
+    Variable  Statistics &  Coefficient Distribution &  T-test Distribution  \\
+    \hline
+    \hline
+    Simple average    &       &  \\
+    \hline
+    Median            &    &  \\
+    \hline
+    Mode              &      &  \\
+    \hline
+    Skewness          &       &  \\
+    \hline
+    kurtosis          &      &  \\
+    \hline
+    Positive Share    &      &  \\
+    \hline
+    Significant Share &  &  \\
+    \hline
+    \end{tabular}
+\end{table}
+
+\clearpage
+\begin{center}
+    \large{\textbf{Coefficient, t-test and selection criteria gains distributions for  }}
+\end{center}
+
+\vspace{-5mm}
+
+\begin{figure}[!ht]
+  \centering
+  \begin{minipage}[b]{0.46\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{contour__b_t.png}
+    \caption{Bivariate Kernel density (Contour view)}
+  \end{minipage}
+  \hfill
+  \begin{minipage}[b]{0.53\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{wireframe__b_t.png}
+    \caption{Bivariate Kernel density (Contour view)}
+  \end{minipage}
+
+  \begin{minipage}[b]{0.48\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Kdensity_criteria_.png}
+    \caption{Selection criteria gains for including  (Kernel view)}
+  \end{minipage}
+  \hfill
+  \begin{minipage}[b]{0.48\textwidth}
+    \centering    
+    \includegraphics[width=\textwidth]{BoxViolinDot_.png}
+    \caption{Selection criteria gains for including  (Box-Violin view)}    
+  \end{minipage}
+\end{figure}
+
+\vspace{1cm}
+
+The following table shows main statistics of coefficient and t-test distribution
+
+\begin{table}[!h]
+    \centering
+    \caption{Statistics}
+    \begin{tabular}{|l|c|c|}
+    \hline
+    Variable  Statistics &  Coefficient Distribution &  T-test Distribution  \\
+    \hline
+    \hline
+    Simple average    &       &  \\
+    \hline
+    Median            &    &  \\
+    \hline
+    Mode              &      &  \\
+    \hline
+    Skewness          &       &  \\
+    \hline
+    kurtosis          &      &  \\
+    \hline
+    Positive Share    &      &  \\
+    \hline
+    Significant Share &  &  \\
+    \hline
+    \end{tabular}
+\end{table}
+
+\clearpage
 
@@
 For each explanatory variable information criteria gains were obtained as the differece between averages information criteria obtained from models which includes and excludes that covariate.
-Available statistics suggests that there {{are or is}} {{numofpositivegainsvariables}} explanatory {{variable or variables}} that improved model accuracy.
-{{Among them, {{bestvar}} or {{bestvar}}}} helps to increase up to a {{gainsinperc}}\% the user selected information criteria.
-On the contrary, there {{are or is}} {{numofnegativegainsvariables}} {{covariate or covariates}} that have a deleterious impact on model accuracy.
-This is specially true for {{worstvar}}, which seems to decrease up to a {{lossinperc}}\% the user selected information criteria}}
-{{/allsubsetregression}}
+Available statistics suggests that there   explanatory  that improved model accuracy.
+or }} helps to increase up to a \% the user selected information criteria.
+On the contrary, there    that have a deleterious impact on model accuracy.
+This is specially true for , which seems to decrease up to a \% the user selected information criteria}}
 
-{{#crossvalidation}}
 \section{k-fold cross-validation}
@@
     \multicolumn{3}{c}{K-fold scheme:\textbf{Insert scheme}} \\
-                 & {{kfolds}}-fold  & {{kfolds}}-fold \\
+                 & 5-fold  & 5-fold \\
     Variables    & Mean             & Median          \\
@@
 \end{table}
-{{/crossvalidation}}
 

### 2019-07-23 src/AllSubsetRegression/const.jl

@@ -1,5 +1,5 @@
 const ALLSUBSETREGRESSION_EXTRAKEY = :allsubsetregression
-const FIXEDVARIABLES_DEFAULT = []
+const FIXEDVARIABLES_DEFAULT = nothing
 const INSAMPLE_MIN = 20
 const OUTSAMPLE_DEFAULT = 20
 const CRITERIA_DEFAULT = []

### 2019-07-23 src/AllSubsetRegression/estimators/ols.jl

@@ -1,6 +1,6 @@
 function ols(
         data::GlobalSearchRegression.GSRegData;
-        fixedvariables::Array=FIXEDVARIABLES_DEFAULT,
+        fixedvariables::Union{Nothing, Array}=FIXEDVARIABLES_DEFAULT,
         outsample=OUTSAMPLE_DEFAULT,
         criteria::Array=CRITERIA_DEFAULT,
         ttest::Bool=TTEST_DEFAULT,
@@ -23,7 +23,7 @@ end
 
 function ols!(
     data::GlobalSearchRegression.GSRegData;
-    fixedvariables::Array=FIXEDVARIABLES_DEFAULT,
+    fixedvariables::Union{Nothing, Array}=FIXEDVARIABLES_DEFAULT,
     outsample=OUTSAMPLE_DEFAULT,
     criteria::Array=CRITERIA_DEFAULT,
     ttest::Bool=TTEST_DEFAULT,

### 2019-07-23 src/Preprocessing/core.jl

@@ -272,6 +272,12 @@ function execute(
         end
     end
 
+    if seasonaladjustment != nothing && time != nothing
+        seasonal_adjustments(data, seasonaladjustment, datanames)
+    elseif seasonaladjustment != nothing && time == nothing
+        error(TIME_VARIABLE_INEXISTENT)
+    end
+
     (data, datanames) = filter_data_by_selected_columns(data, equation, datanames)
 
     depvar = equation[1]
@@ -287,10 +293,6 @@ function execute(
 
     if removeoutliers
         remove_outliers(data)
-    end
-
-    if seasonaladjustment != nothing
-        seasonal_adjustments(data, seasonaladjustment, datanames)
     end
     
     depvar_data = data[1:end, 1]

### 2019-07-23 test/dummy_test.jl

@@ -1,15 +1,51 @@
 using CSV, GlobalSearchRegression, Distributed
 
-data = CSV.read("data/small.csv")
-@time data = GlobalSearchRegression.gsr("y x*", 
-    data, 
-    ttest=true, 
-    kfoldcrossvalidation=true, 
-    residualtest=true,
-    removeoutliers=true,
-    outsample=10,
-    modelavg=true,
-    preliminaryselection=:lasso
+using DataFrames, CSV
+ 
+data = DataFrame(Array{Union{Missing,Float64}}(randn(100,30)))
+data[1,2] = missing
+data[2,6] = missing
+data[3,2] = missing
+data[2,7] = 999999
+data[3,6] = 999999
+data[4,6] = 999999
+headers = [ :y ; [ Symbol("x$i") for i = 1:size(data,2) - 1 ] ]
 
+headers[3] = :positive
+headers[4] = :panel
+headers[5] = :time
+names!(data, headers)
+
+data[:,3] = data[:,3] .+ 10
+data[:,4] = collect(Iterators.flatten(fill(i,25) for i in 1:4))
+data[:,5] = collect(Iterators.flatten(1:25 for i in 1:4))
+
+@time data = GlobalSearchRegression.gsr(
+    "y x* positive", 
+    data,
+    method=:precise,
+    intercept=true,
+    panel=:panel,
+    time=:time,
+    seasonaladjustment=[:time => 4],
+    removeoutliers=true,
+    fe_sqr=[:x1],
+    fe_log=:positive,
+    fe_inv=:positive,
+    fe_lag=[:x10 => 1, :x11 => 2],
+    interaction=[:x11, :x12],
+    preliminaryselection=:lasso,
+    fixedvariables=nothing,
+    outsample=20,
+    criteria=[:r2adj, :bic, :aic, :aicc, :cp, :rmse, :rmseout, :sse],
+    ttest=true,
+    modelavg=true,
+    residualtest=true,
+    orderresults=true,
+    kfoldcrossvalidation=true,
+    numfolds=3
+    #testsetshare=nothing,
+    #exportcsv::Union{Nothing, String}=EXPORTCSV_DEFAULT,
+    #exportsummary::Union{Nothing, String}=EXPORTSUMMARY_DEFAULT
 )
-GlobalSearchRegression.Output.latex(data, path="./Latex")
+#GlobalSearchRegression.Output.latex(data, path="./Latex")

### 2019-07-23 test/Latex/main.tex
Output

@@
 --------------------------------------------------
-
-\subsection{K-fold Cross Validation}
-
-Cross-validation (CV) is a procedure used to examine feature selection robustness to re-sampling.
-Among different alternatives, the K-fold approach has a parameter $K$ which identifies the number of groups that a given database must be split into (see \cite{arlot2010}).
-In this report user selected k-fold number is 5.
-
-The general procedure is as follows:
-
-\begin{enumerate}
-  \item Randomly split the database into k disjoint -roughly equally sized- groups
-  \item For each group:
-  \begin{enumerate}
-    \item Take a group as a hold out or test data set (leave-one-out scheme);
-    \item Take the remaining groups together as a training data set;
-    \item Fit a model on the training set and evaluate it on the test set; and
-    \item Retain the evaluation (i.e out-of-sample Root Mean Square Error -RMSE-).
-  \end{enumerate}
-  \item Summarize model strengths using CV scores
-\end{enumerate}
-
-In \verb GlobalSearchRegression.jl  the K-fold cross-validation is available for both LASSO pre-selection and ASR final selection.
-In the latter, for each K-partition $2^{p} - 1$ alternative models are fitted (where p is the number of potential covariates included in the ASR algorithm) and the candidate ‘optimal’ model is selected using the out-of-sample Root Mean Square Error (obtained from the test set).
-Therefore, K-candidate models are retained (one for each K-partition).
-The final "best" model is obtained using either across-model averages or medians.
-
-This cross-validation specific alternative has been denominated as \textit{Averaging Cross validation (ACV)} by Jung and Hu (see, \cite{jung2015}). The authors found that:
-
-\begin{quote}
-"Due to the averaging effect, efficiency of the final parameter estimates obtained by ACV improves over that of the traditional K-fold CV.
-We note that parameter estimates of CV and ACV are identical when all the candidate ‘optimal’ models from ACV are identical to the model selected by the traditional CV."
-
-\hfill Jung and Hu (2015:168)
-\end{quote}
-
-It is worth mentioning that K-fold preferred methodologies change depending on whether cross-section, time-series or panel data observations are employed.
-For the first one, standard K-fold random allocation is the gold-standard (see \cite{arlot2010}).
 
@@
 \clearpage
-\begin{center}
-    \large{\textbf{Coefficient, t-test and selection criteria gains distributions for  }}
-\end{center}
-
-\vspace{-5mm}
-
-\begin{figure}[!ht]
-  \centering
-  \begin{minipage}[b]{0.46\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{contour__b_t.png}
-    \caption{Bivariate Kernel density (Contour view)}
-  \end{minipage}
-  \hfill
-  \begin{minipage}[b]{0.53\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{wireframe__b_t.png}
-    \caption{Bivariate Kernel density (Contour view)}
-  \end{minipage}
-
-  \begin{minipage}[b]{0.48\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{Kdensity_criteria_.png}
-    \caption{Selection criteria gains for including  (Kernel view)}
-  \end{minipage}
-  \hfill
-  \begin{minipage}[b]{0.48\textwidth}
-    \centering    
-    \includegraphics[width=\textwidth]{BoxViolinDot_.png}
-    \caption{Selection criteria gains for including  (Box-Violin view)}    
-  \end{minipage}
-\end{figure}
-
-\vspace{1cm}
-
-The following table shows main statistics of coefficient and t-test distribution
-
-\begin{table}[!h]
-    \centering
-    \caption{Statistics}
-    \begin{tabular}{|l|c|c|}
-    \hline
-    Variable  Statistics &  Coefficient Distribution &  T-test Distribution  \\
-    \hline
-    \hline
-    Simple average    &       &  \\
-    \hline
-    Median            &    &  \\
-    \hline
-    Mode              &      &  \\
-    \hline
-    Skewness          &       &  \\
-    \hline
-    kurtosis          &      &  \\
-    \hline
-    Positive Share    &      &  \\
-    \hline
-    Significant Share &  &  \\
-    \hline
-    \end{tabular}
-\end{table}
-
-\clearpage
 
@@
 This is specially true for , which seems to decrease up to a \% the user selected information criteria}}
-
-\section{k-fold cross-validation}
-
-\begin{table}[!h]
-  \centering
-  \caption{K-fold cross-validation Results}
-    \begin{tabular}{l c c}
-    \hline
-    \multicolumn{3}{c}{K-fold scheme:\textbf{Insert scheme}} \\
-                 & 5-fold  & 5-fold \\
-    Variables    & Mean             & Median          \\
-    \hline
-    \hline
-                 &                  &                  \\
-                 &                  &                  \\
-    \hline
-
-    Error out-sample &     &   \\
-    Error in-sample  &     &   \\
-                     &     &   \\
-    \hline
-    \hline
-    \multicolumn{3}{c}{\textit{Standard errors in parentheses}} \\
-    \multicolumn{3}{c}{*** p < 0.01, ** p < 0.05, * p < 0.1} \\
-    \hline
-    \end{tabular}
-  \label{tab:addlabel}
-\end{table}
 

### 2019-07-23 src/Output/Output.jl
Output

@@ -1,5 +1,6 @@
 module Output
-    using DelimitedFiles, Printf, Statistics, Mustache
+    using DelimitedFiles, Printf, Statistics, Mustache, KernelDensity, Distributions, StatsPlots, ZipFile, InfoZIP
+    using Plots
     using ..GlobalSearchRegression
 
     export csv, summary, latex

### 2019-07-23 src/Output/decorations/latex/latex.jl

@@ -9,9 +9,12 @@ function latex(data::GlobalSearchRegression.GSRegData; path::Union{Nothing, Stri
         for i in 1:size(data.results, 1)
             latex!(dict, data, data.results[i])
         end
-        #render_plots(dict, data)
         create_workspace(path)
+        if data.results[1].ttest
+            create_figures(data, path)
+        end
         render_latex(dict, path)
+        zip_folder(path)
     end
 end
 
@@ -248,21 +251,28 @@ function render_latex(dict, destfolder::AbstractString)
     close(io)
 end
 
-dropnans(res, var) = res.results[findall(x -> !isnan(x), res.results[:, res.header[var]]), res.header[var]]
+function zip_folder(destfolder::AbstractString)
+    create_zip(joinpath(destfolder,"GSREG.zip"), map(p->joinpath(destfolder, p),readdir(destfolder)))
+end
 
 """
 Create required figures by the template. Generate png images into the dest folder
 """
-function create_figures(res, destfolder)
-    expvars2 = res.expvars[:,1]
-    expvars2 = deleteat!(expvars2, findfirst(isequal(:_cons), expvars2))
+function create_figures(data, destfolder)
+    expvars2 = data.expvars
+    deleteat!(expvars2, GlobalSearchRegression.get_column_index(:_cons, data.expvars))
+
     criteria_diff = Array{Any}(undef, size(expvars2,1), 2)
 
     for (i, expvar) in enumerate(expvars2)
-        x = dropnans(res, Symbol("$(expvar)_b"))
-        y = dropnans(res, Symbol("$(expvar)_t"))
+        bcol = GlobalSearchRegression.get_column_index(Symbol("$(expvar)_b"), data.results[1].datanames)
+        tcol = GlobalSearchRegression.get_column_index(Symbol("$(expvar)_t"), data.results[1].datanames)
+        r2col = GlobalSearchRegression.get_column_index(:r2adj, data.results[1].datanames)
         
-        biden = kde( (x,y), npoints=(100,100))
+        x = data.results[1].data[findall(x -> !isnan(x), data.results[1].data[:, bcol]), bcol]
+        y = data.results[1].data[findall(x -> !isnan(x), data.results[1].data[:, tcol]), tcol]
+        
+        biden = kde((x, y), npoints=(100,100))
         
[…]

### 2019-07-23 src/Output/decorations/latex/tpl.tex
Output

@@
 merging algorithms from different families to reduce both sampling and model uncertainty-, we are developing a novel multi-layer-multi-algorithm methodology combining two reinforcing paradigms: The London School of Economics (LSE) “Testimation” approach -to obtain information about residual properties- and the Bayesian-like “Double-model averaging” -across different covariates and sub-samples.
-This methodology includes five complementary layers -handling cross-section, time series and panel data- see \cite{gsreg2019}: \begin{enumerate}
+This methodology includes five complementary layers -handling cross-section, time series and panel data- see \cite{gsreg2019}:
+
+\begin{enumerate}
     \item Pre-processing: with outlier detection, missing values identification, seasonal adjustment and normalization/standardization functions;
@@
   using GlobalSearchRegression
-      GlobalSearchRegression.gsr(
-        {{#input}}
+  GlobalSearchRegression.gsr({{#input}}
     equation = "{{equation}}",
@@
     method = :{{method}},
-        intercept = {{intercept}},
-        {{#panel}}panel = {{.}},{{/panel}}
-        {{#time}}time = {{.}},{{/time}}
-        {{#seasonaladjustment}}seasonaladjustment = {{.}},{{/seasonaladjustment}}
-        removeoutliers = {{removeoutliers}},
-        {{/input}}
-
-        fe_sqr
-        fe_log
-        fe_inv
-        fe_lag
-        interaction
-        preliminaryselection
-        fixedvariables
-        outsample
-        criteria
-        ttest
-        modelavg
-        residualtest
-        orderresults
-        kfoldcrossvalidation
-        numfolds
-        testsetshare
-        exportcsv
-        exportsummary
+    intercept = {{intercept}},{{#panel}}
+    panel = {{.}},{{/panel}}{{#time}}
+    time = {{.}},{{/time}}{{#seasonaladjustment}}
+    seasonaladjustment = {{.}},{{/seasonaladjustment}}
+    removeoutliers = {{removeoutliers}},{{/input}}{{#featureextraction}}{{#fe_sqr}}
+    fe_sqr = {{.}},{{/fe_sqr}}{{#fe_log}}
+    fe_log = {{.}},{{/fe_log}}{{#fe_inv}}
+    fe_inv = {{.}},{{/fe_inv}}{{#fe_lag}}
+    fe_lag = {{.}},{{/fe_lag}}{{#interaction}}
+    interaction = {{.}},{{/interaction}}{{/featureextraction}}{{#preliminaryselection}}
+    preliminaryselection = :{{preliminaryselection}},{{/preliminaryselection}}{{#allsubsetregression}}{{#fixedvariables}}
+    fixedvariables = {{.}},{{/fixedvariables}}{{#outsample}}
+    outsample = {{.}},{{/outsample}}{{#criteria}}
+    criteria = {{.}},{{/criteria}}
+    ttest = {{ttest}},
+    modelavg = {{modelavg}},
+    residualtest = {{residualtest}},{{#orderresults}}
+    orderresults = {{.}},{{/orderresults}}{{/allsubsetregression}}{{#crossvalidation}}
+    kfoldcrossvalidation = {{.}},{{/crossvalidation}}{{#numfolds}}
+    numfolds = {{.}},{{/numfolds}}{{#testsetshare}}
+    testsetshare = {{.}}{{/testsetshare}}
+  )
 \end{lstlisting}
@@
 In section 3, descriptive statistics are introduced.
-In turn, section 4 is dedicated to LASSO results.
-In turn, section 4 is dedicated to All-subset-regression results.
-After that, section 5 shows All-subset-regression results.
-Finally, the last section examines K-fold cross-validation outcomes.
+{{#preliminaryselection}}After that, LASSO results are examined.{{/preliminaryselection}} Then, All-subset-regression analysis is shown.
+{{#crossvalidation}}Finally, the last section examines K-fold cross-validation outcomes.{{/crossvalidation}}
 
@@
 
-  {{#seasonalfortex}}
-    \item Seasonal-adjustment: variables {{#:fe_seasonaladjustment_names}}{{.}}, {{/:fe_seasonaladjustment_names}}have been selected for seasonal adjustment using \verb SingularSpectrumAnalysis.jl  (see \cite{hassani2007}).
-For each one, the function removes the seasonal component using window lengths equal to {{#:fe_seasonaladjustment_vals}}{{.}}, {{/:fe_seasonaladjustment_vals}}respectively.
-  {{/seasonalfortex}}
-
-  {{#seasonalfortex2}}
-  \item Seasonal-adjustment: variable {{#:fe_seasonaladjustment_names2}}{{.}}{{/:fe_seasonaladjustment_names2}} has been selected for seasonal adjustment using \verb SingularSpectrumAnalysis.jl  (see \cite{hassani2007}).
-The function removes the seasonal component using a window length equal to {{#:fe_seasonaladjustment_vals2}}{{.}}{{/:fe_seasonaladjustment_vals2}}.
-  {{/seasonalfortex2}}
+  {{#seasonaladjustment}}{{#seasonaladjustment}}
+    {{#vars}}
+      \item Seasonal-adjustment: variables {{#names}}{{.}}, {{/names}} have been selected for seasonal adjustment using \verb SingularSpectrumAnalysis.jl  (see \cite{hassani2007}).
+For each one, the function removes the seasonal component using window lengths equal to {{#values}}{{.}}, {{/values}}respectively.
+    {{/vars}}
+    {{#var}}
+      \item Seasonal-adjustment: variable {{#names}}{{.}}{{/names}}, has been selected for seasonal adjustment using \verb SingularSpectrumAnalysis.jl  (see \cite{hassani2007}).
+The function removes the seasonal component using a window length equal to {{#values}}{{.}}{{/values}}.
+    {{/var}}
+  {{/seasonaladjustment}}{{/seasonaladjustment}}
 
@@
 Users are free to combine in-sample and out-of-sample information criteria.
-In this report, selected information criteria include ({{#criteria_names}}{{.}}, {{/criteria_names}}the key variable/s for feature selection.
+In this report, selected information criteria include ({{criteria}}) as the key variable/s for feature selection.
 
@@
 {{/allsubsetregression}}
-
---------------------------------------------------
-
 {{#crossvalidation}}
@@
 {{/crossvalidation}}
-
 {{#input}}
@@
 \clearpage
-
-\section{Variables}
 
@@
     \hline
-    {{#expvars}}
+    {{#expvssars}}
       {{ name }} & {{ coef }} \\
-    {{/expvars}}
+    {{/expvssars}}
     \hline
@@
     Observations &  {{ nobs }} \\
-    \lambda      &  {{ lambda }} \\
+    \lambda      &  {{ lassolambda }} \\
     \hline
@@
 {{#allsubsetregression}}
+
+\clearpage
 \section{Global Search Regression}
@@
     \hline{{#bmexpvars}} 
-    {{name}}     & {{best.b}}{{best.stars}} {{#avg}} & {{b}}{{stars}}    {{/avg}} \\{{#ttest}}
-                 & {{best.bstd}}            {{#avg}} & {{bstd}} {{/avg}} \\{{/ttest}}
+    {{name}}     & {{#best}}{{b}}{{stars}}{{/best}} {{#avg}} & {{b}}{{stars}}    {{/avg}} \\{{#ttest}}
+                 & {{#best}}{{bstd}}{{/best}}       {{#avg}} & {{bstd}} {{/avg}} \\{{/ttest}}
     {{/bmexpvars}}\hline
 
-    Observations &   \multicolumn{ {{^avg}}1{{/avg}} {{#avg}}2{{/avg}} }{c}{ } \\
-    Criteria     &   \multicolumn{ {{^avg}}1{{/avg}} {{#avg}}2{{/avg}} }{c}{ } \\
+    Observations &   \multicolumn{ {{^avg}}1{{/avg}} {{#avg}}2{{/avg}} }{c}{ {{ nobs }} } \\
+    Criteria     &   \multicolumn{ {{^avg}}1{{/avg}} {{#avg}}2{{/avg}} }{c}{ {{ criteria }} } \\
     \hline
@@
 
-In this figure it is shown that potential covariates included in the general unrrestricted model of the all-subset-regression algorithm display singnificant differences in terms of the user selected information criteria.
+%In this figure it is shown that potential covariates included in the general unrrestricted model of the all-subset-regression algorithm display singnificant differences in terms of the user selected information criteria.
 For each explanatory variable information criteria gains were obtained as the differece between averages information criteria obtained from models which includes and excludes that covariate.
@@
     \hline
-                 &                  &                  \\
-                 &                  &                  \\
+{{ median }}
+
+--
+
+{{ average }}
+
+    {{#kfoldvars}}
+      {{ varname }} & {{ meancoef }}{{stars}} & {{ mediancoef }}{{stars}} \\
+                    & {{ meanstd }}           & {{ medianstd }}           \\
+    {{/kfoldvars}}
     \hline
@@
     Error out-sample &     &   \\
-    Error in-sample  &     &   \\
                      &     &   \\

### 2019-07-23 src/CrossValidation/core.jl

@@ -43,8 +43,8 @@ function kfoldcrossvalidation(
     k::Int,
     s::Float64)
 
-    db = randperm(data.nobs)
-    #db = collect(1:data.nobs)
+    #db = randperm(data.nobs)
+    db = collect(1:data.nobs)
     folds = split_database(db, k)
 
     # if data.time != nothing
@@ -69,8 +69,8 @@ function kfoldcrossvalidation(
         reduced.depvar_data = data.depvar_data[dataset]
         reduced.expvars_data = data.expvars_data[dataset, :]
         reduced.nobs = size(dataset, 1)
-        _, vars = GlobalSearchRegression.PreliminarySelection.lasso!(reduced)
-        
+        _, vars = GlobalSearchRegression.PreliminarySelection.lasso!(reduced, addextrasflag=false)
+
         backup = GlobalSearchRegression.copy_data(data)
         backup.expvars = data.expvars[vars]
         backup.expvars_data = data.expvars_data[:,vars]

### 2019-07-23 src/Output/Output.jl

@@ -1,5 +1,16 @@
 module Output
-    using DelimitedFiles, Printf, Statistics, Mustache, KernelDensity, Distributions, StatsPlots, ZipFile, InfoZIP
+    using DelimitedFiles,
+            Printf,
+            Mustache, 
+            KernelDensity,
+            StatsPlots,
+            ZipFile,
+            InfoZIP,
+            Statistics, 
+            StatsPlots,
+            DataFrames,
+            Distributions,
+            Distributed
     using Plots
     using ..GlobalSearchRegression
 

### 2019-07-23 src/Output/decorations/latex/latex.jl

@@ -18,13 +18,38 @@ function latex(data::GlobalSearchRegression.GSRegData; path::Union{Nothing, Stri
     end
 end
 
+function get_col_statistics(data)
+    nnan = filter(x -> !isnan(x), data)
+    poscol = filter(x -> x > 0, nnan)
+    if( isempty(nnan) )
+        return Dict(
+            "avg"      => "",
+            "median"   => "",
+            "mode"     => "",
+            "std"      => "",
+            "skew"     => "",
+            "kurt"     => "",
+            "posshare" => ""
+        )
+    end
+    Dict(
+        "avg"      => @sprintf("%.3f", mean(nnan)),
+        "median"   => @sprintf("%.3f", median(nnan)),
+        "mode"     => @sprintf("%.3f", mode(nnan)),
+        "std"      => @sprintf("%.3f", std(nnan)),
+        "skew"     => @sprintf("%.3f", skewness(nnan)),
+        "kurt"     => @sprintf("%.3f", kurtosis(nnan)),
+        "posshare" => @sprintf("%.3f", size(poscol, 1) / size(nnan, 1))
+    )
+end
+
 function latex!(dict::Dict, data::GlobalSearchRegression.GSRegData)
     # Preprocessing    
     preprocessing_dict = process_dict(data.extras[Preprocessing.PREPROCESSING_EXTRAKEY])
     preprocessing_dict["equation"] = join(map(x -> "$x", filter(x -> x != :_cons, preprocessing_dict["datanames"])), " ")
     preprocessing_dict["datanames"] = string("[:", join(preprocessing_dict["datanames"], ", :"), "]")
     preprocessing_dict["descriptive"] = []
-
+        
     datanames_index = GlobalSearchRegression.create_datanames_index(data.expvars) 
     
     for (i, var) in enumerate(data.expvars)
@@ -33,7 +58,7 @@ function latex!(dict::Dict, data::GlobalSearchRegression.GSRegData)
         c_obs = length(obs)
         c_miss = length(orig) - c_obs
         push!(preprocessing_dict["descriptive"], Dict(
-            "name" => string(var),
+            "name" => replace(string(var), "_" => "\\_"),
             "nobs" => length(obs),
             "mean" => @sprintf("%.2f", mean(obs)),
             "std"  => @sprintf("%.2f", std(obs)),
[…]

### 2019-07-23 src/PreliminarySelection/core.jl

@@ -16,8 +16,12 @@ function lasso(data::GlobalSearchRegression.GSRegData)
     lasso!(GlobalSearchRegression.copy_data(data))
 end
 
-function lasso!(data::GlobalSearchRegression.GSRegData)
-    betas = lassoselection(data)
+function lasso!(data::GlobalSearchRegression.GSRegData; addextrasflag=true)
+    betas, lambda = lassoselection(data)
+
+    if betas == nothing
+        return data, map(b -> true, data.expvars)
+    end
 
     data.extras[:lasso_betas] = betas
 
@@ -31,13 +35,15 @@ function lasso!(data::GlobalSearchRegression.GSRegData)
     data.expvars = data.expvars[vars]
     data.expvars_data = data.expvars_data[:,vars]
     
-    data = addextras(data, lassonumvars)
-
+    if( addextrasflag )
+        data = addextras(data, lassonumvars, betas, lambda)
+    end
+    
     return data, vars
 end
 
 function computablevars(nvars::Int)
-    return 8
+    return 3
     min(Int(floor(log(2,Sys.total_memory()/2 ^30) + 21)), nvars)
 end
 
@@ -47,7 +53,7 @@ function lassoselection(data)
     nvars = computablevars(size(data.expvars,1))
 
     if nvars >= size(data.expvars,1)
-        return data.expvars
+        return data.expvars, nothing
     end
 
     path = glmnet(data.expvars_data, data.depvar_data; nlambda=1000)
@@ -58,10 +64,10 @@ function lassoselection(data)
             if cant == nvars 
                 best = i
             end
-            break;
+            break
         end
         best = i
     end
 
-    path.betas[:, best]
+    return path.betas[:, best], path.lambda[best]
 end

### 2019-07-23 src/PreliminarySelection/utils.jl

@@ -1,10 +1,13 @@
 """
 Add values to extras
 """
-function addextras(data, lassonumvars)
+function addextras(data, lassonumvars, betas, lambda)
     data.extras[GlobalSearchRegression.generate_extra_key(PRELIMINARYSELECTION_EXTRAKEY, data.extras)] = Dict(
-        :enabled => true,
-        :lassonumvars => lassonumvars
+        :preliminaryselection => :lasso,
+        :lassonumvars => lassonumvars,
+        :lassobetas => betas,
+        :lassolambda => lambda,
+        :nobs => data.nobs
     )
     return data
 end

### 2019-07-23 src/core.jl

@@ -109,7 +109,7 @@ function gsr(
     )
 
     if featureextraction_enabled(fe_sqr, fe_log, fe_inv, fe_lag, interaction)
-        data = FeatureExtraction.featureextraction!(data, fe_lag=fe_lag, fe_log=fe_log, fe_inv=fe_inv, interaction=interaction, removemissings=true)
+        data = FeatureExtraction.featureextraction!(data, fe_sqr=fe_sqr, fe_lag=fe_lag, fe_log=fe_log, fe_inv=fe_inv, interaction=interaction, removemissings=true)
     end
 
     original_data = copy_data(data)
@@ -141,10 +141,10 @@ function gsr(
     end
 
     if exportcsv != nothing
-        GlobalSearchRegression.Output.csv(data, exportcsv)
+        GlobalSearchRegression.Output.csv(data, filename=exportscsv)
     end
 
-    println(GlobalSearchRegression.Output.summary(data, filename=exportsummary))
+    #println(GlobalSearchRegression.Output.summary(data, filename=exportsummary))
 
     return data
 end

### 2019-07-23 test/dummy_test.jl

@@ -9,7 +9,10 @@ data = CSV.read("data/small.csv")
     removeoutliers=true,
     outsample=10,
     modelavg=true,
-    preliminaryselection=:lasso
-
+    fe_sqr=:x1,
+    fe_inv=[:x2, :x3],
+    criteria=[:aic],
+    preliminaryselection=:lasso,
+    orderresults=true
 )
 GlobalSearchRegression.Output.latex(data, path="./Latex")

### 2019-07-23 src/Output/decorations/latex/tpl.tex
Export zip from temporal folder

@@
 {{ median }}
-
 --
-
 {{ average }}
-
     {{#kfoldvars}}

### 2019-07-23 test/Latex/main.tex
Export zip from temporal folder

--- 2019-07-23 test/Latex/main.tex
@@
   GlobalSearchRegression.gsr(
-        equation = "y x1 x2 x3 x4 x5",
+    equation = "y x1 x2 x3 x4 x5 x6 x7 x8 x9 x10 x11 x12 x13 x14 x15 x16 x17 x18 x19 x20 x21 x22 x23 x24 x25 x26 x27 x28 x29 x30 x31 x32 x33 x34 x35 x36 x37 x38 x39 x40 x41 x42 x43 x44 x45 x46 x47 x48 x49 x50 x51 x52 x53 x54 x55 x56 x57 x58 x59 x60 x61 x62 x63 x64 x65 x66 x67 x68 x69 x70 x71 x72 x73 x74 x75 x76 x77 x78 x79 x80 x81 x82 x83 x84 x85 x86 x87 x88 x89 x90 x91 x92 x93 x94 x95 x96 x97 x98 x99 x100 x101 x102 x103 x104 x105 x106 x107 x108 x109 x110 x111 x112 x113 x114 x115 x116 x117 x118 x119 x120 x121 x122 x123 x124 x125 x126 x127 x128 x129 x130 x131 x132 x133 x134 x135 x136 x137 x138 x139 x140 x141 x142 x143 x144 x145 x146 x147 x148 x149 x150 x151 x152 x153 x154 x155 x156 x157 x158 x159 x160 x161 x162 x163 x164 x165 x166 x167 x168 x169 x170 x171 x172 x173 x174 x175 x176 x177 x178 x179 x180 x181 x182 x183 x184 x185 x186 x187 x188 x189 x190 x191 x192 x193 x194 x195 x196 x197 x198 x199 x200 x201 x202 x203 x204 x205 x206 x207 x208 x209 x210 x211 x212 x213 x214 x215 x216 x217 x218 x219 x220 x221 x222 x223 x224 x225 x226 x227 x228 x229 x230 x231 x232 x233 x234 x235 x236 x237 x238 x239 x240 x241 x242 x243 x244 x245 x246 x247 x248 x249 x250 x251 x252 x253 x254 x255 x256 x257 x258 x259 x260 x261 x262 x263 x264 x265 x266 x267 x268 x269 x270 x271 x272 x273 x274 x275 x276 x277 x278 x279 x280 x281 x282 x283 x284 x285 x286 x287 x288 x289 x290 x291 x292 x293 x294 x295 x296 x297 x298 x299 x300 x301 x302 x303 x304 x305 x306 x307 x308 x309 x310 x311 x312 x313 x314 x315 x316 x317 x318 x319 x320 x321 x322 x323 x324 x325 x326 x327 x328 x329 x330 x331 x332 x333 x334 x335 x336 x337 x338 x339 x340 x341 x342 x343 x344 x345 x346 x347 x348 x349 x350 x351 x352 x353 x354 x355 x356 x357 x358 x359 x360 x361 x362 x363 x364 x365 x366 x367 x368 x369 x370 x371 x372 x373 x374 x375 x376 x377 x378 x379 x380 x381 x382 x383 x384 x385 x386 x387 x388 x389 x390 x391 x392 x393 x394 x395 x396 x397 x398 x399 x400 x401 x402 x403 x404 x405 x406 x407 x408 x409 x410 x411 x412 x413 x414 x415 x416 x417 x418 x419 x420 x421 x422 x423 x424 x425 x426 x427 x428 x429 x430 x431 x432 x433 x434 x435 x436 x437 x438 x439 x440 x441 x442 x443 x444 x445 x446 x447 x448 x449 x450 x451 x452 x453 x454 x455 x456 x457 x458 x459 x460 x461 x462 x463 x464 x465 x466 x467 x468 x469 x470 x471 x472 x473 x474 x475 x476 x477 x478 x479 x480 x481 x482 x483 x484 x485 x486 x487 x488 x489 x490 x491 x492 x493 x494 x495 x496 x497 x498 x499 x500 x501 x502 x503 x504 x505 x506 x507 x508 x509 x510 x511 x512 x513 x514 x515 x516 x517 x518 x519 x520 x521 x522 x523 x524 x525 x526 x527 x528 x529 x530 x531 x532 x533 x534 x535 x536 x537 x538 x539 x540 x541 x542 x543 x544 x545 x546 x547 x548 x549 x550 x551 x552 x553 x554 x555 x556 x557 x558 x559 x560 x561 x562 x563 x564 x565 x566 x567 x568 x569 x570 x571 x572 x573 x574 x575 x576 x577 x578 x579 x580 x581 x582 x583 x584 x585 x586 x587 x588 x589 x590 x591 x592 x593 x594 x595 x596 x597 x598 x599 x600 x601 x602 x603 x604 x605 x606 x607 x608 x609 x610 x611 x612 x613 x614 x615 x616 x617 x618 x619 x620 x621 x622 x623 x624 x625 x626 x627 x628 x629 x630 x631 x632 x633 x634 x635 x636 x637 x638 x639 x640 x641 x642 x643 x644 x645 x646 x647 x648 x649 x650 x651 x652 x653 x654 x655 x656 x657 x658 x659 x660 x661 x662 x663 x664 x665 x666 x667 x668 x669 x670 x671 x672 x673 x674 x675 x676 x677 x678 x679 x680 x681 x682 x683 x684 x685 x686 x687 x688 x689 x690 x691 x692 x693 x694 x695 x696 x697 x698 x699 x700 x701 x702 x703 x704 x705 x706 x707 x708 x709 x710 x711 x712 x713 x714 x715 x716 x717 x718 x719 x720 x721 x722 x723 x724 x725 x726 x727 x728 x729 x730 x731 x732 x733 x734 x735 x736 x737 x738 x739 x740 x741 x742 x743 x744 x745 x746 x747 x748 x749 x750 x751 x752 x753 x754 x755 x756 x757 x758 x759 x760 x761 x762 x763 x764 x765 x766 x767 x768 x769 x770 x771 x772 x773 x774 x775 x776 x777 x778 x779 x780 x781 x782 x783 x784 x785 x786 x787 x788 x789 x790 x791 x792 x793 x794 x795 x796 x797 x798 x799 x800 x801 x802 x803 x804 x805 x806 x807 x808 x809 x810 x811 x812 x813 x814 x815 x816 x817 x818 x819 x820 x821 x822 x823 x824 x825 x826 x827 x828 x829 x830 x831 x832 x833 x834 x835 x836 x837 x838 x839 x840 x841 x842 x843 x844 x845 x846 x847 x848 x849 x850 x851 x852 x853 x854 x855 x856 x857 x858 x859 x860 x861 x862 x863 x864 x865 x866 x867 x868 x869 x870 x871 x872 x873 x874 x875 x876 x877 x878 x879 x880 x881 x882 x883 x884 x885 x886 x887 x888 x889 x890 x891 x892 x893 x894 x895 x896 x897 x898 x899 x900 x901 x902 x903 x904 x905 x906 x907 x908 x909 x910 x911 x912 x913 x914 x915 x916 x917 x918 x919 x920 x921 x922 x923 x924 x925 x926 x927 x928 x929 x930 x931 x932 x933 x934 x935 x936 x937 x938 x939 x940 x941 x942 x943 x944 x945 x946 x947 x948 x949 x950 x951 x952 x953 x954 x955 x956 x957 x958 x959 x960 x961 x962 x963 x964 x965 x966 x967 x968 x969 x970 x971 x972 x973 x974 x975 x976 x977 x978 x979 x980 x981 x982 x983 x984 x985 x986 x987 x988 x989 x990 x991 x992 x993 x994 x995 x996 x997 x998 x999 x1000",
     data = dataname,
-        datanames = [:y, :x1, :x2, :x3, :x4, :x5, :_cons],
-        method = :fast,
+    datanames = [:y, :x1, :x2, :x3, :x4, :x5, :x6, :x7, :x8, :x9, :x10, :x11, :x12, :x13, :x14, :x15, :x16, :x17, :x18, :x19, :x20, :x21, :x22, :x23, :x24, :x25, :x26, :x27, :x28, :x29, :x30, :x31, :x32, :x33, :x34, :x35, :x36, :x37, :x38, :x39, :x40, :x41, :x42, :x43, :x44, :x45, :x46, :x47, :x48, :x49, :x50, :x51, :x52, :x53, :x54, :x55, :x56, :x57, :x58, :x59, :x60, :x61, :x62, :x63, :x64, :x65, :x66, :x67, :x68, :x69, :x70, :x71, :x72, :x73, :x74, :x75, :x76, :x77, :x78, :x79, :x80, :x81, :x82, :x83, :x84, :x85, :x86, :x87, :x88, :x89, :x90, :x91, :x92, :x93, :x94, :x95, :x96, :x97, :x98, :x99, :x100, :x101, :x102, :x103, :x104, :x105, :x106, :x107, :x108, :x109, :x110, :x111, :x112, :x113, :x114, :x115, :x116, :x117, :x118, :x119, :x120, :x121, :x122, :x123, :x124, :x125, :x126, :x127, :x128, :x129, :x130, :x131, :x132, :x133, :x134, :x135, :x136, :x137, :x138, :x139, :x140, :x141, :x142, :x143, :x144, :x145, :x146, :x147, :x148, :x149, :x150, :x151, :x152, :x153, :x154, :x155, :x156, :x157, :x158, :x159, :x160, :x161, :x162, :x163, :x164, :x165, :x166, :x167, :x168, :x169, :x170, :x171, :x172, :x173, :x174, :x175, :x176, :x177, :x178, :x179, :x180, :x181, :x182, :x183, :x184, :x185, :x186, :x187, :x188, :x189, :x190, :x191, :x192, :x193, :x194, :x195, :x196, :x197, :x198, :x199, :x200, :x201, :x202, :x203, :x204, :x205, :x206, :x207, :x208, :x209, :x210, :x211, :x212, :x213, :x214, :x215, :x216, :x217, :x218, :x219, :x220, :x221, :x222, :x223, :x224, :x225, :x226, :x227, :x228, :x229, :x230, :x231, :x232, :x233, :x234, :x235, :x236, :x237, :x238, :x239, :x240, :x241, :x242, :x243, :x244, :x245, :x246, :x247, :x248, :x249, :x250, :x251, :x252, :x253, :x254, :x255, :x256, :x257, :x258, :x259, :x260, :x261, :x262, :x263, :x264, :x265, :x266, :x267, :x268, :x269, :x270, :x271, :x272, :x273, :x274, :x275, :x276, :x277, :x278, :x279, :x280, :x281, :x282, :x283, :x284, :x285, :x286, :x287, :x288, :x289, :x290, :x291, :x292, :x293, :x294, :x295, :x296, :x297, :x298, :x299, :x300, :x301, :x302, :x303, :x304, :x305, :x306, :x307, :x308, :x309, :x310, :x311, :x312, :x313, :x314, :x315, :x316, :x317, :x318, :x319, :x320, :x321, :x322, :x323, :x324, :x325, :x326, :x327, :x328, :x329, :x330, :x331, :x332, :x333, :x334, :x335, :x336, :x337, :x338, :x339, :x340, :x341, :x342, :x343, :x344, :x345, :x346, :x347, :x348, :x349, :x350, :x351, :x352, :x353, :x354, :x355, :x356, :x357, :x358, :x359, :x360, :x361, :x362, :x363, :x364, :x365, :x366, :x367, :x368, :x369, :x370, :x371, :x372, :x373, :x374, :x375, :x376, :x377, :x378, :x379, :x380, :x381, :x382, :x383, :x384, :x385, :x386, :x387, :x388, :x389, :x390, :x391, :x392, :x393, :x394, :x395, :x396, :x397, :x398, :x399, :x400, :x401, :x402, :x403, :x404, :x405, :x406, :x407, :x408, :x409, :x410, :x411, :x412, :x413, :x414, :x415, :x416, :x417, :x418, :x419, :x420, :x421, :x422, :x423, :x424, :x425, :x426, :x427, :x428, :x429, :x430, :x431, :x432, :x433, :x434, :x435, :x436, :x437, :x438, :x439, :x440, :x441, :x442, :x443, :x444, :x445, :x446, :x447, :x448, :x449, :x450, :x451, :x452, :x453, :x454, :x455, :x456, :x457, :x458, :x459, :x460, :x461, :x462, :x463, :x464, :x465, :x466, :x467, :x468, :x469, :x470, :x471, :x472, :x473, :x474, :x475, :x476, :x477, :x478, :x479, :x480, :x481, :x482, :x483, :x484, :x485, :x486, :x487, :x488, :x489, :x490, :x491, :x492, :x493, :x494, :x495, :x496, :x497, :x498, :x499, :x500, :x501, :x502, :x503, :x504, :x505, :x506, :x507, :x508, :x509, :x510, :x511, :x512, :x513, :x514, :x515, :x516, :x517, :x518, :x519, :x520, :x521, :x522, :x523, :x524, :x525, :x526, :x527, :x528, :x529, :x530, :x531, :x532, :x533, :x534, :x535, :x536, :x537, :x538, :x539, :x540, :x541, :x542, :x543, :x544, :x545, :x546, :x547, :x548, :x549, :x550, :x551, :x552, :x553, :x554, :x555, :x556, :x557, :x558, :x559, :x560, :x561, :x562, :x563, :x564, :x565, :x566, :x567, :x568, :x569, :x570, :x571, :x572, :x573, :x574, :x575, :x576, :x577, :x578, :x579, :x580, :x581, :x582, :x583, :x584, :x585, :x586, :x587, :x588, :x589, :x590, :x591, :x592, :x593, :x594, :x595, :x596, :x597, :x598, :x599, :x600, :x601, :x602, :x603, :x604, :x605, :x606, :x607, :x608, :x609, :x610, :x611, :x612, :x613, :x614, :x615, :x616, :x617, :x618, :x619, :x620, :x621, :x622, :x623, :x624, :x625, :x626, :x627, :x628, :x629, :x630, :x631, :x632, :x633, :x634, :x635, :x636, :x637, :x638, :x639, :x640, :x641, :x642, :x643, :x644, :x645, :x646, :x647, :x648, :x649, :x650, :x651, :x652, :x653, :x654, :x655, :x656, :x657, :x658, :x659, :x660, :x661, :x662, :x663, :x664, :x665, :x666, :x667, :x668, :x669, :x670, :x671, :x672, :x673, :x674, :x675, :x676, :x677, :x678, :x679, :x680, :x681, :x682, :x683, :x684, :x685, :x686, :x687, :x688, :x689, :x690, :x691, :x692, :x693, :x694, :x695, :x696, :x697, :x698, :x699, :x700, :x701, :x702, :x703, :x704, :x705, :x706, :x707, :x708, :x709, :x710, :x711, :x712, :x713, :x714, :x715, :x716, :x717, :x718, :x719, :x720, :x721, :x722, :x723, :x724, :x725, :x726, :x727, :x728, :x729, :x730, :x731, :x732, :x733, :x734, :x735, :x736, :x737, :x738, :x739, :x740, :x741, :x742, :x743, :x744, :x745, :x746, :x747, :x748, :x749, :x750, :x751, :x752, :x753, :x754, :x755, :x756, :x757, :x758, :x759, :x760, :x761, :x762, :x763, :x764, :x765, :x766, :x767, :x768, :x769, :x770, :x771, :x772, :x773, :x774, :x775, :x776, :x777, :x778, :x779, :x780, :x781, :x782, :x783, :x784, :x785, :x786, :x787, :x788, :x789, :x790, :x791, :x792, :x793, :x794, :x795, :x796, :x797, :x798, :x799, :x800, :x801, :x802, :x803, :x804, :x805, :x806, :x807, :x808, :x809, :x810, :x811, :x812, :x813, :x814, :x815, :x816, :x817, :x818, :x819, :x820, :x821, :x822, :x823, :x824, :x825, :x826, :x827, :x828, :x829, :x830, :x831, :x832, :x833, :x834, :x835, :x836, :x837, :x838, :x839, :x840, :x841, :x842, :x843, :x844, :x845, :x846, :x847, :x848, :x849, :x850, :x851, :x852, :x853, :x854, :x855, :x856, :x857, :x858, :x859, :x860, :x861, :x862, :x863, :x864, :x865, :x866, :x867, :x868, :x869, :x870, :x871, :x872, :x873, :x874, :x875, :x876, :x877, :x878, :x879, :x880, :x881, :x882, :x883, :x884, :x885, :x886, :x887, :x888, :x889, :x890, :x891, :x892, :x893, :x894, :x895, :x896, :x897, :x898, :x899, :x900, :x901, :x902, :x903, :x904, :x905, :x906, :x907, :x908, :x909, :x910, :x911, :x912, :x913, :x914, :x915, :x916, :x917, :x918, :x919, :x920, :x921, :x922, :x923, :x924, :x925, :x926, :x927, :x928, :x929, :x930, :x931, :x932, :x933, :x934, :x935, :x936, :x937, :x938, :x939, :x940, :x941, :x942, :x943, :x944, :x945, :x946, :x947, :x948, :x949, :x950, :x951, :x952, :x953, :x954, :x955, :x956, :x957, :x958, :x959, :x960, :x961, :x962, :x963, :x964, :x965, :x966, :x967, :x968, :x969, :x970, :x971, :x972, :x973, :x974, :x975, :x976, :x977, :x978, :x979, :x980, :x981, :x982, :x983, :x984, :x985, :x986, :x987, :x988, :x989, :x990, :x991, :x992, :x993, :x994, :x995, :x996, :x997, :x998, :x999, :x1000, :_cons],
+    method = :precise,
     intercept = true,
-
-        removeoutliers = true,
-
-        fe_sqr
-        fe_log
-        fe_inv
-        fe_lag
-        interaction
-        preliminaryselection
-        fixedvariables
-        outsample
-        criteria
-        ttest
-        modelavg
-        residualtest
-        orderresults
-        kfoldcrossvalidation
-        numfolds
-        testsetshare
-        exportcsv
-        exportsummary
+    removeoutliers = ,
+    preliminaryselection = :lasso,
+    outsample = 10,
+    criteria = [:aic, :aicc, :cp, :r2adj, :rmseout],
+    ttest = true,
+    modelavg = true,
+    residualtest = true,
+    orderresults = true,
+    kfoldcrossvalidation = Dict{Any,Any}(&quot;median&quot;=&gt;[3.0 0.0 0.0 0.0 0.0 0.0 0.0 0.0 0.0 0.0 -0.110223 0.117787 -1.06407 66.0 3.0 56.7211 0.225622 9.63996 0.927044 1.06744 0.201039 0.7426 2.4323e-6 0.655581 0.0 0.0 0.0 0.0 0.0 0.0 0.0 0.0 0.0 0.0 0.0 0.0 0.0 0.0 0.0 0.0 0.0 0.0],&quot;kfolds&quot;=&gt;3,&quot;average&quot;=&gt;[3.33333 0.121148 0.033808 1.19447 -0.135271 0.0442381 -1.01926 0.0 0.0 0.0 -0.102466 0.114535 -0.896072 66.6667 2.66667 55.1408 0.206017 10.058 0.90649 1.1032 0.185638 0.671841 1.62484e-5 0.581203 0.106131 0.0382284 0.925414 0.0920784 0.0328706 0.933747 0.0 0.0 0.0 0.0 0.0 0.0 0.0 0.0 0.0 -0.115661 0.037252 -1.03494],&quot;datanames&quot;=&gt;Symbol[:index, :x6_b, :x6_bstd, :x6_t, :x8_b, :x8_bstd, :x8_t, :x932_b, :x932_bstd, :x932_t, :_cons_b, :_cons_bstd, :_cons_t, :nobs, :ncoef, :sse, :r2, :F, :rmse, :rmseout, :r2adj, :jbtest, :wtest, :order, :x348_b, :x348_bstd, :x348_t, :x806_b, :x806_bstd, :x806_t, :x964_b, :x964_bstd, :x964_t, :x61_b, :x61_bstd, :x61_t, :x428_b, :x428_bstd, :x428_t, :x599_b, :x599_bstd, :x599_t],&quot;tsetsize&quot;=&gt;0.0,&quot;ttest&quot;=&gt;true),
+  )
 \end{lstlisting}
@@
 In section 3, descriptive statistics are introduced.
-In turn, section 4 is dedicated to LASSO results.
-In turn, section 4 is dedicated to All-subset-regression results.
-After that, section 5 shows All-subset-regression results.
+After that, LASSO results are examined.
+Then, All-subset-regression analysis is shown.
 Finally, the last section examines K-fold cross-validation outcomes.
@@
 
-  \item Remove-outliers: extreme observations (because of input errors or extraordinary/non-relevant events) have been removed using the standard 3-sigma rule (see \cite{lehmann2013}).
 \end{enumerate}
@@
 
-In this report, the $\lambda$ parameter has been dynamically defined in order to retain up to 6 covariates.
+In this report, the $\lambda$ parameter has been dynamically defined in order to retain up to 3 covariates.
 
@@
 Users are free to combine in-sample and out-of-sample information criteria.
-In this report, selected information criteria include (the key variable/s for feature selection.
+In this report, selected information criteria include ([:aic, :aicc, :cp, :r2adj, :rmseout]) as the key variable/s for feature selection.
 
@@
   \item The residualtest=true option enables white heteroskedasticity, Jarque-Bera normality test and the Breusch-Godfrey test for autocorrelation to be implemented for each model.
+  \item User's specification of orderresults=true entails that the output matrix has been sorted by the the above mentioned normalized, harmonized and potentially combined selection criteria.
 \end{enumerate}
-
---------------------------------------------------
-
 \subsection{K-fold Cross Validation}
@@
 Among different alternatives, the K-fold approach has a parameter $K$ which identifies the number of groups that a given database must be split into (see \cite{arlot2010}).
-In this report user selected k-fold number is 5.
+In this report user selected k-fold number is 3.
 
@@
 
-\section{Variables}
-
 \begin{table}[!h]
@@
     \hline
-    x1 & Insert Description & 96 & -0.03 & 1.08 & 2.29 & -2.76 & 0.00\% \\ 
-    x2 & Insert Description & 96 & -0.11 & 0.90 & 1.61 & -2.31 & 0.00\% \\ 
-    x3 & Insert Description & 96 & -0.10 & 0.95 & 2.15 & -2.38 & 0.00\% \\ 
-    x4 & Insert Description & 96 & 0.13 & 1.00 & 2.63 & -2.73 & 0.00\% \\ 
-    x5 & Insert Description & 96 & -0.09 & 0.84 & 1.80 & -2.48 & 0.00\% \\ 
-    _cons & Insert Description & 96 & 1.00 & 0.00 & 1.00 & 1.00 & 0.00\% \\ 
+    x263 & Insert Description & 100 & -0.07 & 1.12 & 2.81 & -2.97 & 0.00\% \\ 
+    x779 & Insert Description & 100 & 0.10 & 1.00 & 2.72 & -2.40 & 0.00\% \\ 
+    x813 & Insert Description & 100 & -0.02 & 0.88 & 3.64 & -1.77 & 0.00\% \\ 
+    \_cons & Insert Description & 100 & 1.00 & 0.00 & 1.00 & 1.00 & 0.00\% \\ 
     \hline
@@
     \hline
-       &  \\
-       &  \\
-       &  \\
-       &  \\
-       &  \\
-       &  \\
+      x263 & -0.015 \\
+      x779 & -0.005 \\
+      x813 & -0.001 \\
     \hline
     \hline
-    Observations &  96 \\
-    \lambda      &   \\
+    Observations &  100 \\
+    \lambda      &  0.282 \\
     \hline
@@
 
+\clearpage
 \section{Global Search Regression}
@@
     \hline 
-    x1     & -0.121***  & -0.126***     \\
-                 &              & 0.103  \\
+    x263     & -0.253***  & -0.264***     \\
+                 & 0.088        & 0.089  \\
 
-    x2     &   & -0.012***     \\
-                 &              & 0.118  \\
+    x779     & -0.230**  & -0.253**     \\
+                 & 0.100        & 0.103  \\
 
-    x3     & 0.108*  & 0.109*     \\
-                 &              & 0.114  \\
+    x813     & -0.280**  & -0.299**     \\
+                 & 0.115        & 0.118  \\
 
-    x4     & 0.169*  & 0.152*     \\
-                 &              & 0.111  \\
-
-    x5     &   & -0.083***     \\
-                 &              & 0.136  \\
-
-    _cons     & 0.142*  & 0.146*     \\
-                 &              & 0.109  \\
+    \_cons     & -0.127  & -0.128     \\
+                 & 0.101        & 0.104  \\
     \hline
 
-    Observations &   \multicolumn{ 1  }{c}{ } \\
-    Criteria     &   \multicolumn{ 1  }{c}{ } \\
+    Observations &   \multicolumn{ 1  }{c}{ 100 } \\
+    Criteria     &   \multicolumn{ 1  }{c}{ [:aic, :aicc, :cp, :r2adj, :rmseout] } \\
     \hline
@@
 \begin{center}
-    \large{\textbf{Coefficient, t-test and selection criteria gains distributions for  }}
+    \large{\textbf{Coefficient, t-test and selection criteria gains distributions for x263 }}
 \end{center}
@@
     \centering
-    \includegraphics[width=\textwidth]{contour__b_t.png}
+    \includegraphics[width=\textwidth]{contour_x263_b_t.png}
     \caption{Bivariate Kernel density (Contour view)}
@@
     \centering
-    \includegraphics[width=\textwidth]{wireframe__b_t.png}
+    \includegraphics[width=\textwidth]{wireframe_x263_b_t.png}
     \caption{Bivariate Kernel density (Contour view)}
@@
     \centering
-    \includegraphics[width=\textwidth]{Kdensity_criteria_.png}
-    \caption{Selection criteria gains for including  (Kernel view)}
+    \includegraphics[width=\textwidth]{Kdensity_criteria_x263.png}
+    \caption{Selection criteria gains for including x263 (Kernel view)}
   \end{minipage}
@@
     \centering    
-    \includegraphics[width=\textwidth]{BoxViolinDot_.png}
-    \caption{Selection criteria gains for including  (Box-Violin view)}    
+    \includegraphics[width=\textwidth]{BoxViolinDot_x263.png}
+    \caption{Selection criteria gains for including x263 (Box-Violin view)}    
   \end{minipage}
@@
     \hline
-    Variable  Statistics &  Coefficient Distribution &  T-test Distribution  \\
+    Variable x263 Statistics &  Coefficient Distribution &  T-test Distribution  \\
     \hline
     \hline
-    Simple average    &       &  \\
+    Simple average    & -0.267      & -2.969 \\
     \hline
-    Median            &    &  \\
+    Median            & -0.266   & -2.965 \\
     \hline
-    Mode              &      &  \\
+    Mode              & -0.253     & -2.884 \\
     \hline
-    Skewness          &       &  \\
+    Skewness          & 0.013      & 0.090 \\
     \hline
-    kurtosis          &      &  \\
+    kurtosis          & -0.214     & -0.060 \\
     \hline
-    Positive Share    &      &  \\
+    Positive Share    & -1.312     & -1.878 \\
     \hline
-    Significant Share &  &  \\
+    Significant Share & 0.000 &  \\
     \hline
@@
 \begin{center}
-    \large{\textbf{Coefficient, t-test and selection criteria gains distributions for  }}
+    \large{\textbf{Coefficient, t-test and selection criteria gains distributions for x779 }}
 \end{center}
@@
     \centering
-    \includegraphics[width=\textwidth]{contour__b_t.png}
+    \includegraphics[width=\textwidth]{contour_x779_b_t.png}
     \caption{Bivariate Kernel density (Contour view)}
@@
     \centering
-    \includegraphics[width=\textwidth]{wireframe__b_t.png}
+    \includegraphics[width=\textwidth]{wireframe_x779_b_t.png}
     \caption{Bivariate Kernel density (Contour view)}
@@
     \centering
-    \includegraphics[width=\textwidth]{Kdensity_criteria_.png}
-    \caption{Selection criteria gains for including  (Kernel view)}
+    \includegraphics[width=\textwidth]{Kdensity_criteria_x779.png}
+    \caption{Selection criteria gains for including x779 (Kernel view)}
   \end{minipage}
@@
     \centering    
-    \includegraphics[width=\textwidth]{BoxViolinDot_.png}
-    \caption{Selection criteria gains for including  (Box-Violin view)}    
+    \includegraphics[width=\textwidth]{BoxViolinDot_x779.png}
+    \caption{Selection criteria gains for including x779 (Box-Violin view)}    
   \end{minipage}
@@
     \hline
-    Variable  Statistics &  Coefficient Distribution &  T-test Distribution  \\
+    Variable x779 Statistics &  Coefficient Distribution &  T-test Distribution  \\
     \hline
     \hline
-    Simple average    &       &  \\
+    Simple average    & -0.259      & -2.505 \\
     \hline
-    Median            &    &  \\
+    Median            & -0.258   & -2.502 \\
     \hline
-    Mode              &      &  \\
+    Mode              & -0.230     & -2.287 \\
     \hline
-    Skewness          &       &  \\
+    Skewness          & 0.025      & 0.184 \\
     \hline
-    kurtosis          &      &  \\
+    kurtosis          & -0.084     & -0.042 \\
     \hline
-    Positive Share    &      &  \\
+    Positive Share    & -1.031     & -1.172 \\
     \hline
-    Significant Share &  &  \\
+    Significant Share & 0.000 &  \\
     \hline
@@
 \begin{center}
-    \large{\textbf{Coefficient, t-test and selection criteria gains distributions for  }}
+    \large{\textbf{Coefficient, t-test and selection criteria gains distributions for x813 }}
 \end{center}
@@
     \centering
-    \includegraphics[width=\textwidth]{contour__b_t.png}
+    \includegraphics[width=\textwidth]{contour_x813_b_t.png}
     \caption{Bivariate Kernel density (Contour view)}
@@
     \centering
-    \includegraphics[width=\textwidth]{wireframe__b_t.png}
+    \includegraphics[width=\textwidth]{wireframe_x813_b_t.png}
     \caption{Bivariate Kernel density (Contour view)}
@@
     \centering
-    \includegraphics[width=\textwidth]{Kdensity_criteria_.png}
-    \caption{Selection criteria gains for including  (Kernel view)}
+    \includegraphics[width=\textwidth]{Kdensity_criteria_x813.png}
+    \caption{Selection criteria gains for including x813 (Kernel view)}
   \end{minipage}
@@
     \centering    
-    \includegraphics[width=\textwidth]{BoxViolinDot_.png}
-    \caption{Selection criteria gains for including  (Box-Violin view)}    
+    \includegraphics[width=\textwidth]{BoxViolinDot_x813.png}
+    \caption{Selection criteria gains for including x813 (Box-Violin view)}    
   \end{minipage}
@@
     \hline
-    Variable  Statistics &  Coefficient Distribution &  T-test Distribution  \\
+    Variable x813 Statistics &  Coefficient Distribution &  T-test Distribution  \\
     \hline
     \hline
-    Simple average    &       &  \\
+    Simple average    & -0.305      & -2.572 \\
     \hline
-    Median            &    &  \\
+    Median            & -0.304   & -2.567 \\
     \hline
-    Mode              &      &  \\
+    Mode              & -0.280     & -2.434 \\
     \hline
-    Skewness          &       &  \\
+    Skewness          & 0.023      & 0.153 \\
     \hline
-    kurtosis          &      &  \\
+    kurtosis          & -0.140     & -0.023 \\
     \hline
-    Positive Share    &      &  \\
+    Positive Share    & -1.464     & -1.959 \\
     \hline
-    Significant Share &  &  \\
+    Significant Share & 0.000 &  \\
     \hline
@@
 \begin{center}
-    \large{\textbf{Coefficient, t-test and selection criteria gains distributions for  }}
+    \large{\textbf{Coefficient, t-test and selection criteria gains distributions for _cons }}
 \end{center}
@@
     \centering
-    \includegraphics[width=\textwidth]{contour__b_t.png}
+    \includegraphics[width=\textwidth]{contour__cons_b_t.png}
     \caption{Bivariate Kernel density (Contour view)}
@@
     \centering
-    \includegraphics[width=\textwidth]{wireframe__b_t.png}
+    \includegraphics[width=\textwidth]{wireframe__cons_b_t.png}
     \caption{Bivariate Kernel density (Contour view)}
@@
     \centering
-    \includegraphics[width=\textwidth]{Kdensity_criteria_.png}
-    \caption{Selection criteria gains for including  (Kernel view)}
+    \includegraphics[width=\textwidth]{Kdensity_criteria__cons.png}
+    \caption{Selection criteria gains for including _cons (Kernel view)}
   \end{minipage}
@@
     \centering    
-    \includegraphics[width=\textwidth]{BoxViolinDot_.png}
-    \caption{Selection criteria gains for including  (Box-Violin view)}    
+    \includegraphics[width=\textwidth]{BoxViolinDot__cons.png}
+    \caption{Selection criteria gains for including _cons (Box-Violin view)}    
   \end{minipage}
@@
     \hline
-    Variable  Statistics &  Coefficient Distribution &  T-test Distribution  \\
+    Variable _cons Statistics &  Coefficient Distribution &  T-test Distribution  \\
     \hline
     \hline
-    Simple average    &       &  \\
+    Simple average    & -0.128      & -1.223 \\
     \hline
-    Median            &    &  \\
+    Median            & -0.127   & -1.244 \\
     \hline
-    Mode              &      &  \\
+    Mode              & -0.127     & -1.263 \\
     \hline
-    Skewness          &       &  \\
+    Skewness          & 0.018      & 0.180 \\
     \hline
-    kurtosis          &      &  \\
+    kurtosis          & 0.016     & 0.125 \\
     \hline
-    Positive Share    &      &  \\
+    Positive Share    & -1.293     & -1.131 \\
     \hline
-    Significant Share &  &  \\
-    \hline
-    \end{tabular}
-\end{table}
-
-\clearpage
-\begin{center}
-    \large{\textbf{Coefficient, t-test and selection criteria gains distributions for  }}
-\end{center}
-
-\vspace{-5mm}
-
-\begin{figure}[!ht]
-  \centering
-  \begin{minipage}[b]{0.46\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{contour__b_t.png}
-    \caption{Bivariate Kernel density (Contour view)}
-  \end{minipage}
-  \hfill
-  \begin{minipage}[b]{0.53\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{wireframe__b_t.png}
-    \caption{Bivariate Kernel density (Contour view)}
-  \end{minipage}
-
-  \begin{minipage}[b]{0.48\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{Kdensity_criteria_.png}
-    \caption{Selection criteria gains for including  (Kernel view)}
-  \end{minipage}
-  \hfill
-  \begin{minipage}[b]{0.48\textwidth}
-    \centering    
-    \includegraphics[width=\textwidth]{BoxViolinDot_.png}
-    \caption{Selection criteria gains for including  (Box-Violin view)}    
-  \end{minipage}
-\end{figure}
-
-\vspace{1cm}
-
-The following table shows main statistics of coefficient and t-test distribution
-
-\begin{table}[!h]
-    \centering
-    \caption{Statistics}
-    \begin{tabular}{|l|c|c|}
-    \hline
-    Variable  Statistics &  Coefficient Distribution &  T-test Distribution  \\
-    \hline
-    \hline
-    Simple average    &       &  \\
-    \hline
-    Median            &    &  \\
-    \hline
-    Mode              &      &  \\
-    \hline
-    Skewness          &       &  \\
-    \hline
-    kurtosis          &      &  \\
-    \hline
-    Positive Share    &      &  \\
-    \hline
-    Significant Share &  &  \\
-    \hline
-    \end{tabular}
-\end{table}
-
-\clearpage
-\begin{center}
-    \large{\textbf{Coefficient, t-test and selection criteria gains distributions for  }}
-\end{center}
-
-\vspace{-5mm}
-
-\begin{figure}[!ht]
-  \centering
-  \begin{minipage}[b]{0.46\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{contour__b_t.png}
-    \caption{Bivariate Kernel density (Contour view)}
-  \end{minipage}
-  \hfill
-  \begin{minipage}[b]{0.53\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{wireframe__b_t.png}
-    \caption{Bivariate Kernel density (Contour view)}
-  \end{minipage}
-
-  \begin{minipage}[b]{0.48\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{Kdensity_criteria_.png}
-    \caption{Selection criteria gains for including  (Kernel view)}
-  \end{minipage}
-  \hfill
-  \begin{minipage}[b]{0.48\textwidth}
-    \centering    
-    \includegraphics[width=\textwidth]{BoxViolinDot_.png}
-    \caption{Selection criteria gains for including  (Box-Violin view)}    
-  \end{minipage}
-\end{figure}
-
-\vspace{1cm}
-
-The following table shows main statistics of coefficient and t-test distribution
-
-\begin{table}[!h]
-    \centering
-    \caption{Statistics}
-    \begin{tabular}{|l|c|c|}
-    \hline
-    Variable  Statistics &  Coefficient Distribution &  T-test Distribution  \\
-    \hline
-    \hline
-    Simple average    &       &  \\
-    \hline
-    Median            &    &  \\
-    \hline
-    Mode              &      &  \\
-    \hline
-    Skewness          &       &  \\
-    \hline
-    kurtosis          &      &  \\
-    \hline
-    Positive Share    &      &  \\
-    \hline
-    Significant Share &  &  \\
+    Significant Share & 0.000 &  \\
     \hline
@@
     \multicolumn{3}{c}{K-fold scheme:\textbf{Insert scheme}}    \\
-                 & 5-fold  & 5-fold \\
+                    & 3-fold         & 3-fold \\
     Variables       & Mean                    & Median          \\
@@
     \hline
-                 &                  &                  \\
-                 &                  &                  \\
+[3.0 0.0 0.0 0.0 0.0 0.0 0.0 0.0 0.0 0.0 -0.110223 0.117787 -1.06407 66.0 3.0 56.7211 0.225622 9.63996 0.927044 1.06744 0.201039 0.7426 2.4323e-6 0.655581 0.0 0.0 0.0 0.0 0.0 0.0 0.0 0.0 0.0 0.0 0.0 0.0 0.0 0.0 0.0 0.0 0.0 0.0]
+
+--
+
+[3.33333 0.121148 0.033808 1.19447 -0.135271 0.0442381 -1.01926 0.0 0.0 0.0 -0.102466 0.114535 -0.896072 66.6667 2.66667 55.1408 0.206017 10.058 0.90649 1.1032 0.185638 0.671841 1.62484e-5 0.581203 0.106131 0.0382284 0.925414 0.0920784 0.0328706 0.933747 0.0 0.0 0.0 0.0 0.0 0.0 0.0 0.0 0.0 -0.115661 0.037252 -1.03494]
+
     \hline

### 2019-07-23 src/core.jl

@@ -25,7 +25,8 @@ function gsr(
     numfolds::Int=NUMFOLDS_DEFAULT,
     testsetshare::Union{Float32, Float64}=TESTSETSHARE_DEFAULT,
     exportcsv::Union{Nothing, String}=EXPORTCSV_DEFAULT,
-    exportsummary::Union{Nothing, String}=EXPORTSUMMARY_DEFAULT
+    exportsummary::Union{Nothing, String}=EXPORTSUMMARY_DEFAULT,
+    exportlatex::Union{Nothing, String}=EXPORTLATEX_DEFAULT
     )
 
     gsr(
@@ -55,7 +56,8 @@ function gsr(
         numfolds=numfolds,
         testsetshare=testsetshare,
         exportcsv=exportcsv,
-        exportsummary=exportsummary
+        exportsummary=exportsummary,
+        exportlatex=exportlatex
     )
 end
 
@@ -86,7 +88,8 @@ function gsr(
     numfolds::Int=NUMFOLDS_DEFAULT,
     testsetshare::Union{Float32, Float64}=TESTSETSHARE_DEFAULT,
     exportcsv::Union{Nothing, String}=EXPORTCSV_DEFAULT,
-    exportsummary::Union{Nothing, String}=EXPORTSUMMARY_DEFAULT
+    exportsummary::Union{Nothing, String}=EXPORTSUMMARY_DEFAULT,
+    exportlatex::Union{Nothing, String}=EXPORTLATEX_DEFAULT
 )
 
     if fe_lag == nothing || seasonaladjustment != nothing
@@ -142,6 +145,10 @@ function gsr(
 
     if exportcsv != nothing
         GlobalSearchRegression.Output.csv(data, filename=exportscsv)
+    end
+
+    if exportlatex != nothing
+        GlobalSearchRegression.Output.latex(data, original_data, path=exportlatex)
     end
 
     #println(GlobalSearchRegression.Output.summary(data, filename=exportsummary))

### 2019-07-23 test/dummy_test.jl

@@ -1,51 +1,18 @@
-using CSV, GlobalSearchRegression, Distributed
-
-using DataFrames, CSV
+using CSV, GlobalSearchRegression, Distributed, DataFrames, CSV
  
-data = DataFrame(Array{Union{Missing,Float64}}(randn(100,30)))
-data[1,2] = missing
-data[2,6] = missing
-data[3,2] = missing
-data[2,7] = 999999
-data[3,6] = 999999
-data[4,6] = 999999
-headers = [ :y ; [ Symbol("x$i") for i = 1:size(data,2) - 1 ] ]
-
-headers[3] = :positive
-headers[4] = :panel
-headers[5] = :time
-names!(data, headers)
-
-data[:,3] = data[:,3] .+ 10
-data[:,4] = collect(Iterators.flatten(fill(i,25) for i in 1:4))
-data[:,5] = collect(Iterators.flatten(1:25 for i in 1:4))
-
+data = CSV.read("data/fat.csv")
 @time data = GlobalSearchRegression.gsr(
-    "y x* positive", 
+    "y *", 
     data,
-    method=:precise,
     intercept=true,
-    panel=:panel,
-    time=:time,
-    seasonaladjustment=[:time => 4],
-    removeoutliers=true,
-    fe_sqr=[:x1],
-    fe_log=:positive,
-    fe_inv=:positive,
-    fe_lag=[:x10 => 1, :x11 => 2],
-    interaction=[:x11, :x12],
     preliminaryselection=:lasso,
-    fixedvariables=nothing,
-    outsample=20,
-    criteria=[:r2adj, :bic, :aic, :aicc, :cp, :rmse, :rmseout, :sse],
+    outsample=10,
+    criteria=[:aic, :aicc, :cp],
     ttest=true,
     modelavg=true,
     residualtest=true,
     orderresults=true,
     kfoldcrossvalidation=true,
-    numfolds=3
-    #testsetshare=nothing,
-    #exportcsv::Union{Nothing, String}=EXPORTCSV_DEFAULT,
-    #exportsummary::Union{Nothing, String}=EXPORTSUMMARY_DEFAULT
+    numfolds=3,
+    exportlatex="/home/valentin/GSREG.zip"
 )
-#GlobalSearchRegression.Output.latex(data, path="./Latex")

### 2019-07-25 src/Output/decorations/latex/tpl.tex
cross validation latex output

--- 2019-07-23 src/Output/decorations/latex/tpl.tex
@@
 
-\clearpage
-
 \begin{table}[!h]
@@
   \caption{Descriptive Statistics for the main dataset}
-    \begin{tabular}{|p{2cm}|p{4cm}|c|c|c|c|c|c|}
+    \begin{tabular}{|p{2cm}|c|c|c|c|c|c|c|}
     \hline
@@
     \hline
-    {{/name}}{{#name}}{{name}} & Insert Description & {{nobs}} & {{mean}} & {{std}} & {{max}} & {{min}} & {{miss}}\% \\ 
+    {{/name}}{{#name}}{{name}} &  & {{nobs}} & {{mean}} & {{std}} & {{max}} & {{min}} & {{miss}}\% \\ 
     {{/name}}{{/descriptive}}\hline
@@
     \hline
-    Skewness          & {{b.std}}      & {{t.std}} \\
+    Std               & {{b.std}}      & {{t.std}} \\
     \hline
-    kurtosis          & {{b.skew}}     & {{t.skew}} \\
+    Skewness          & {{b.skew}}     & {{t.skew}} \\
     \hline
-    Positive Share    & {{b.kurt}}     & {{t.kurt}} \\
+    kurtosis          & {{b.kurt}}     & {{t.kurt}} \\
     \hline
-    Significant Share & {{b.posshare}} & {{t.sigshare}} \\
+    Positive Share    & {{posshare}} &  \\
+    \hline
+    Significant Share &  & {{sigshare}} \\
     \hline
@@
     \multicolumn{3}{c}{K-fold scheme:\textbf{Insert scheme}}                             \\
-                    & {{kfolds}}-fold         & {{kfolds}}-fold \\
+               &                  \multicolumn{2}{c}{ {{kfolds}}-fold }                  \\
     Variables  & Mean                             & Median                               \\
@@
     \hline
-{{ median }}
-
---
-
-{{ average }}
-
     {{#kfoldvars}}
-      {{ varname }} & {{ meancoef }}{{stars}} & {{ mediancoef }}{{stars}} \\
-                    & {{ meanstd }}           & {{ medianstd }}           \\
+    {{name}}   & {{#mean}}{{b}}{{stars}}{{/mean}} & {{#median}}{{b}}{{stars}}{{/median}} \\
+               & {{#mean}}{{bstd}}{{/mean}}       & {{#median}}{{bstd}}{{/median}}       \\
     {{/kfoldvars}}
@@
 
-    Error out-sample &     &   \\
-                     &     &   \\
+    Error out-sample &  {{#outsample}}{{mean}}{{/outsample}}   & {{#outsample}}{{median}}{{/outsample}} \\
     \hline

### 2019-07-25 src/CrossValidation/utils.jl

@@ -3,14 +3,14 @@ Add values to extras
 """
 function addextras(data, result)
     data.extras[GlobalSearchRegression.generate_extra_key(CROSSVALIDATION_EXTRAKEY, data.extras)] = Dict(
-        :datanames => result.datanames,
         :ttest => result.ttest,
         :kfolds => result.k,
         :tsetsize => result.s,
         :panel => data.panel,
         :time => data.time,
-        :median => result.median_data, #TODO: Add expvars
-        :average => result.average_data #TODO: Add expvars
+        :datanames => result.datanames,
+        :median => result.median_data,
+        :average => result.average_data
     )
     return data
 end

### 2019-07-25 src/Output/Output.jl

@@ -11,7 +11,7 @@ module Output
             DataFrames,
             Distributions,
             Distributed
-    using Plots
+    using Plots, StatsPlots
     using ..GlobalSearchRegression
 
     export csv, summary, latex

### 2019-07-25 src/Output/core.jl

@@ -1,1 +1,1 @@
-#Base.show(io::IO, data::GlobalSearchRegression.GSRegData) = summary(data)
+Base.show(io::IO, data::GlobalSearchRegression.GSRegData) = ""

### 2019-07-25 src/Output/decorations/latex/latex.jl

@@ -25,7 +25,6 @@ end
 
 function get_col_statistics(data)
     nnan = filter(x -> !isnan(x), data)
-    poscol = filter(x -> x > 0, nnan)
     if( isempty(nnan) )
         return Dict(
             "avg"      => "",
@@ -33,8 +32,7 @@ function get_col_statistics(data)
             "mode"     => "",
             "std"      => "",
             "skew"     => "",
-            "kurt"     => "",
-            "posshare" => ""
+            "kurt"     => ""
         )
     end
     Dict(
@@ -43,8 +41,7 @@ function get_col_statistics(data)
         "mode"     => @sprintf("%.3f", mode(nnan)),
         "std"      => @sprintf("%.3f", std(nnan)),
         "skew"     => @sprintf("%.3f", skewness(nnan)),
-        "kurt"     => @sprintf("%.3f", kurtosis(nnan)),
-        "posshare" => @sprintf("%.3f", size(poscol, 1) / size(nnan, 1))
+        "kurt"     => @sprintf("%.3f", kurtosis(nnan))
     )
 end
 
@@ -118,8 +115,12 @@ function latex!(dict::Dict, data::GlobalSearchRegression.GSRegData, originaldata
         
         betas = dict[string(PreliminarySelection.PRELIMINARYSELECTION_EXTRAKEY)]["lassobetas"]
         betas_dict = []
+        @show betas
+        @show data.expvars
         for (i, beta) in enumerate(filter(j -> j != 0, betas))
             if( beta != 0)
+                @show beta
+                @show data.expvars[i]
                 push!(betas_dict, Dict("name" => replace(string(data.expvars[i]), "_" => "\\_"), "coef" => @sprintf("%.3f", beta)))
             end
         end
@@ -145,6 +146,7 @@ function latex!(dict::Dict, data::GlobalSearchRegression.GSRegData, originaldata
         if "fixedvariables" in keys(dict) && size(dict["fixedvariables"], 1) == 0
             delete!(dict["fixedvariables"])
         end
+
         datanames_index = GlobalSearchRegression.create_datanames_index(result.datanames)
         cols = GlobalSearchRegression.get_selected_variables(Int64(result.bestresult_data[datanames_index[:index]]), data.expvars, data.intercept)
         
@@ -209,16 +211,31 @@ function latex!(dict::Dict, data::GlobalSearchRegression.GSRegData, originaldata
                     end
                 end
             end
+
[…]

### 2019-07-25 src/PreliminarySelection/core.jl

@@ -19,7 +19,7 @@ end
 function lasso!(data::GlobalSearchRegression.GSRegData; addextrasflag=true)
     betas, lambda = lassoselection(data)
 
-    if betas == nothing
+    if isnothing(betas)
         return data, map(b -> true, data.expvars)
     end
 
@@ -53,7 +53,7 @@ function lassoselection(data)
     nvars = computablevars(size(data.expvars,1))
 
     if nvars >= size(data.expvars,1)
-        return data.expvars, nothing
+        return nothing, nothing
     end
 
     path = glmnet(data.expvars_data, data.depvar_data; nlambda=1000)

### 2019-07-25 test/latex.jl

@@ -1,15 +1,18 @@
-using CSV, GlobalSearchRegression, Distributed
-
-data = CSV.read("test/data/small.csv")
-
-data = GlobalSearchRegression.Preprocessing.input("y x*", data, intercept=true)
-result = GlobalSearchRegression.AllSubsetRegression.ols(
+using CSV, GlobalSearchRegression, Distributed, DataFrames, CSV
+ 
+data = CSV.read("data/fat.csv")
+@time data = GlobalSearchRegression.gsr(
+    "y *", 
     data,
+    intercept=true,
+    preliminaryselection=:lasso,
     outsample=10,
-    criteria=[:r2adj, :bic, :aic, :aicc, :cp, :rmse, :sse, :rmseout],
+    criteria=[:aic, :aicc, :cp],
     ttest=true,
     modelavg=true,
     residualtest=true,
-    orderresults=false
+    orderresults=true,
+    kfoldcrossvalidation=true,
+    numfolds=3,
+    exportlatex=ARGS[1]
 )
-GlobalSearchRegression.OutputDecoration.csv_res(result.results[1], "salida.csv")

### 2019-07-26 src/Output/decorations/latex/tpl.tex
Intelligent text

--- 2019-07-23 src/Output/decorations/latex/tpl.tex
@@
 
-%In this figure it is shown that potential covariates included in the general unrrestricted model of the all-subset-regression algorithm display singnificant differences in terms of the user selected information criteria.
+{{#intelligent_text}}
+In this figure it is shown that potential covariates included in the general unrrestricted model of the all-subset-regression algorithm display singnificant differences in terms of the user selected information criteria.
 For each explanatory variable information criteria gains were obtained as the differece between averages information criteria obtained from models which includes and excludes that covariate.
-Available statistics suggests that there {{are or is}} {{numofpositivegainsvariables}} explanatory {{variable or variables}} that improved model accuracy.
-{{Among them, {{bestvar}} or {{bestvar}}}} helps to increase up to a {{gainsinperc}}\% the user selected information criteria.
-On the contrary, there {{are or is}} {{numofnegativegainsvariables}} {{covariate or covariates}} that have a deleterious impact on model accuracy.
-This is specially true for {{worstvar}}, which seems to decrease up to a {{lossinperc}}\% the user selected information criteria}}
+Available statistics suggests that there {{^multiple_positive_variables}}is{{/multiple_positive_variables}}{{#multiple_positive_variables}}are{{/multiple_positive_variables}} {{numofpositivegainsvariables}} explanatory {{^multiple_positive_variables}}variable{{/multiple_positive_variables}}{{#multiple_positive_variables}}variables{{/multiple_positive_variables}} that improved model accuracy.
+{{#multiple_positive_variables}}Among them, {{/multiple_positive_variables}} {{ bestvar }} helps to increase up to a {{bestvar_gainsinperc}}\% the user selected information criteria.
+{{#no_negative_variables}}And least important variable is {{ worstvar }} which only increases information criteria in {{worstvar_gainsinperc}}\%.{{/no_negative_variables}}
+
+{{^no_negative_variables}}On the contrary, there {{^multiple_negative_variables}}is{{/multiple_negative_variables}}{{#multiple_negative_variables}}are{{/multiple_negative_variables}} {{numofnegativegainsvariables}} {{^multiple_negative_variables}}covariate{{/multiple_negative_variables}}{{#multiple_negative_variables}}covariates{{/multiple_negative_variables}} that decreased the model accuracy.
+This is specially true for {{worstvar}}, which seems to decrease up to a {{worstvar_gainsinperc}}\% the user selected information criteria.{{/no_negative_variables}}
+{{/intelligent_text}}
+
 {{/allsubsetregression}}

### 2019-07-26 src/Output/decorations/latex/latex.jl

@@ -335,4 +335,26 @@ function create_figures(data, destfolder)
     labels = convert(Array{String}, a[:,2])
     bar(labels, a[:,1], legend = false, color = :blues, orientation = :horizontal, xlabel="Average impact of each variable on the Adj. R2")
     savefig(joinpath(destfolder, "cov_relevance.png"))
+
+    positivegainsvariables = findall(x => x > 0, a[:,1])
+    negativegainsvariables = findall(x => x < 0, a[:,1])
+
+    intelligent_text = Dict()
+    intelligent_text["numofpositivegainsvariables"] = size(positivegainsvariables, 1)
+    intelligent_text["numofnegativegainsvariables"] = size(negativegainsvariables, 1)
+
+    intelligent_text["multiple_positive_variables"] = intelligent_text["numofpositivegainsvariables"] > 1
+    intelligent_text["multiple_negative_variables"] = intelligent_text["numofpositivegainsvariables"] > 1
+    intelligent_text["no_negative_variables"] = intelligent_text["numofnegativegainsvariables"] == 0
+
+    
+    intelligent_text["bestvar"] = a[1,2]
+    intelligent_text["bestvar_gainsinperc"] = a[1,1]
+
+    intelligent_text["worstvar"] = a[end,2]
+    intelligent_text["worstvar_gainsinperc"] = a[end,1]
+
+    dict[string(GlobalSearchRegression.AllSubsetRegression.ALLSUBSETREGRESSION_EXTRAKEY)]["intelligent_text"] = intelligent_text
+
+
 end

### 2019-07-26 src/Output/decorations/latex/tpl.tex
Intelligent text

@@
     \hline
-{{ median }}
---
-{{ average }}
     {{#kfoldvars}}
-      {{ varname }} & {{ meancoef }}{{stars}} & {{ mediancoef }}{{stars}} \\
-                    & {{ meanstd }}           & {{ medianstd }}           \\
+    {{name}}   & {{#mean}}{{b}}{{stars}}{{/mean}} & {{#median}}{{b}}{{stars}}{{/median}} \\
+               & {{#mean}}{{bstd}}{{/mean}}       & {{#median}}{{bstd}}{{/median}}       \\
     {{/kfoldvars}}

### 2019-07-26 test/AllSubsetRegression/runtests.jl

@@ -6,8 +6,6 @@ data_small = CSV.read(DATABASE_SMALL)
     @testset "With T-test" begin
         res = gsr("y x*", data_small, ttest=true)
 
-        @show res.results[1]
-
         @test 1 == 1
     end
 end

### 2019-07-26 test/dummy_test.jl

@@ -1,4 +1,4 @@
-using CSV, GlobalSearchRegression, Distributed
+using CSV, GlobalSearchRegression
 
 data = CSV.read("visitors.csv")
 
@@ -18,6 +18,7 @@ data = GlobalSearchRegression.gsr(
     residualtest=true,
     orderresults=true,
     kfoldcrossvalidation=true,
-    numfolds=5,
-    exportcsv="visitors_output.csv"
+    numfolds=10,
+    exportcsv="visitors_output.csv",
+    exportlatex="latex.zip"
 )

### 2019-09-24 src/Output/decorations/latex/latex.jl
latest changes

@@ -238,6 +238,8 @@ function latex!(dict::Dict, data::GlobalSearchRegression.GSRegData, originaldata
         end, data.expvars)
         
         dict[string(GlobalSearchRegression.AllSubsetRegression.ALLSUBSETREGRESSION_EXTRAKEY)]["expvars"] = expvars_dict
+        dict[string(GlobalSearchRegression.AllSubsetRegression.ALLSUBSETREGRESSION_EXTRAKEY)]["expvarswithoutcons"] = 
+        filter(x -> x["name"] != :_cons, expvars_dict)
         dict[string(GlobalSearchRegression.AllSubsetRegression.ALLSUBSETREGRESSION_EXTRAKEY)]["bestmodel"] = d_bestmodel
 
         if dict[string(GlobalSearchRegression.AllSubsetRegression.ALLSUBSETREGRESSION_EXTRAKEY)]["criteria"] != nothing

### 2019-09-24 test/latex.jl
rm extra files

@@ -1,18 +1,0 @@
-using CSV, GlobalSearchRegression, Distributed, DataFrames, CSV
- 
-data = CSV.read("data/fat.csv")
-@time data = GlobalSearchRegression.gsr(
-    "y *", 
-    data,
-    intercept=true,
-    preliminaryselection=:lasso,
-    outsample=10,
-    criteria=[:aic, :aicc, :cp],
-    ttest=true,
-    modelavg=true,
-    residualtest=true,
-    orderresults=true,
-    kfoldcrossvalidation=true,
-    numfolds=3,
-    exportlatex=ARGS[1]
-)

### 2019-10-01 paper/paper.tex
Update paper.tex

--- 2019-07-12 paper/paper.tex
@@
 The aim of this paper is twofold.
-The first one is to describe a novel research-project aimed at building bridges between machine learning and econometric worlds.
+The first one is to describe a novel research-project designed for building bridges between machine learning and econometric worlds.
 The second one is to introduce the main characteristics and comparative performance of the first Julia-native all-subset regression algorithm included in \verb GlobalSearchRegression.jl  (v1.0.3).
@@
 Execution times were obtained from a HED architecture using a Threadripper 1950x build, with 16 cores (32 threads) overclocked to 3.8GHz and 64 GiB of DDR4-RAM at 3200Mhz.
-Comparative scripts were implemented on Julia 1.0.3, R 3.6.0 and Stata 15 IC, running on Ubuntu 18.04.2 LTS -Linux kernel 4.15-\footnote{All these test are available \href{https://github.com/ParallelGSReg/GlobalSearchRegression.jl/tree/master/juliacon2019proceedings/reproducibility}{here}} \vskip 6pt
+Comparative scripts were implemented on Julia 1.0.3, R 3.6.0 and Stata 15 IC, running on Ubuntu 18.04.2 LTS -Linux kernel 4.15-\footnote{All these test are available \href{https://github.com/ParallelGSReg/GlobalSearchRegression.jl/tree/master/Reproducibility}{here}} \vskip 6pt
 
